\chapter{Soundings}

Dawn arrived in shades of pewter, a muted wash of light that made the harbor look as though someone had sketched it in graphite and forgotten to color the page. Elena Ruiz pulled her hood tight against the chill and tightened the straps on her weight belt while the skiff rocked beneath her boots. Spray beaded on the metal railings, quicksilver dots that dripped back into the bay as if reluctant to let the day begin.

"Last checks," she called, voice muffled by her neoprene hood. Her breath fogged the air between her and Talia, who stood knee-deep on the stern platform, mask already in place. Beyond them, the Providence team adjusted their gear in efficient silence, the emergency dive now routine in the wake of Calista. It had been three days since the hurricane, three days of triage dives at dawn and paperwork marathons at dusk. Exhaustion had set up camp in Elena's muscles like an unwelcome tenant.

Talia flashed an OK sign. "Currents are calmer than yesterday," she said. "Visibility might even stretch to a meter if we're lucky."

"I'll take a meter." Elena glanced toward the shoreline. The boardwalk was still a patchwork of tarps and exposed joists, volunteers moving like ants along the fractured length. Generators hummed, mingling with gull cries and the distant thrum of a Coast Guard cutter ferrying supplies. Somewhere behind the mobile lab's open door, Marco's voice carried over a crackling radio, promising more caldo and coffee for anyone with a bucket brigade blister.

Elena rolled her shoulders, banishing the ache that threatened to distract her. She dropped backward into the water. Cold wrapped around her like an iron embrace. For a heartbeat she let herself hang suspended, bubbles streaming past her ears. Then she angled downward, following the guide rope toward the nursery grid.

The water remained a fog of sediment despite Talia's optimism. Elena narrowed her focus to what lay within arm's reach: twisted fronds of eelgrass, a stray dock plank, the ghostly outline of their first frame emerging like a shipwreck. A thin film of containment gel still shimmered around the solvent drum they'd secured the day before, the curtain billowing gently in the tide. The Providence diver stationed beside it lifted a hand in greeting.

Elena checked the instruments clipped to her chest harness. Temperature two degrees cooler than yesterday—good. Turbidity high—expected. Oxygen levels stable—miraculous. She let relief seep in, careful not to let it loosen the determination that kept her limbs moving. They had lost thirty percent of the nursery, but the surviving coral still clung stubbornly to life, polyps open, grasping at currents laden with plankton.

She eased along the frame, fingers skimming the metal struts. A snapped branch wavered beside her, tips glowing faintly in the filtered light. She cradled it carefully, mindful of the mucous layer that protected the living tissue, and tucked it into the mesh collection pouch tethered to her hip. For every fragment they could salvage today, there was a chance it would reanchor in a rehab tank, regrow, rejoin the reef. The work felt like rescuing syllables of a language she refused to let the ocean forget.

By the time her tank gauge dipped toward the reserve line, the pouch bulged with fragments. She and Talia ascended together, breaking through the surface in tandem. Air rushed into Elena's lungs with a gasp that tasted of diesel and dawn.

"Three frames cleared," Talia reported, pulling off her mask. Her dark hair clung to her cheeks. "The pump housing on Frame Six is still loose, but I cinched it down with a new clamp."

"Good." Elena hauled herself onto the platform, muscles trembling. She stripped off her gloves, flexing fingers tinged pink from the cold. The Providence divers hoisted the solvent drum into a containment cradle with careful efficiency. Elena watched until the drum sat secure, the hazard labels glaring accusation in the weak light.

"Department of Environmental Protection wants a sample before we dispose of it," one diver said.

"They can take all the samples they want," Elena replied. Rage simmered beneath the fatigue, a slow-burning current she harnessed to stay upright. "Just make sure the chain of custody is airtight. Tidefront isn't wriggling out of this."

She helped guide the collection bags into insulated coolers, logging each fragment and location. The clipboard blurred momentarily. Elena blinked hard, clearing the dizziness. Sleep had become a rumor. Meals a handful of almonds between briefings. She pressed the back of her hand to her eyes until the world steadied.

"You're running on fumes," Talia observed. "Let me take the afternoon dive."

"You have the mayor's briefing," Elena reminded her. "And the volunteers trust your updates more than mine right now. You're the reason half the high school signed up for marine ecology workshops."

Talia snorted. "Flattery doesn't make you less exhausted."

"No," Elena agreed. "But data does. Get the new growth charts uploaded before noon. The oversight committee wants real-time metrics."

Talia rolled her eyes affectionately. "Yes, boss."

By the time Elena crossed the boardwalk toward the Institute, the sun had burned through the clouds enough to paint the bay in muted silver. Volunteers hammered new planks in a steady rhythm while prayer flags snapped overhead and children ferried buckets of debris and sea glass toward the recycling bins.

Inside the Institute's conference room, the air smelled faintly of coffee and wet plywood. Priya stood at the head of the table, sleeves rolled to her elbows, a stack of legal briefs in one hand. Adrian sat beside her with a laptop open, its screen cluttered with spreadsheets and satellite imagery. His tie hung loose, the crisp professionalism of the Sterling Foundation tempered by the salt stains on his cuffs.

"How bad?" Priya asked as soon as Elena stepped in.

Elena set the coolers gently on the table. "Survivability looks better than yesterday's dive. We salvaged twenty-one viable fragments. Frame Six is stable. The solvent drum is secured and ready for DEP sampling."

Priya exhaled slowly, some tension bleeding from her shoulders. "That's something."

Adrian slid a fresh cup of coffee across the table. "Drink," he said softly. "We have a video call with the Department of Coastal Oversight at ten, and the Attorney General's office at noon."

Elena wrapped her hands around the mug, letting the heat sink into her palms. "Any update from Tidefront's legal team?"

"They're sending their project manager to the oversight hearing," Adrian replied. "Lane Caldwell. He wants to argue the drum was an unavoidable casualty of the storm, not negligence."

Priya barked a humorless laugh. "Then Lane can explain why their emergency protocols listed those drums as secured when clearly they were not."

Elena sifted through the stack of paperwork. Permit violations. Photographs of the breached containment berm. Testimony from contractors whose overtime requests had been denied in favor of speed. Each document was a wave building toward something unstoppable.

"The community deserves to hear the truth," she said. "We take them the data, the photos, the sample analysis. We show them the reef's injuries."

"We also show them the path forward," Adrian added. His eyes met hers, steady. "The foundation board approved emergency funds this morning. Four million to cover immediate restoration, volunteer stipends, mental health services. And we're redirecting the Tidefront grant toward building a permanent marine resilience lab on the cannery's second floor."

Elena blinked. "You pushed that through already?"

"Our board needed to respond before the news cycle paints us as complicit." He spread his hands. "And we are complicit. That doesn't change the fact that we can leverage our weight to repair what we broke."

Priya nodded once. "We'll announce the lab at the oversight hearing. It turns the narrative from failure to accountability."

The word \textit{lab} settled in Elena's chest with a strange mix of hope and dread. A permanent facility. Resources beyond anything they'd dared to dream. The kind of infrastructure that could keep Marisport's reef on the map long after the hurricane scars faded. And yet the letter in her jacket pocket grew heavier, its folded edges pressing against her ribs like a reminder.

She pulled the letter free, smoothing the creases. Priya's gaze sharpened. "You tell Marco yet?"

"Not yet." Elena's voice came out thinner than she intended. "I haven't told anyone."

"I assume this isn't a rejection," Adrian said lightly, attempting levity that didn't quite reach his eyes. "Unless you're composing a very polite no."

Elena traced the International Oceanic Collective letterhead with her thumb. "Dr. Okoye wants an answer within the week. Six months abroad. Rotations after that. Funding for the Institute and community partners."

Priya set down her legal briefs, the motion so deliberate it quieted the air between them. "Elena, this invitation is everything you've worked for."

"It's everything that takes me away." The words escaped before she could temper them. She swallowed. "We're hanging the reef together with fishing line and borrowed hope. Marco's café is a relief kitchen. My father is rebuilding half the boardwalk by hand. If I leave now—"

"If you leave," Priya interrupted gently, "you do it with a plan so solid the town can't imagine failing. The lab gives us infrastructure. Talia is ready to step into more leadership. Marco has a staff who adores him. Your father has two apprentices waiting for him to stop micromanaging."

Elena laughed despite the tightness in her throat. "He'll never stop micromanaging."

"Exactly." Priya squeezed her shoulder. "Tell Marco before rumors do. We'll shoulder whatever falls."

Adrian cleared his throat. "If you want me to brief the board on your potential leave, I can frame it as a sabbatical."

"I don't know what I want you to frame it as," Elena said, honest. "I don't know if I'm staying or going."

Priya's gaze softened. "You're allowed to want both."

Before Elena could respond, the conference room door swung open and Marco strode in carrying a tray of sandwiches wrapped in parchment. Flour dusted his forearms. Fatigue lined his face, but his smile ignited warmth in her chest.

"I heard something about coffee but no mention of actual food," he said as he set the tray down. Priya snatched a sandwich with a grateful hum. Marco brushed a quick kiss against Elena's temple, the simple contact undoing her.

"How's the kitchen?" she asked, already anticipating the answer.

"Feeding half the town." His tired smile held pride. "Ignacio keeps trying to sneak back onto the grill. Mom's threatening to duct-tape him to a chair."

Elena chuckled, tension easing. "Sounds right."

Marco followed her gaze to the letter in her hand. "Problem?"

She folded the paper. "Something we should talk about tonight."

He nodded, understanding sharpening his features. "Then tonight." Another squeeze to her shoulder, and he was gone, the scent of coffee trailing behind him.

The door clicked shut. Silence settled like silt. Priya lifted her brows. "Tonight," she echoed.

"Tonight," Elena confirmed, the single word heavy with everything she had yet to confess.

\bigskip

The morning blurred into meetings. The Department of Coastal Oversight wanted detailed contamination mapping; Elena delivered numbers, overlays, drone footage. The Attorney General's office requested sworn statements; Priya provided them, citing every statute violated. Adrian navigated the Sterling board's contrition and strategy with the precision of a captain steering through a minefield.

By midafternoon, the Institute had transformed into a rotating stage of officials, volunteers, and journalists. Elena slipped out whenever she could, moving between the rehab tanks to monitor the newly collected coral fragments. The tanks glowed azure beneath the lab's fluorescent lights, bubbles rising like tiny prayer beads. She logged each fragment's condition, adjusting water flow, whispering encouragement she pretended was only for the coral.

"Talking to them helps," a voice said softly. Dr. Nia Okoye smiled up at her from the tablet propped on the counter, bracelets flashing as she adjusted the camera.

"Nia," Elena breathed. "I wasn't expecting—"

"I watched the footage," Nia said. "Your town weathered a monster. Your leadership was \textit{agbara}. Strength of spirit." She leaned closer. "Which is precisely why I want you in this consortium. We're building a network of coastal communities adapting in real time. We need someone who understands that reefs are kin, not scenery."

"If I join, I'm gone six months," Elena said. "Maybe longer."

"You've built a team to carry on," Nia countered. "Priya, Talia, even Adrian Sterling. They believe in this work because you taught them how." Her gaze softened. "The world needs your blueprints, Elena. Marisport's resilience could guide villages halfway across the globe."

Elena stared at the coral fragments, each one a delicate tree waiting to root. "When do you need an answer?"

"Forty-eight hours."

The words tightened Elena's chest. "Forty-eight hours," she echoed.

"Whatever you decide," Nia said, "the invitation remains open. But I hope you'll let the tide carry you farther."

The call ended with promises of follow-up documents. Elena sat in the quiet hum of the lab, the water pumps keeping rhythm with her pulse. Forty-eight hours. Two tides. Not enough time and exactly the amount the ocean ever afforded her.

\bigskip

Evening draped itself over Marisport in hues of indigo and copper. The Lighthouse Café glowed like a lantern, windows fogged from steam and laughter. Marco moved among volunteers with the grace of someone who could sense hunger before it was voiced, his mother wielding a wooden spoon like a scepter.

Elena washed her hands, tied on an apron, and elbowed him gently. "Point me to the bowls."

"Thought you were banned after the gumbo fiasco," he teased.

"New era," she shot back, falling into step beside him. Together they ladled soup, traded quick jokes with fishermen comparing storm scars, and slipped bowls into tired hands. Priya typed furiously in the corner while Adrian coordinated deliveries by the door. Through the window, lanterns lined the broken boardwalk, flickering in memory and defiance.

When the last volunteer drifted out and Isabela retreated upstairs to rest, the café settled into quiet. Marco locked the door, flipped the sign to \textit{Closed}, and turned to face Elena. The lantern light softened his features, but the worry etched there was stark.

"Forty-eight hours," he said softly.

Elena froze. "You heard?"

"Priya stopped by the kitchen with legal briefs and accidentally mentioned it." He stepped closer. "Why didn't you tell me?"

She set the dish towel down, fingers trembling. "Because I was afraid the words would make it real. Because every time I tried, someone needed sandbags or satellite maps or a lullaby. Because I didn't know how to ask you to hold me while I contemplated leaving."

Marco's expression crumpled, not with anger but with hurt. "Elena."

She forced herself to meet his gaze. "Dr. Okoye wants me to lead a global coral resilience initiative. Six months in the Philippines, then rotating residencies. Funding for the Institute, for community partners. It's everything I've fought for." Her voice cracked. "And the timing is cruel."

He leaned against the counter, arms folded. "Do you want to go?"

She opened her mouth, closed it. Honesty tasted like salt. "Yes," she whispered. "God, yes. I want to learn from reefs halfway around the world, bring back techniques that could save ours, prove that Marisport's work matters on a global scale."

He nodded slowly. "Then say the rest."

"I'm terrified that if I leave, everything will crumble. That I'll come back to find the reef dead, the Institute underfunded, the café a memory. I'm terrified of losing you."

Marco's laughter was ragged. "You think I haven't been terrified every day since Calista's first wind advisory? Since Adrian walked back into town? Since you dove into a storm surge to relight the lighthouse? Fear doesn't disappear if you stay." He pushed off the counter, stepping close enough that his presence filled her senses. "But Elena, you don't get to dim yourself because you're afraid of what shines beyond this harbor."

Tears pricked her eyes. "How are you so calm?"

"I'm not." He cupped her face, thumbs brushing away the tears that escaped. "Inside, I'm a tangled fishing line. But I also know who you are. You'd haunt yourself if you turned this down. I'd rather learn how to love you across oceans than watch you wither within sight of the lighthouse."

She pressed her forehead to his. "I don't deserve you."

"Too late." He kissed her, slow and grounding. The kiss tasted of cinnamon and salt, of promises forged in gale-force winds. When they pulled apart, his eyes shone. "We'll figure out the logistics. We'll set up calls, send care packages, argue about time zones."

Elena laughed through the tears. "You'll fall asleep on video chats with flour on your cheek."

"And you'll pretend you're not crying when baby coral spawn." He rested his forehead against hers again. "Tell me what you need to make this decision."

"I need to know the town won't see it as abandonment." The admission thudded between them. "That Priya won't resent me. That Adrian won't take this as his chance to..." She trailed off, uncertain.

Marco shook his head. "Priya is already plotting your going-away party. Adrian wants to be the kind of man who supports you, not the reason you stay. And the town? They watched you face down a hurricane. They'll understand that you're fighting for them from afar."

Elena inhaled shakily. "Forty-eight hours."

"We'll make every one count." He kissed her once more, then stepped back. "For tonight, sleep. I'll cover the morning shift. You don't have to be at the boardwalk at dawn."

She opened her mouth to protest. He silenced her with a look. "Sleep, mi sirena."

She yielded, exhaustion crashing over her like a wave. They climbed the stairs to the small apartment above the café, shedding damp clothes for soft cotton. Marco fell asleep within minutes, his breathing steady. Elena lay awake longer, the letter on the nightstand a silent metronome ticking down the hours. When sleep finally claimed her, it pulled her into dreams of reefs glowing like constellations beneath foreign seas.

\bigskip

The next morning dawned crisp, the air washed clean by post-storm breezes. Elena woke to the smell of coffee and the sight of a note taped to the bedroom door in Marco's looping handwriting: \textit{Go to the Institute. Priya threatened to kidnap you if you tried to steal a shift. Also, your father says the new pilings await your inspection. Love you.}

She smiled despite the anxiety curling in her gut. She dressed quickly, tucking the invitation letter into her satchel, and stepped onto the boardwalk. Workers already clustered around the damaged sections, their chatter buoyant. Her father stood on the edge of a newly installed piling, arms crossed, supervising two apprentices as they bolted a brace into place.

"Don't hover," Elena called. "They've got it."

"I'm supervising quality control," he retorted. "You taught me that phrase, remember?"

She kissed his cheek. "I'll be at the oversight hearing by noon. Try not to rebuild the entire town before I get back."

"No promises." He squeezed her hand. "Do what you always do. Tell the truth louder than anyone else."

At the Institute, Priya tossed her a garment bag. Inside hung a navy suit, improbably tailored to fit.

"Mayor Liao's emergency stash," Priya said. "Functional pockets included."

Elena pinned her hair into a sleek twist, startled by how quickly the salt-crusted scientist gave way to a composed witness.

They drove to Providence in Adrian's SUV, poster tubes rattling in the back seat. Outside, storm-scarred dunes blurred past while Adrian gripped the wheel too tightly.

"You good?" Priya asked.

"Define good," he muttered. "I'm about to dismantle a project my family funded."

"Then do it clean," Priya said. "Lane will blame the storm. We'll show the negligence." Elena let their exchange anchor her, palm pressed to the glass as the tide beside the highway kept steady time.

The State Department of Coastal Oversight convened in a stark auditorium lined with photographs of Rhode Island's shoreline. Reporters filled the back rows. Community members from Marisport clustered together, faces drawn but resolute. Mayor Liao sat beside Captain Hernández, both of them wearing the storm's fatigue like armor. Talia had taken the train at dawn, her notebook already open.

Lane Caldwell stood at the front with a glossy presentation projecting behind him. Slick suit, polished smile, the kind of man who believed charm could plaster over structural cracks. "Calista was a once-in-a-century storm," he declared. "Our site complied with all safety protocols. The solvent drum dislodged due to unprecedented surge levels."

Elena's jaw tightened. Priya squeezed her arm. "Our turn," she murmured when the chairwoman called Elena's name.

Elena approached the podium, heart pounding but steps steady. She placed the coral fragment she'd carried in a small glass bowl on the table—a visual reminder of what the hearing threatened to reduce to charts. Cameras clicked.

"Dr. Elena Ruiz," the chairwoman said. "You have prepared a statement."

"I have," Elena replied. She unfolded her notes, the paper thick beneath her fingers. "On October seventeenth, Hurricane Calista struck Marisport with sustained winds of one hundred twenty miles per hour and a storm surge of nearly ten feet. Our coral nursery—established in partnership with the Sterling Foundation and adjacent to the Tidefront Residences construction site—sustained significant damage. Thirty percent of our coral fragments were destroyed. The rest were coated in debris, including a fifty-gallon drum of hydrocarbon solvent labeled as Tidefront property."

She clicked the remote. Drone footage filled the screen—before and after shots of the nursery, the drum wedged like a canker among the coral. Gasps rippled through the room.

"Tidefront's emergency plan, submitted to this committee six months ago, listed all hazardous materials as stored in secured containment lockers three feet above projected surge levels. The drum we recovered had been stored at ground level, behind a temporary barricade that failed."

She let the silence stretch. "This was not an unforeseeable act of God. It was negligence. Negligence that compounded a natural disaster's impact and threatened a protected reef we have spent five years restoring."

Lane shifted in his seat. "Dr. Ruiz, with all respect, no containment system is foolproof against a Category Three—"

"Category Three storms are no longer anomalies," Elena cut in, voice steady. "They're the new normal. You marketed Tidefront as climate-resilient luxury. Yet your contractors cut corners to meet deadlines. You declined overtime requests to secure containers before the storm. You filed progress reports with falsified photographs."

The room buzzed. Lane's smile faltered. "Those allegations are unsubstantiated."

Priya rose smoothly, binder in hand. "We have affidavits from former employees, timestamped emails, and procurement records showing cheaper, non-compliant braces purchased to save costs." She placed copies before the committee. "And we have the solvent sample ready for DEP analysis."

The chairwoman's expression hardened. "Mr. Caldwell, can you explain these discrepancies?"

Lane stammered. "Our subcontractors—"

"Your responsibility," Adrian interjected from the audience, his voice clear. "The Sterling Foundation funded this project under the agreement that all environmental safeguards would be met. They were not. As CEO, I am suspending all financial support to Tidefront effective immediately. Those funds will be redirected to the Marisport Marine Institute to establish a permanent resilience lab and cover damages caused by this negligence."

"Watch me," Adrian said quietly when Lane sputtered a protest.

Elena met the committee's gaze. "Marisport is not opposed to development. We are opposed to development that treats our coastline like a prop. The reef is not decoration. It is defense. Habitat. History. You cannot buy back what you break with fines. You can only rebuild with accountability." She placed a hand on the glass bowl containing the coral fragment. "This survived the storm. It clung to the nursery frame while waves tried to rip it free. Give us the authority and resources to ensure the next storm doesn't carry a chemical weapon into our waters."

Silence followed her words, thick and charged. The chairwoman conferred briefly with her colleagues before speaking. "Effective immediately, the Department orders Tidefront Residences to cease operations pending a full environmental audit. All hazardous materials must be removed under DEP supervision. The Department will pursue penalties for safety violations. Furthermore, we support redirecting Sterling Foundation funds to the Marisport Marine Institute for the establishment of a resilience laboratory and community relief."

Applause broke out among the Marisport contingent. Elena released a breath she hadn't realized she'd been holding. She caught Talia's eye—tears shone on the younger woman's lashes. Captain Hernández thumped his cane twice in approval. Lane slumped, defeat etched across his features.

As the hearing adjourned, reporters surged. Elena kept her answers focused on community resilience while Priya worked the prosecutors and Adrian owned the foundation's failure. In the lobby, Mayor Liao clasped Elena's hands. "Magnificent," she said. "This lab changes everything. And when you call from the Philippines, we'll have better Wi-Fi."

Elena nodded, throat tight.

Outside, autumn sun burned brighter than it had in days. Elena stepped aside for a breath as Adrian joined her, tie loosened entirely.

"You okay?" he asked.

"Ask me in forty-eight hours," she replied, echoing her words to Marco.

He huffed a laugh. "Fair." He shoved his hands in his pockets. "For what it's worth, I meant every word in there. Redirecting the funds isn't enough, but it's a start."

"It's more than a start." She studied him. "Thank you for not making this about you."

"Trust me, the temptation was there," he said wryly. "Old habits die hard. But watching you and Marco..." He trailed off, looking out at the Providence River. "You're the tide that keeps this town honest. I'm just trying not to drown in my own mistakes."

Elena's expression softened. "You're doing more than staying afloat."

He shook his head. "Don't absolve me yet." He hesitated. "If you go—when you go—I'll keep the lab on track. Priya and I already drafted a governance plan. Talia's on the advisory board. This place will thrive."

The certainty in his tone steadied her. "Hold me to the promise that you'll stay," she said. "The town needs you to rebuild your family's name with actions, not press releases."

"Consider me anchored." He extended a hand. She squeezed it, gratitude and history woven into the grip.

The drive back to Marisport passed in a blur of phone calls. Priya fielded media requests. Adrian coordinated with lawyers. Elena leaned her head against the window, the coastline sliding by like a film strip. Her phone buzzed with messages—Talia sending heart emojis, Marco asking for updates, her father requesting a hardware list.

When they reached the harbor, dusk had settled. Lanterns lined the boardwalk, twice as many as the night before. Volunteers moved among them, relighting wicks. Children dangled shells from strings between the lamps, the makeshift mobiles chiming in the breeze.

The Institute's parking lot had been transformed into an impromptu celebration. Someone wheeled out speakers playing a playlist of beach-town classics. Tables overflowed with potluck dishes. The air smelled of grilled fish and cinnamon. Marco stood near the mobile lab, distributing cups of hot cider. He looked up as Elena approached, relief lighting his features.

"How'd it go?" he asked, pressing a mug into her hands.

"Tidefront shut down. Funds redirected." She took a sip, letting the cider's warmth soothe her throat. "They're building us a resilience lab."

Cheers erupted around them as the news rippled through the crowd. Someone hoisted Elena onto a crate, insisting she share the update. She spoke briefly, focusing on the community's victory rather than personal accolades. The crowd responded with applause, then with renewed determination. Sign-up sheets for lab volunteer committees circulated. Musicians tuned instruments for a spontaneous jam session. The town, battered but unbowed, chose celebration as resistance.

As the night deepened, Elena wandered toward the water's edge. The lanterns painted the waves gold. She could almost imagine the reef shimmering beneath, wounded but alive. Marco joined her, sliding an arm around her waist. Priya stood nearby, phone finally tucked away. Adrian lingered a few steps behind, hands in his pockets, gaze fixed on the horizon.

Elena's phone buzzed. A text from Dr. Okoye: \textit{Hope the hearing went well. When you're ready, let's discuss travel logistics.}\

Forty-eight hours had shrunk to less than twenty-four. The countdown drummed in her pulse. She took a deep breath.

"I have to call her," she said quietly.

Marco squeezed her hand. "Do it."

She stepped away from the crowd, down to the break in the boardwalk where the storm had ripped away planks. The temporary railing glittered with shells tied there by children. Elena dialed. The phone rang twice.

"Elena," Nia greeted. "I take it the hearing brought good news?"

"It did." Elena stared at the dark water, the tide inching inward. "And I have an answer for you."

Her voice steadied. "I'm in."

Nia's delighted exhale crackled through the speaker. "Welcome aboard."

The words loosened a knot Elena hadn't realized she carried. Relief mingled with fear, with exhilaration, with the ache of impending distance. She ended the call and turned back toward the celebration. Marco's smile met her, luminous. Priya lifted a glass in salute. Adrian nodded once, solemn approval.

Elena rejoined them, the night wrapping around her like a promise. The lantern light reflected in her eyes as she leaned into Marco, as Priya clapped her back hard enough to make her laugh, as Adrian murmured something about flight logistics.

The tide surged, kissing the scarred shoreline. The resilience lab would rise. The reef would heal, stubborn and luminous. Elena would leave, carrying Marisport in her bones, returning with new stories etched in salt. The town that had taught her to listen to the water now urged her to follow it beyond the horizon.

Above them, the lighthouse beam swept across the harbor, a slow, steady arc. Elena lifted her face to the light, let it paint her in silver, and felt the moment she had been bracing for finally arrive. The tide was turning, and she chose to move with it.

\noindent\textit{Reflection: Saying yes to Nia under lantern light felt less like leaving and more like widening the circle that keeps Marisport afloat. Watching the town celebrate, I understood that our resilience lab is already bigger than one coastline. My job now is to make sure the tide that carries me away also brings back resources, stories, and strength for everyone who lifted those lanterns with me.}
