\chapter{Shockwaves}

The lagoon held its breath as the sun slid behind the karst cliffs. Cicadas hummed in the palms, their rhythm syncing with the thud of Elena's pulse. Headlamps bobbed across the compound while the team gathered in the equipment shed, hands busy with coils of cable and waterproof cases. The air smelled of salt and solder. Elena checked the hydrophones one by one, fingers moving with a focus that blurred the edges of her exhaustion.

"Set two along the reef shelf and one inside the channel," Aisha instructed, tapping the map spread across a crate. Her voice carried the clipped calm of someone who refused to acknowledge fear. "Leo, you're with me on the drone boat. Elena, Alon, take the night dive. We need acoustic proof before the coast guard will commit a patrol."

Alon adjusted the strap of his dive light, eyes narrowed. "The syndicate listens, too. If they spot the drone, they'll relocate."

"Then we move quieter than they do," Elena said. The compass pressed warm against her sternum, a steady counterpoint to the electric tension thrumming through her.

Aisha's gaze flicked toward her. "You sure you're ready for a night dive after forty-eight hours on island time?"

"I've slept worse," Elena replied, thinking of hurricane shifts in Marisport, the laboratory lights blinking through endless rain. "We don't get a second chance if they blast the nursery."

The shed door creaked. Mateo—one of the youngest stewards, barely twenty—entered carrying a crate of bioluminescent markers, the kind Elena used during coral spawning. "For the perimeter," he said shyly. "If we need to guide the boats without radios."

Elena smiled despite the knots in her stomach. "Perfect. We'll lay them along the channel."

They moved down to the dock together, footsteps muffled on the weathered planks. The lagoon mirrored the first scatter of stars; distant fishing boats blinked on the horizon like low constellations. Elena shrugged into her wetsuit, the neoprene cool against her skin, and slipped the hydrophone cable over her shoulder. When she glanced back, the field station glowed warm in the dark. Through the open shutters she could see team members hunched over monitors, their silhouettes sharp against shifting graphs.

Aisha touched Elena's elbow before she stepped off the dock. "Remember—if you hear detonation charges being primed, surface and signal immediately. We can't outswim a shockwave."

"Understood," Elena said. Fear traced cold fingers along her spine, but purpose burned hotter. She squeezed Alon's shoulder. "Let's go."

\bigskip

Water closed over her like velvet. The lagoon's surface swallowed the drone of insects, replacing it with the muted rush of currents and the soft clink of dive gear. Elena's dive light carved a narrow tunnel through the dark, revealing swaying seagrass and startled parrotfish flashing emerald and cobalt before vanishing into shadow. Beside her, Alon's beam traced the contour of the limestone shelf that guarded the outer reef.

They swam in synchrony honed over decades of working the sea. Elena secured the first hydrophone beneath an overhang, fixing it with epoxy putty that hardened in seconds. The device's indicator light winked green, pulsing with the rhythm of the reef's ambient song. She imagined the soundscape layering in the data feed—shrimp crackle, fish chatter, and, if the rumors proved true, the telltale mechanical whine of improvised detonators.

At the edge of the drop-off, the reef sprawled like a city asleep. Coral heads rose in shadowed towers, some bleached bone-white, others still clinging to color. A school of jacks wheeled overhead, silver bodies catching the starlight filtered through the surface. Elena's chest tightened. She had promised these colonies another chance. Tonight the promise felt like a shield and a burden all at once.

She placed the second hydrophone near a fan coral unfurling like ink. As she worked, Alon drifted higher, scanning the channel. His light paused on a patch of coral rubble—fresh, jagged edges. He signaled the hand motion for "recent damage." Elena nodded, noting it for the report. She traced the fracture line with her gloved fingers, feeling the vibration of passing currents. The reef felt wary, braced.

They angled toward the channel mouth, where the lagoon breathed in and out through a narrow throat. Here the current quickened, tugging at Elena's fins. She wedged the final hydrophone between two stones and activated the transmitter. The device chimed faintly in her ear through the bone-conducting comms. Above, the ghost outline of the drone boat glided, its electric motor silent.

"Hydrophones live," Aisha's voice crackled in Elena's earpiece. "Signal strength solid."

"Copy," Elena murmured, bubbles trailing in silver strings. She reached for Alon's arm, and together they lingered, letting their lights fade to minimize detection. The dark enfolded them, alive with plankton that ignited at the sweep of their hands. For a heartbeat, Elena forgot the threat. This was why she had crossed an ocean—the quiet communion with a world most people never saw.

A low hum vibrated through the water. Elena stiffened. It wasn't the steady throb of legal fishing vessels. This sound was jagged, uneven—a generator cobbled together. Alon's grip tightened. He angled his light toward the open sea, but the noise vanished as abruptly as it had arrived, swallowed by distance.

"Did you catch that?" Elena whispered.

"Yes," Aisha replied. "Recording. They might be testing equipment. Stay alert."

Elena's lungs ached with the need for air. She tapped Alon's wrist twice—time to surface. They rose slowly, breaking the water near the mangroves. The night air pressed humid and thick, cicadas resuming their chorus. Across the lagoon, the drone boat's screen glowed, Leo hunched over the controls.

"Signal spike at zero-one-hundred degrees," Leo called quietly when they climbed aboard. "Pattern matches known blast rigs."

Aisha swore under her breath. "They're scouting the far sandbar. That's inside the protected radius."

Elena stripped off her mask, breath fogging in the night. "Let's set the markers along the channel. If they try to cut through, they'll light themselves up."

Alon nodded, already reaching for Mateo's crate of bioluminescent floats. They deployed them like a secret constellation, each orb glowing blue when it touched water. The channel transformed into a luminous artery, invisible from land but obvious to anyone in the lagoon. A warning. A promise that someone was watching.

\bigskip

Back at the field station, monitors bathed the command room in pale light. Acoustic spectrograms scrolled across screens like heartbeat charts. Nia leaned over the central console, braids coiled atop her head, eyes sharp.

"We picked up three motor signatures and one metallic clatter," she said as Elena toweled salt from her hair. "Sounds like they're loading charges."

Elena's skin prickled. "Can we triangulate their location?"

"Working on it," Leo replied, fingers flying across the keyboard. "Hydrophones give us bearings, but we need a second recording to confirm distance."

Aisha checked her watch. "The coast guard's night patrol is grounded until dawn—mechanical issue. Best they can do is stage a team an hour away."

"That's too late," Alon snapped. "The tide will slack near midnight. Perfect conditions for a blast."

Nia exhaled. "Then we stall them."

Elena glanced at the wall clock. In Marisport, it was late morning. Marco would be prepping the lunch rush. The thought steadied her. "We have the drone. We have markers. We have community liaisons who know every inlet. We can create a presence so thick they'll choke on it."

Aisha's lips twitched. "You always fight with theater?"

"With visibility," Elena corrected. "Bullies prefer shadows."

They divided tasks with the ease of a crew who trusted one another's strengths. Aisha and Leo prepped the drone for low-altitude surveillance, its infrared camera ready to catch heat signatures on the water. Alon coordinated with community volunteers via encrypted chat, assigning lookout points along the mangroves. Nia drafted a message to the municipal council, documenting the acoustic evidence in real time—paper trails that would matter in court.

Elena slipped onto the porch, dialing the satellite phone. The connection crackled before smoothing into the warm baritone she craved.

"Hey, sirena," Marco answered, voice wrapped in clinking cutlery and distant laughter. "You underwater?"

"Freshly surfaced," she said, letting the sound of him wash over the night's raw edges. "We're on blast-watch."

Silence hummed through the line. Then, soft but steady: "Tell me what you need."

"I need you to keep breathing," she said, throat tight. "And maybe distract me for thirty seconds."

"Ignacio burnt the morning batch of guava pastries," he reported immediately. "The whole café smells like campfire. Priya's here writing legal threats on napkins. Adrian just sent a video of the lab's turbine spinning for the first time. He labeled it `Baby's First Whirr'."

Elena laughed, the sound shaky but real. "Tell them all I'm proud."

"I will." Marco hesitated. "Stay safe."

"Trying," she whispered. "I'll call when it's over."

She hung up and pressed the compass against her palm, grounding herself in its steady weight. The night stretched taut, a wire ready to snap.

\bigskip

An hour later, the hydrophone feed spiked again. The sound this time was unmistakable—the metallic scrape of rebar against wood, followed by a low thud.

"That's a blast keg," Alon said, jaw clenched. "They're staging at Cove Seven."

Cove Seven. Elena pictured the map: a crescent of mangroves half a mile north, reachable only through a maze of narrow cuts. Perfect for smugglers. Perfect for ambushes.

"We can't wait for dawn," Aisha said. "We go now, document everything, and stay out of range."

Elena grabbed her waterproof notebook, sliding it into her dry bag. "I'll take the skiff with Alon. We can approach from the eastern channel—quiet."

"I'll fly the drone overhead," Leo said, already launching the craft from the dock. Its rotors whispered as it lifted, lights dimmed to near invisibility.

Nia handed Elena a small pouch. "Emergency flares. Only if you're spotted. We don't escalate unless we must."

The skiff cut through the lagoon with the engine barely above idle. Elena knelt at the bow, peering ahead while Alon navigated the mangrove labyrinth by memory. The night air smelled of brine and mud, thick with the musk of unseen birds. Once, the skiff brushed against a tangle of roots, the scrape loud as a gunshot in the quiet. They paused, listening. Only the drone of insects replied.

Cove Seven materialized as a pocket of open water walled by mangroves. A single boat floated near the far bank, its hull dark, silhouette low. Men moved aboard it—four, maybe five—hauling crates from shore. Elena raised her binoculars, the night-vision lenses painting the scene in ghostly green. She saw burlap sacks, metal pipes, coils of fuse. On the bank, a generator sputtered, wires snaking into the boat's hold.

She snapped photos through the binoculars, each click nearly silent. Beside her, Alon recorded audio, his microphone tuned to capture whispered orders. Voices drifted across the water in Tagalog. Elena caught fragments: "...drop point..." "...half the reef..." "...buyers waiting..."

Her stomach lurched. This wasn't subsistence desperation. It was organized extraction.

A branch snapped behind them. Elena froze. A flashlight beam swept the mangroves, slicing past their boat by inches. Someone patrolled the shoreline.

Alon's hand hovered over the throttle, muscles taut. Elena shook her head. Moving now would draw attention. Instead, she slipped into the water, silent as shadow, and pushed the skiff deeper into the roots. Mud sucked at her boots. Mangrove crabs skittered across her knuckles. The light passed again, closer. She held her breath until her lungs burned.

When the beam finally swung away, she dared exhale. Sweat slicked her palms despite the water. They waited five more agonizing minutes, capturing footage of the men loading cylindrical bundles into a net. Then, slowly, they backed the skiff out of the cove, using a pole instead of the motor until they cleared the narrow cut.

Back at the field station, they downloaded the footage. The grainy images were damning—faces clear, explosives unmistakable.

"This is enough," Nia said, sending the files to the coast guard commander. "They'll dispatch at first light."

"First light," Alon echoed bitterly. "They could blast in an hour."

Elena rubbed the bridge of her nose. "Then we keep pressure on."

\bigskip

In Marisport, the clock ticked toward midnight. Marco locked the café door and leaned against the counter, phone pressed to his ear. The audio Elena had sent—metal scraping, men whispering—hissed softly from his laptop. Priya sat beside him, laptop open to a legal form titled \textit{Affidavit of Acoustic Evidence}. Adrian paced near the window, restless energy bottled in tailored slacks.

"They're staging an attack on a reef under our alliance," Priya said. "We have standing to file an international complaint."

Adrian nodded. "Sterling's regional partners operate in the Philippines. I'll leverage every contract."

Marco's throat tightened. "Leverage won't stop an explosion tonight."

"No," Priya agreed, eyes softening. "But it builds a wall they can't climb tomorrow."

Marco stared at the compass hanging on the café's coat rack—the twin to Elena's, polished by years of fingers. He wished he could hurl it across the ocean like a lifeline. Instead he breathed, in and out, matching the rhythm of the recorded waves.

His phone buzzed. A photo from Elena appeared: blue orbs floating in dark water like captured stars. \textit{Channel is lit. Holding the line.} His heart clenched. He typed back: \textit{We're with you. Whole town's awake.} It wasn't literally true, but he knew if he called, a dozen volunteers would show up with laptops and prayers.

Adrian stopped pacing. "I just received a message from our Manila liaison. She says a shipping company named Blue Current Logistics has been supplying fuel to syndicates after storms."

Priya's eyes narrowed. "Blue Current... aren't they subcontracted by Tidefront?"

"They were," Adrian said grimly. "Until we cut Tidefront off. Looks like they're searching for new revenue."

Marco's stomach sank. The web stretched farther than any of them wanted to admit. He pictured Elena standing in humid darkness, confronting the latest mutation of greed. He whispered to the empty café, "Hold on."

\bigskip

The hours before dawn blurred into a litany of watch rotations. Elena paced the dock, eyes flicking between the horizon and the tablet streaming the hydrophone feed. Every surge of static tightened her shoulders. Around three a.m., Mateo stumbled out with mugs of ginger tea, his hair sticking up like kelp.

"You should rest," he told Elena, earnest and insistent.

She shook her head. "After the tide turns."

"The reef needs you strong," he argued. "Not half-asleep."

Elena softened. He reminded her of the high school volunteers back home, stubborn and soft-hearted. "Twenty minutes," she conceded. She curled on a deck chair, head resting against her folded arms, and let the soundscape lull her. In her half-sleep she dreamed of Marisport's lighthouse beam sweeping across the Philippine Sea, guiding her home.

A sharp chime yanked her awake. The tablet flashed red. The hydrophone feed registered a seismic tremor—small, but distinct.

"They're testing charges," Aisha said, appearing at Elena's shoulder as if conjured. "We have maybe thirty minutes before they move."

Dawn stained the horizon bruised purple. Birds stirred in the mangroves. Elena shrugged on her dive vest. "We intercept in the channel. Make it impossible for them to deploy without hitting us."

"That's dangerous," Nia warned.

"So is letting them obliterate the nursery," Elena countered. "We'll take the research barge. It's big enough to block their path."

Aisha's smile was sharp. "You really did build a resistance manual in Marisport, didn't you?"

"We call it community organizing," Elena said dryly.

They mobilized with practiced urgency. Volunteers boarded kayaks, paddling to key choke points. The research barge groaned as the winch lowered it into the water. Solar panels gleamed dull in the pre-dawn light. Elena took the helm, Alon handling the lines. The barge's engine rumbled as they positioned it across the channel entrance, anchors dropping with heavy splashes.

"Drone picked up movement," Leo called over the radio. "Boat leaving Cove Seven, heading your way. Five occupants."

Elena's heart hammered. She adjusted the barge's position, ensuring minimal gaps. The bioluminescent markers still glowed faintly, painting the water with ethereal blue.

The syndicate's boat emerged from the mangroves like a predatory fish. Its bow sliced through the water, engine growling. Elena could see the men now—faces set, eyes hard. One stood near the bow with a long pole. Another manned the motor, jaw clenched. Crates sat stacked midship, tarps hiding their lethal cargo.

"This channel is closed," Elena called, voice ringing across the water. "Protected zone."

The man at the bow laughed, a harsh sound. "Move or be moved."

"The coast guard is en route," Aisha added through a megaphone. "You have minutes to clear out."

"Lies," the man spat. "You foreigners think you own the sea."

"I'm not foreign," Alon said quietly, stepping to Elena's side. His voice amplified without shouting. "This is my home. Blast here and you poison your children's catch for years."

The man's gaze flicked, surprise rippling. "We do what we must to eat."

Elena raised the drone's live feed on her tablet, angling it so the men could see themselves, faces captured in high-definition, crates exposed. "And you sell the haul to buyers who don't even fish. We have you on record. Walk away."

For a heartbeat, she thought it might work. Then one of the men grabbed a flare gun, aiming at the barge.

"Down!" Aisha shouted.

The flare streaked across the gap, slamming into the barge's railing. Fire licked along the metal before extinguishing in the damp morning air. Elena's fear transmuted into fury. She slammed the throttle forward, grinding the barge closer until its hull scraped the mangrove roots. There was no path through now. Only a stubborn wall of community will.

The syndicate boat revved, inching closer as if to ram them. Elena held her ground. Sweat trickled down her spine. The compass pressed into her sternum like a brand.

A siren wailed in the distance. The men cursed, glancing over their shoulders. The coast guard cutter rounded the bend moments later, bow wake frothing. Officers leveled rifles, voices booming through loudspeakers.

"Vessel bearing registry number PC-731, cut your engine and prepare to be boarded!"

The syndicate's pilot hesitated too long. An officer fired a warning shot across the bow. The men raised their hands, fury etched deep. One kicked the crate nearest him. It toppled, a bundle rolling toward the water.

"No!" Elena lunged, grabbing the tarp before it slid overboard. The weight dragged her toward the edge. Alon caught her waist, hauling her back. Together they wrestled the crate upright. Sweat dripped into Elena's eyes. The smell of sulfur and oil assaulted her senses.

Coast guard officers boarded the syndicate vessel in a flurry of shouts and metal clanks. Within minutes, the men were cuffed, the generator shut down, the explosives secured. Elena sagged against the railing, adrenaline ebbing. Her hands trembled.

"You okay?" Aisha asked, breathless but grinning.

Elena nodded, though the word stuck in her throat. "We bought the reef time."

"And proof," Nia said over the radio. "Coast guard wants your statement immediately. Also, Manila news outlets are already calling."

Elena groaned. "Of course they are."

\bigskip

By midmorning, the field station buzzed with officials. Coast guard officers recorded witness statements. Local council members arrived with thermoses of coffee and eyes wide with relief. The confiscated explosives sat under tarps, guarded and inert for now. Elena recounted the night's events three times, each version more precise despite fatigue fraying her edges.

When the interviews finally ended, she slipped away to the shaded veranda, sinking onto the steps. The lagoon sparkled innocent under the noon sun. It was hard to reconcile the placid scene with the violence they had just averted.

Her satellite phone vibrated. Marco's face filled the small screen, smile soft. "You look like you fought a hurricane," he said gently.

"Feels like it," she replied. Her voice wobbled. "We stopped them. Coast guard took them into custody."

He exhaled, relief palpable even through the lag. "I'm so proud of you."

"I wanted to cry and throw up simultaneously," she admitted.

"Sounds about right." His smile turned wry. "Priya's drafting statements for the press in case they spin it. Adrian's calling Blue Current's board with lawyers on the line."

"Tell them thank you," she whispered. "And you?"

"I'm making sure the café staff eats," he said. "And I started the `While She's Saving the World` playlist you made last year. It still slaps."

Elena laughed softly. "I miss you."

"I miss you more," he said. "Call me when you need to fall apart."

"I might need that soon," she replied. They lingered in silence, the kind that held them even across oceans. When they hung up, Elena pressed the phone to her chest, breathing through the swell of homesickness.

A shadow fell across the steps. Alon sat beside her, handing over a plastic container. Inside, sticky rice wrapped in banana leaves glistened. "From the council," he said. "They said heroes need breakfast."

Elena managed a tired smile. "Share with me?"

He nodded. They ate in companionable quiet, watching the lagoon. After a few bites, Alon cleared his throat. "Those men... I recognized one. He used to fish with my cousin."

"Desperation makes people vulnerable," Elena said softly.

"And greed guides them," Alon countered. "We need to offer another tide to ride."

"We'll build it," she promised, though the path ahead loomed steep. Her mind spun with possibilities—alternative livelihoods, reef stewardship stipends, partnerships with eco-tourism cooperatives. Each idea required time, funding, trust. She squared her shoulders. One fragment at a time.

\bigskip

That afternoon, the community council convened an emergency assembly in the village hall. Ceiling fans stirred heavy air, their whir blending with the murmur of voices. Fisher families filled the benches, faces etched with worry and curiosity. At the front, Alon stood beside Elena and Aisha, their presence both shield and lightning rod.

Mayor Cruz banged a gavel. "We gather today because illegal blast fishing nearly destroyed our reef this morning. Thanks to our partners, it was stopped. But we must decide how to protect our waters moving forward."

Murmurs rippled. A wiry man in his forties rose. "We fish because we must eat. Outsiders bring money, but when storms come, they vanish."

Elena stepped forward, palms open. "I am not here to replace your knowledge. I'm here to invest in it. In Marisport, we rebuilt after a hurricane because fishers led the response. We secured stipends for patrols, funded by the very developers who caused the damage. We can pursue similar restitution here—make those who profit from destruction pay for restoration."

A woman cradling a toddler stood. "Restitution takes time. Hunger does not."

Aisha cleared her throat. "The Collective can expand our emergency relief fund. Immediate, no-interest microgrants for fishers who agree to join reef guardianship. In exchange, we offer training in sustainable harvest methods, tourism guiding, coral nursery work."

Skepticism flickered. Elena felt it like a physical weight. She glanced at Alon. He nodded, stepping forward.

"I was born on this shoreline," he said. "I've seen blast fishing destroy our future. These partners crossed oceans because they believe in us. We hold them accountable, yes. But we also hold ourselves accountable. No more excuses."

Silence fell, thick and charged. Then the wiry man sighed. "What do you need from us tonight?"

Elena lifted her notebook. "A roster of fishers willing to patrol with us. Stories we can bring to Manila to demand funding. Ideas you trust."

Hands rose slowly, then faster. Names filled the page. Commitments, fragile but real, took shape. Elena's chest ached with gratitude. This is what rebuilding looked like—uncertain, communal, stubbornly hopeful.

\bigskip

As dusk settled again, fatigue crashed over Elena in waves. She retreated to the lab to log the day's data. The room smelled of salt and soldering flux. Screens displayed hydrophone recordings, drone footage, legal documents. She uploaded everything to redundant servers—Marisport, Manila, Boston—layers of protection against erasure.

A notification pinged. An email from Priya: \textit{Tidefront execs attempting to downplay Blue Current ties. Adrian and I pushing for international inquiry. Rest. Proud of you.}\

Another message blinked from an unknown sender. Subject: \textit{We need to talk about your reef.}\ When she opened it, a single sentence waited: \textit{You stopped one boat. There are others coming—with better funding. Meet me where the mangroves open to the sea at moonrise if you want names.}\ The sender ID was a string of numbers.

A chill skated down Elena's spine. She forwarded the email to Aisha and Nia immediately. Within seconds, Aisha appeared in the doorway.

"Trap?" she asked.

"Maybe," Elena said. "Maybe a frightened crewmember."

"We don't go alone," Aisha stated. "And we alert the coast guard."

"They'll take hours," Elena argued. "If this is a lead, we can't let it slip."

Aisha crossed her arms. "You realize this is how horror stories begin."

"Horror stories begin when we ignore warnings," Elena countered. "We set terms. Public place, eyes everywhere."

Nia joined them, expression tight. "If we go, we go prepared. No heroics."

Elena nodded. Her heart pounded, a different rhythm now—anticipation laced with dread. The day's victory had peeled back a larger threat. She could feel it looming like a storm beyond the horizon.

\bigskip

Moonrise painted the lagoon in silver. Elena, Aisha, and Alon waited near the mangrove opening, headlamps off, ears attuned to every rustle. Mateo sat fifty yards back with a radio, ready to summon help. The compass lay against Elena's pulse, steadying her shaking fingers.

A figure emerged from the shadows—a young man, barely older than Mateo, clothes soaked. He kept his hands raised. "Don't shoot," he whispered.

"We don't have guns," Aisha said dryly. "You have sixty seconds."

The young man's eyes darted between them. "My brother was on that boat. They made me stay behind to watch the fuel. He called from the coast guard cell. He said the buyers will just hire another crew. Bigger boats. They talked about a shipment coming in three days, at the old airstrip north of here. Blue Current logo on the crates."

Elena's stomach twisted. "What kind of shipment?"

"Industrial charges. Enough to take out the entire reef," he said, voice breaking. "The buyers are paying triple. They said once the reef is gone, they can dredge the channel deeper for cargo ships."

Dredge the channel. Elena's mind flashed to Tidefront's plans in Marisport—deep-water docks masquerading as revitalization. The web tightened.

"Why tell us?" Alon asked quietly.

"Because my brother cried," the young man said, tears streaking his face. "He said the reef is the only thing that keeps the storms gentle. If we destroy it, our village dies."

Elena stepped closer, keeping her voice gentle. "Do you have proof? Names?"

He nodded, pulling a crumpled piece of paper from his pocket. Coordinates scrawled across it, along with three names. One leapt out at Elena like a striking eel: \textit{Harlan Vance}. Tidefront's former project manager, the man who had smirked through depositions in Marisport.

Her pulse roared in her ears. "Thank you," she said. "We'll get you protection."

The young man shook his head. "I have to disappear." He backed into the mangroves, swallowed by darkness before they could argue.

Elena stared at the coordinates, the ink smudged but legible. A storm rumbled beyond the horizon. She felt its pull all the way across the world.

Aisha blew out a breath. "Looks like our fight just leveled up."

"And spread," Alon added grimly.

Elena clenched her fist around the paper. She pictured Marco in the café, Priya in city hall, Adrian navigating boardrooms. Their battles had always been intertwined. Now the line connecting Marisport and Palawan glowed fierce.

"We need to warn them," she whispered, already dialing. The phone rang, connecting across oceans. When Marco answered, she didn't waste time.

"Harlan Vance is here," she said. "And he brought the war with him."

Silence crackled, electric. Then Marco's voice, steady despite the shock: "Then we fight on two fronts."

Elena looked at the moonlit lagoon, its calm surface belying the turbulence beneath. The compass thudded against her heart, pointing north, pointing home. Somewhere beyond the horizon, forces gathered. The tide was rising, and none of them could afford to stand still.

The night held its breath once more, waiting for the next wave.

\noindent\textit{Reflection: Tonight's confession from a frightened brother confirmed what my gut already knew—the forces threatening Palawan and Marisport are the same tide wearing different masks. Hearing Harlan Vance's name echoed across oceans lit a fire I thought hurricanes had already stoked to its limits. From here on, every plan has to assume the fight is global and personal at once.}
