\chapter{Low Tide}

The morning tide crept low over Marisport like a held breath, revealing veins of barnacled rock that usually hid beneath the glitter of the bay. Elena Ruiz stood barefoot on the damp dock planks behind the Marisport Marine Institute, wetsuit peeled to her waist, fog rising in white tendrils around her shoulders. Dawn brushed the horizon with color, the faintest lavender melting into gold, and the gulls were only beginning to quarrel themselves awake. For a suspended heartbeat the town seemed to belong solely to the sea and to her.

"You good down there?" Talia's voice floated from the skiff, light as a gull's wing. The graduate student balanced a clipboard and a thermos in one hand while trying to coil a stubborn length of rope with the other.

"Give me five more minutes," Elena called back, sliding the rest of the suit over her shoulders. The neoprene clung to her skin like a second tide. "I want to reach the nursery pods before the sun crests."

Talia made a face. "You sound like the sunrise waits for you."

"Sometimes it does." Elena grinned, the expression easier in the salt air. She tucked a loose strand of hair beneath her cap, sealed the collar at her throat, and took a moment to scan the bay. Beyond the mouth of the harbor, fishing boats were only beginning to stir. The Lighthouse Café's chimney, two piers down, exhaled its first breath of coffee smoke. Even the lighthouse itself, white tower cutting the pastel sky, seemed caught in a languid yawn.

She stepped into the skiff, the boat rocking gently under her weight, and accepted her fins from Talia. As the motor coughed to life, the sound of Marisport thinned, replaced by the fizz of saltwater against aluminum hull. Elena braced her knees and watched the dock recede, the Institute's weathered shingle siding fading into the fog. Out here, with the wind combing her face and the brine stinging her lips, she could almost forget the paperwork piled on her desk, the grant proposals waiting for revision, the Save the Reef fundraiser brochures still in draft. The ocean was immediate, demanding, merciful in its clarity.

"You're sure you don't want backup?" Talia asked when they reached the first buoy. The student's grin had faded into a seriousness Elena recognized: the reverence of someone who had seen damage they couldn't fix quickly enough.

"I'll be fine. Logging coral polyp growth isn't exactly a two-person job." Elena clipped the tether to the buoy, scanned her checklist, and met Talia's gaze. "But keep the radio clear in case the current decides to pick a fight."

"Got it. And Elena?" Talia hesitated, fingers drumming against the thermos. "Coffee will be waiting."

"That's the best incentive you could offer." Elena settled her mask over her face, let the strap snap into place. The world narrowed to the edges of the tempered glass, the taste of silicone on her lips. She filled her lungs, rolled backward over the gunwale, and surrendered to the water.

The sea embraced her with cold arms. Sound distorted into a muted roar, the surface a shimmering sheet overhead. Elena kicked downward, ears popping, bubbles feathering past her cheeks. Light filtered green and gold around her, refracted into wavering ribbons that danced over the spine of the reef.

She hovered above the coral nursery they'd installed three seasons ago, a grid of metal frames anchored into the seabed. Suspended from the structures like chandeliers hung branching fragments of staghorn coral—fragile, luminous bone structures that swayed with the pulse of the tide. Tiny fish flitted between them, flashes of cobalt and tangerine, scales catching the dawn. She checked the cable ties, noted the growth spurts, recorded them on the waterproof slate strapped to her forearm. Every centimeter mattered. Every thriving branch meant the reef was inching toward resilience.

When she reached the third frame, she paused. A section of coral near the base wore a bloom of sickly brown algae, a warning flare against the pale blue. Elena bit back a curse. The algae meant heat stress or pollution or something insidious she hadn't accounted for. She brushed it gently with a gloved finger, mindful not to damage the polyps. The algae smeared but clung. She scribbled on her slate: Sample needed. Monitor weekly.

She spent forty minutes among the coral, cataloguing growth nodes, adjusting the solar-powered pumps that circulated cooler water through the nursery. The tasks were rote yet demanding, the underwater equivalent of tending a delicate garden. Her muscles settled into a rhythm, mind empty but for the pulse of observation. When her tank edged toward its reserve line, she ascended slowly, hands trailing through columns of bubbles that sparkled like champagne.

The world exploded back into sound when her head broke the surface. Gulls screeched. The distant rumble of a fishing trawler drifted across the bay. Talia waved from the skiff, her relief visible even from ten yards away.

"You were down there forever," Talia called as Elena swam the last stretch. "I was about to come drag you up."

"Don't let the reef hear you calling it boring," Elena said, hauling herself over the side. Water streamed from her suit, pooling in the bottom of the boat. She peeled the mask from her face, blinking against the brightness. The sun had fully risen, washing the world in gold. "Besides, I found algae bloom on Pod Three. We need to increase the flow rate and maybe adjust the nutrient mix."

"That's our third bloom this month." Talia's brow furrowed. "Could the outflow from the west dock be drifting this far?"

"If it is, they're in violation of their permit." Elena reached for her towel, scrubbing her hair dry. The breeze caught the damp strands and braided salt into them. "I'll check the current data when we get back. And maybe pay the dockmaster a friendly visit."

Talia snorted. "Your version of friendly makes grown men sweat."

"Only when they're dumping bilge into protected waters." Elena's smile didn't reach her eyes. The day had begun beautifully, but the algae's presence was a grit in her shoe she couldn't shake. She glanced toward the harbor mouth. The lighthouse towered over the channel, stalwart and watchful, but even that familiar silhouette felt loaded with expectation.

They motored back toward the Institute, the skiff cutting through the bay with gentle lurches. Elena watched the town come alive: fishermen tossing nets, kids racing bikes along the boardwalk, tourists in pastel windbreakers pointing at seals like they'd discovered aliens. The scent of coffee and cinnamon drifted from the Lighthouse Café.

When they docked, Elena helped Talia haul the gear onto the weathered planks. The Institute building loomed behind them, cedar shingles silvered by salt, windows rimmed in peeling teal paint. An anchor, half-buried in the lawn, served as both decoration and statement of purpose. Inside, the corridors smelled faintly of seaweed and printer toner.

"I'll rinse the suits," Talia offered, wrestling the tank cart toward the hose station. "You go make that algae report before you forget."

"As if I could forget." Elena slung her gear bag over her shoulder and climbed the wooden steps, each creak tuned to a note she'd known since childhood. The Institute had been her refuge when the world outside felt too small. She'd measured summers by the number of dives logged in these waters, had mapped her adolescence by the progression from volunteer to intern to researcher to lead marine biologist. The walls held photographs of team members past and present, and among them a faded print of her younger self, sunburned and grinning beside a coral transplant, Marco's arm draped over her shoulders.

The memory tugged at her in unexpected ways. She shook it off and made for her office.

Her desk was a battlefield of spreadsheets, environmental impact statements, and a half-eaten granola bar fusing to its wrapper. A whiteboard dominated the opposite wall, crammed with timelines: grant deadlines, volunteer orientations, the upcoming Reef Revival Gala they'd been planning for six months. At the corner of the board hung a Polaroid of Marco pouring latte art shaped like a seahorse. Elena touched the edge of the photo, a habitual caress, before switching on her computer.

She drafted the algae report with the swift efficiency of someone used to documenting every anomaly. She attached photos, cross-referenced last week's water temperature readings, flagged potential compliance issues. By the time she hit send, the granola bar had turned to paste in her mouth, and her inbox had populated with new demands: a message from the Marisport City Council reminding her of the partnership presentation next week, three emails from volunteers asking if they could bring friends to the reef clean-up, and a fundraising update that made her stomach drop.

Projected goal: \$150,000.

Current pledges: \$47,230.

She blew out a breath. The Reef Revival Gala had to succeed, or the Institute would be forced to scale back the restoration project—the thought of leaving sections of the reef to fend for themselves felt like betrayal. She clicked open the spreadsheet attached to the fundraising email, scanning the list of donors. The Sterling Foundation occupied a blank line, a ghost entry she'd been dancing around for weeks.

Elena leaned back, chair groaning beneath her. The Sterling Foundation had funded projects across the eastern seaboard, from oyster reef rebuilds to tidal energy research. They were, by all accounts, generous and strategic. They also bore the surname that had once been spoken in Marisport with equal parts admiration and disdain.

Adrian Sterling had been her best friend until he wasn't. The memory of his laughter still existed somewhere in her bones, but it was layered over with the sharp tang of his family's scandal, the night they'd left Marisport like thieves in the dark. She had watched his taillights disappear down Ocean Avenue and had taught herself not to expect apology. For ten years she succeeded. And then, three weeks ago, the Sterling Foundation's regional director had called to request a meeting.

She hadn't responded yet. Every time she drafted an email, her fingers froze over the keys. What would she even say? Dear Mr. Sterling, thank you for your offer. Please confirm whether you're the same boy who promised to build me a glass-bottom boat and then vanished. She rubbed her temples until stars danced behind her eyelids.

A knock sounded at her open door. Elena straightened as Dr. Priya Singh, the Institute's director, leaned against the frame. Priya's silver-streaked hair was piled in a loose knot, her expression equal parts exhaustion and mischievous glee.

"Tell me you found something miraculous," Priya said without preamble.

"Define miraculous." Elena gestured to her screen. "If algae blooms count as miracles now, then yes."

Priya sighed. "At least it gives us another bullet point for the grant narrative. 'Local industry threatens delicate reef ecology; your funding can help us fight back.'"

"I hate couching catastrophe as an opportunity," Elena muttered.

"So do I. But donors love a villain, and we'd rather point to bilge pumps than the slow boil of climate change." Priya stepped into the office, lowering herself into the chair opposite Elena's desk. "Which brings me to the real reason I'm here."

Elena braced herself. "If it's about the Gala budget, I'm already on it."

"It's not." Priya folded her hands, her gaze keen. "It's about the Sterling Foundation. They're sending someone to tour the facility this afternoon."

Elena's pulse stumbled. "They confirmed?"

"Confirmed and insisted on today. I would have looped you in sooner, but their regional director only called an hour ago." Priya's lips twitched. "Apparently the new CEO is passing through Marisport and wants to see the project firsthand."

It took a moment for the words to register. "The new CEO," Elena repeated. "As in—"

"Adrian Sterling himself," Priya finished gently. "He's landing at noon. I thought it best you hear it from me before the rumor mill does its worst."

Elena's stomach flipped, as though the boat had pitched beneath her. Ten years. Ten years of carefully rerouted thoughts, of learning how to breathe around the space he'd once occupied. She had built a life, a future, a partnership. And now he was returning, not as the boy who left, but as the head of an empire whose philanthropy could save their reef.

"We can reschedule if you need time," Priya offered, misreading her silence.

"No." The word left Elena's mouth before she could temper it. "If the Sterling Foundation is willing to invest, we can't afford to delay."

Priya nodded slowly. "We'll give him the tour together. But Elena—" She leaned forward, the steel in her eyes softened by worry. "Are you all right?"

Elena considered lying. It would be easy to shape her mouth into a smile, to pretend the past was as distant as the horizon. Instead, she said, "I'll be fine once I get some coffee."

Priya's chuckle filled the room like sunlight. "Then go to Marco. He called earlier asking if you were stopping by."

Of course he had. Marco always seemed to know when she needed anchoring. Elena gathered her bag, tucked the Sterling file into her satchel, and headed downstairs.

Marisport's main street unfurled along the harbor like a ribbon of color. Shops painted in cheerful hues—turquoise, coral pink, bright yellow—perched on stilts above the boardwalk. Fishermen's nets hung to dry, fluttering in the breeze like flags. The salty air carried hints of fried cod, caramel, and the tang of tar from freshly patched hulls. Elena walked past the ferry terminal, past the art gallery displaying ocean-themed oils, until the familiar red-and-white awning of the Lighthouse Café came into view.

Behind the counter stood Marco Alvarez, sleeves rolled to his elbows, the tattoo of a compass on his forearm peeking through foam. His dark curls fell into his eyes as he poured espresso with practiced precision. When he looked up and spotted Elena, his face broke into a smile that crinkled the corners of his eyes—the smile that had once convinced her that staying in Marisport didn't mean surrendering her dreams.

"There she is," he called, sliding a latte toward a waiting customer. "Fresh from saving the ocean, or from wrestling it into submission?"

"Today it tried to throw algae at me," Elena said, weaving through the crowd. She leaned over the counter to press a kiss to his cheek, the stubble rough against her lips. His skin smelled faintly of citrus and coffee. "I might need something stronger than caffeine."

"Lucky for you, we serve emotional support muffins." He waggled his eyebrows and set a blueberry muffin on the counter. "On the house."

"If you keep feeding me like this, I won't fit into my wetsuit." She took a grateful bite, the tart berries bursting sweet juice.

"I'll start a new line: elastic wetsuits," he said, then lowered his voice. "You all right? You look like you're bracing for a storm."

Elena exhaled, the sound slipping out before she could control it. "Priya just told me Adrian Sterling is coming by the Institute this afternoon."

Marco's hands stilled around the espresso tamper. For a heartbeat his expression was unreadable. Then he set the tamper down, his smile carefully measured. "The Adrian Sterling?"

"Apparently he's the Foundation's new CEO."

Marco's mouth twisted. "I thought he ran as far from Marisport as he could." He resumed his motions, tamping espresso with a little more force than necessary. "Guess money has a way of forgiving geography."

"This isn't about the past." Elena heard the defensiveness in her tone and winced. "We need funding. The reef—"

"I know," Marco interrupted gently. "I know how much this means to you." He slid a latte toward her, the foam etched into a perfect fern. "I just want to make sure he doesn't walk in and turn your world upside down again."

"He won't." Elena wrapped her hands around the warm cup, letting the heat seep into her palms. "I'm engaged now. My life is here."

Marco's gaze softened. He brushed his fingers over hers, the contact grounding. "Damn right it is."

"Are you coming by tonight?" Marco asked, voice casual but eyes searching. "Mom wants to finalize the guest list for the engagement party."

Elena grimaced. "Do we have to talk about centerpieces?"

"Apparently it's non-negotiable. She's been pinning 'nautical chic' ideas all week." He made air quotes, his grin returning. "If we're not careful, she'll turn the café into a ship's deck."

"As long as she doesn't make everyone wear sailor hats." Elena chuckled. The idea of the engagement party always brought a ripple of nerves. Celebrating their commitment publicly felt both joyous and exposed, like inviting the entire town to inspect the seams of their relationship. Still, Marco's excitement was infectious. "I'll be there after the Sterling tour."

"Good." He leaned across the counter to kiss her properly this time, the world narrowing to the warmth of his mouth, the familiar electric current that hummed between them. When they broke apart, a teenager wolf-whistled. Marco flipped him a towel without looking. The café erupted in easy laughter.

Back at the Institute, the day blurred into a series of tasks. She met with the volunteer coordinator to finalize the beach clean-up logistics, reviewed water quality reports, and fielded a call from the local radio station requesting an interview. She moved through it all with mechanical precision, her mind split between the algae bloom and the impending arrival of Adrian Sterling.

At eleven-thirty, Priya appeared in her doorway again. "He just texted," she announced. "ETA twenty minutes."

Elena stood, smoothing her hair, wishing she had worn something less practical than a navy polo and khaki field pants. The shirt bore the Institute's logo: a stylized wave encircling a coral branch. It felt like armor. She glanced at the Polaroid of Marco, then tucked it into the top drawer. She wasn't sure if she was protecting the photo from the past, or the past from the photo.

They met in the lobby, its walls adorned with maps of the bay, framed photographs of reef ecosystems, and a glass display case housing coral skeletons. The scent of salt clung even here, mingling with the faint musk of old books. Priya straightened a stack of brochures and gave Elena a once-over.

"Ready?" she asked.

"Define ready." Elena forced a smile. "Do I look like someone about to woo a billionaire philanthropist?"

"You look like someone who knows exactly what she's doing," Priya said. "And that's more valuable than any gala gown."

The glass doors whooshed open as a breeze swept in, carrying the faint rumble of a high-end car engine. Elena's heartbeat accelerated. She told herself it was because potential funding walked through those doors. The story she spun for herself did not account for the figure who stepped into the lobby, eyes scanning, shoulders squared.

Adrian Sterling was both familiar and unfamiliar. Gone was the lanky teenager who'd trailed her along the docks, hair perpetually tousled by salt spray. The man before her wore a tailored charcoal suit that managed to look both crisp and relaxed, the jacket unbuttoned. His hair was shorter, the gold threaded through dark waves, his jaw sharper. Yet his eyes—sea-glass green, flecked with amber—were the same. They landed on Elena, and for a moment the air between them thickened.

"Priya Singh," he said, extending a hand. "Thank you for accommodating me on such short notice."

"Mr. Sterling, welcome to the Marisport Marine Institute." Priya shook his hand, her professionalism a steady tide. "This is Elena Ruiz, our lead marine biologist and the architect of the reef restoration project."

Adrian's gaze lingered on Elena. "Architect," he echoed softly. "That's fitting." He stepped toward her, hand outstretched. "Elena."

Her name in his mouth was a tide she hadn't anticipated. Elena forced her hand to meet his. His grip was warm, firm, the contact sending an unwelcome shiver up her arm. "Mr. Sterling," she said, the formal address a shield.

He smiled, a quick flash that tilted the corners of his mouth. "It's Adrian."

"We're honored by your interest," Priya interjected smoothly. "Shall we begin the tour?"

They moved through the Institute's corridors, Elena reciting facts with practiced ease. She showed him the lab where they cultured coral fragments, the tanks where juvenile fish acclimated before release, the data center that tracked ocean temperatures. Adrian asked pointed questions about metrics, longevity, community involvement. His attention was sharp, his focus genuine. If he felt any personal history haunting the hallways, he didn't show it.

"Our coral nursery has seen a thirty-two percent increase in growth since we installed the cooling pumps," Elena said as they paused by a series of monitors displaying real-time reef footage. "But the algae blooms are worrying. We need to expand the filtration system and work with local industry to mitigate runoff."

"And that's where the funding gap lies?" Adrian asked.

"Partially. The expanded system requires new infrastructure, and maintenance isn't cheap." Elena folded her arms. "We're also investing in community education. Restoration isn't sustainable unless the town understands what's at stake."

Adrian nodded. "I read your proposal. The outreach component impressed me. Not enough projects factor in cultural stewardship." He glanced at her, something like admiration flickering. "You always were the one reminding me that the ocean isn't just data points."

Elena's throat tightened. "You read the proposal personally?"

"I insisted." Adrian's smile was rueful. "Marisport deserves more than a cursory glance."

They continued to the observation deck overlooking the bay. The glass wall framed the water, now dotted with sailboats. The sunlight painted the waves silver. For a moment, silence settled among them.

"It's changed," Adrian murmured, eyes distant. "And yet—"

"The tide still comes in," Elena finished before she could stop herself. It had been their phrase once, whispered whenever they needed reassurance that even the worst days would ebb.

Adrian's gaze snapped to hers. The shared memory hung between them, fragile as a spun shell. Priya cleared her throat gently, reminding them of her presence.

"The Institute's mission aligns closely with the Sterling Foundation's new initiatives," Adrian said, recovering. "We're shifting focus toward long-term community partnerships. One-time donations don't cut it anymore."

"We're looking for partners, not patrons," Priya replied. "Our goal is to make this reef self-sustaining, which requires years of investment."

"Agreed." Adrian's attention returned to Elena. "I'd like to discuss specifics. Perhaps over lunch?"

Elena hesitated. Sharing a meal felt dangerously intimate, a step beyond professional courtesy. Yet refusing could jeopardize the project. She caught Priya's eye. The director's subtle nod was both encouragement and warning.

"We can meet at the Institute conference room," Elena suggested, opting for neutral ground.

Adrian inclined his head. "Of course. I'll have my assistant send over the framework we're considering." He glanced out at the bay again, expression unreadable. "It's good to see Marisport fighting for its reef."

"We never stopped," Elena said softly.

After he left, promising to return at two with preliminary figures, the lobby seemed to exhale. Priya turned to Elena, eyebrows raised.

"You handled that well," she said. "Despite the...history."

Elena let out a breath she hadn't realized she'd been holding. "History doesn't matter if it gets in the way of the reef."

"Doesn't it?" Priya asked gently.

Elena didn't answer. Instead, she retreated to her office, closing the door behind her. Her reflection stared back from the window: eyes wide, shoulders tense. She pressed her forehead against the glass, letting the coolness steady her.

The afternoon unfurled in a blur of planning. Adrian returned with a comprehensive outline of a multi-year funding partnership, contingent on matched community contributions and measurable benchmarks. He spoke of renewable energy initiatives, of transforming Marisport into a model for sustainable coastal communities. Elena listened, scribbling notes, heart hammering. The potential was staggering. So was the risk.

"We'd be in this together," Adrian said at one point, his voice low. "Our names side by side on every report, every news article."

The words lodged in Elena's chest. She imagined the town whispering. She imagined Marco's jaw tightening. She imagined the reef glowing healthy, unthreatened by algae blooms. Duty warred with the personal. In the end, duty won. She agreed to draft a revised proposal for their partnership, to be presented to the Institute board and the city council within the week.

By the time Adrian left, dusk was painting the sky in streaks of rose and violet. Elena lingered on the observation deck, watching the tide roll in. Her reflection blended with the sea beyond the glass. She could almost see the ghost of her younger self pressed against the window, dreaming of saving the world.

"Elena." Priya's voice broke the spell. "You should go. Marco's mother will hunt you down if you're late."

Elena huffed a laugh. "Do you ever go home?"

"Eventually." Priya squeezed her shoulder. "You did well today. Regardless of what happens next, you kept the focus where it belonged."

"On the reef," Elena said.

"On the future," Priya corrected gently.

Outside, the evening air wrapped around her like a shawl. The harbor glittered with lights, reflections rippling like scattered coins. She walked the familiar path toward the Lighthouse Café, her steps slowing as she approached. Laughter spilled from the open doors, mingled with music—Mateo strumming his guitar in the corner, by the sound of it.

Inside, the café had been transformed for the engagement planning meeting. Tables pushed together, covered in navy cloth with jars of fairy lights. Marco's mother, Isabela, presided over a spread of empanadas and ceviche. She bustled over as soon as Elena entered, enfolding her in a hug that smelled like cinnamon and comfort.

"¡Mi sirena!" Isabela exclaimed, pulling back to study Elena's face. "You look tired. Sit, eat. We need you strong for centerpiece debates."

"I'm not sure I'm emotionally prepared," Elena confessed, though her smile came easier now. Marco appeared at her side, slipping an arm around her waist. He kissed her temple, the gesture instinctive, claiming.

They spent the next hour debating seating charts and menu options, Isabela jotting notes with decisive strokes. Marco interjected jokes to keep the mood light. Mateo contributed by insisting on live music. Elena listened, chimed in, let herself be carried by the current of family. Yet even as she laughed, the day pressed against her ribs. Adrian's voice echoed. The reef's needs loomed.

When the meeting wound down, Marco pulled her onto the patio overlooking the harbor. The night air was thick with salt and possibility. Boats bobbed like sleeping creatures. The lighthouse's beam swept across the water, rhythmic, steady.

"You were quiet," Marco said softly.

"Long day." Elena leaned against the railing, the wood cool against her forearms. "Adrian wants a partnership. Multi-year, comprehensive. It could secure the reef's future."

Marco stared out at the water. "And put his name next to yours on everything."

"It's not about names." Elena turned to face him. "It's about the work."

"Maybe to you." Marco's voice held no accusation, but the hurt threaded through it was palpable. "To the town? To my mother, who's still mad about what his family did to hers?" He scrubbed a hand over his face. "To me?"

Elena's chest tightened. "Marco, I love you."

"I know." He met her gaze, eyes dark, vulnerable. "I don't question that. I just..." He exhaled slowly. "When he left, you were shattered. I spent months helping you find pieces of yourself again. The idea of him walking back in, even for something good—it scares me."

She stepped closer, pressing her palm to his chest. His heartbeat thrummed beneath her fingers. "I'm not that girl anymore. I'm not waiting for him. I'm choosing us. And I'm choosing the reef, because it's bigger than any of us." Her voice wavered. "I need you with me on this."

Marco covered her hand with his. "I'm here." He swallowed. "I just need to figure out how to be okay with sharing you—with your work, with the town, with your past."

They stood in silence, the lighthouse beam sweeping over them, painting their faces in alternating light and shadow. Elena rested her head against his shoulder, eyes on the horizon where the sea met the night.

Far off, a yacht's silhouette glided toward the marina. Elena's phone vibrated in her pocket. She pulled it out, expecting a text from Priya or perhaps a volunteer. Instead, an unfamiliar number flashed on the screen. A voice mail notification blinked.

Curiosity prickled. She pressed play, the speaker muffled against the night sounds.

"Elena," a voice said, low and warm and achingly familiar. Adrian. "Thank you for today. I know it wasn't easy. I'd like to talk more—about the project, about Marisport. There's...history between us that I don't want to ignore. I'll be at the old pier tomorrow at sunrise. If you want to meet, I'll be there. If not, I'll take that as my answer."

The message ended with the faint crash of waves in the background, as if he'd recorded it by the shore. Elena stared at the phone, the world tilting. Sunrise. The old pier where they'd once carved their initials into the railing. The past unfurling like a tide.

Marco's arm tightened around her waist. "Everything okay?"

Elena slipped the phone back into her pocket, pulse pounding. She looked out at the dark ribbon of the old pier, barely visible beyond the harbor lights. The tide was rising, relentless.

"Yeah," she lied, voice barely above a whisper. "Just another wave coming in."

She wasn't sure if she would let it break over her—or if she'd plant her feet and let it crash elsewhere. The night wrapped around them, thick with salt and promise. Somewhere beyond the harbor, dawn waited, holding its breath.

\noindent\textit{Reflection: The night ended with the lighthouse sweeping across more than the harbor; it exposed how the reef, my family, Marco, and even Adrian's returning voice are all currents tugging at the same heart. Standing on that patio, I felt the cost of inviting the past back into our work, yet I also sensed how refusing the tide would leave the reef unguarded. I need to remember that choosing the partnership means choosing to keep redefining loyalty before the next wave hits.}
