\chapter{Moonlit Bearings}

The Rotterdam call unspooled with the sterile chill of boardrooms Elena had learned to endure. On the screen, Tidecraft's chairwoman appeared as a blurred silhouette, voice clipped and incredulous. "These allegations are unfounded," she insisted. "Our auditors assure us—"

"Your auditors missed wire transfers to shell shipping companies disguised as art acquisitions," Priya interrupted, tone scalpel-sharp. "We have the ledger."

Adrian leaned forward, eyes icy. "And I can confirm from Sterling board records that Deep Chroma never commissioned the installations your filings reference. Money left, nothing arrived."

Elena watched the woman's composure crack. "This is a misunderstanding," the chairwoman tried again.

"The misunderstanding is believing we won't drag you into daylight," Elena said quietly. Her voice carried the calm of a slack tide moments before it surges. "Return the siphoned funds. Cooperate with federal investigators. Or watch the Geneva summit become a tribunal."

The silence that followed felt like held breath. Finally, the chairwoman relented. "We'll cooperate." The words tasted sour even through speakers.

When the call ended, Priya slumped back, pinching the bridge of her nose. "One domino," she said. "Dozens left."

"Navarro won't fold that easily," Adrian warned. "She'll throw lesser names to the tide and claim ignorance."

"Then we dig faster," Elena replied. The compass lay against her sternum, metal warm from the heat of the room. "Geneva can't be a stage for her lies."

Outside, rain slicked the boardwalk, turning planks into mirror. The storm had rolled in off schedule, fat drops drumming on the lab's windows. Elena stepped onto the covered walkway, inhaling petrichor mixed with salt. The reef would be awash with fresh water, sensors blinking warnings. Her muscles ached for immersion, for the honest resistance of tides against skin.

As she headed toward the equipment room, Marco intercepted her, umbrella tilted against the downpour. "Hey," he said softly. "Mom's on a call with the caterer. She asked if we could finalize the engagement party guest list tonight." He grimaced. "I told her I'd ask." His eyes searched hers. "We good?"

Elena's chest tightened. "We're... navigating." She lifted her hand to his cheek, thumb brushing stubble. "The Recovery Trust mess isn't resolved. Geneva prep is a riptide. I'm barely keeping up."

"I know." He caught her hand, pressing a kiss to her palm. "I'm here. Even when you're halfway across the world."

Guilt flashed hot. "I don't deserve how steady you are." The words slipped out.

"Maybe steadiness is my storm," he said, attempting a smile. "Come by after your dive? I'll make caldo."

"I'll try." She stepped back, letting rain spatter her face. The sea called, insistent.

She suited up with Talia, who raised a brow. "Night dive in rain. You're stubborn."

"The sensors flagged salinity drop," Elena replied, adjusting her mask. "We need real-time data." The truth—part of it. The rest was the need to submerge, to find clarity in the hush beneath waves.

Adrian appeared, rain jacket plastered to his frame. "You're going out now?"

"Can't postpone a tide," she said. "Want to man the surface station?"

He nodded, stepping into the skiff without hesitation. Talia shot Elena a knowing glance but said nothing. They motored out, rain stippling the water, the lighthouse beam a blurred arc. Waves slapped the hull, chop heightened by the storm. Elena breathed through the spray, the cold sting a welcome sharpness.

At the dive site, bioluminescence shimmered beneath the surface, green glows swirling like submerged constellations. Elena rolled backward into the water, shock of cold stealing her breath before the wetsuit's insulation kicked in. The sea enveloped her, rain pounding above like distant drums.

She descended along the guide rope, headlamp cutting through murk. The reef glowed ethereal under the storm, polyps retracted, fish sheltering in crevices. Sensors blinked amber, logging anomalies. Elena adjusted flow valves, recorded salinity readings, fingers numb inside neoprene gloves. The task steadied her. Down here, truth was tangible—numbers, currents, the flex of coral skeletons under hand.

When she surfaced twenty minutes later, rain sheeted across the bay. Adrian leaned over the gunwale, eyes wide. "You okay?"

"Fine," she sputtered, pulling off her regulator. "Salinity drop's within tolerance. We'll need to flush the northern channel tomorrow."

"I'll coordinate crews," he said automatically, helping haul her tank aboard. Rain plastered his hair, darkening it to near-black. His face was inches from hers. The storm muffled the world, leaving only the hiss of rain on water and the thud of her heart.

Talia busied herself with equipment, pointedly facing away. Elena shivered, the cold biting. Adrian shrugged out of his jacket, draping it over her shoulders without asking. The fabric smelled faintly of cedar and soap. Warmth seeped in.

They reached the dock, unloading in practiced silence. Talia departed with a wave, calling over her shoulder, "Don't drown in paperwork." Elena laughed, the sound torn by wind. She and Adrian hurried under the awning, rain cascading around them in silver sheets. The world felt suspended, the harbor hushed under the downpour's roar.

"Thank you," she said, clutching the jacket tighter. Water dripped from her hair, tracing cold lines down her neck. The compass pressed cool and certain against her sternum.

Adrian's gaze dropped to the pendant, then lifted to her face. "I keep thinking about what you said last night," he murmured. "About finding the shore." He stepped closer, close enough that his breath warmed her rain-chilled cheeks. "I don't want to rush you. But I also don't want to pretend I'm not standing here every night hoping you'll reach for me."

The rain pounded, masking their voices. Elena felt the tide inside her crest. The space between them hummed. She thought of Marco's steady hands, of promises made under calmer skies. She thought of Adrian beside her in courtrooms, on piers, in war rooms—of the way he saw her storms and stepped closer instead of flinching.

"I'm tired of pretending too," she whispered. The admission felt like diving into deep water. Fear and relief crashed.

Adrian's expression shattered—hope, disbelief, hunger flickering like lightning. "Elena—"

She reached for him. Their mouths met, tentative at first, the kiss tasting of rain and salt. Then urgency surged, years of restraint snapping like a wave over a seawall. His hands cupped her face, thumbs brushing raindrops from her skin. She fisted his soaked shirt, pulling him closer, the world narrowing to warmth amid storm.

When they finally broke apart, breaths ragged, rain plastered her hair to her cheeks. Adrian rested his forehead against hers. "Tell me if this is wrong," he whispered. "I'll walk away." His voice shook.

Elena closed her eyes. The tide roared in her veins. "It's complicated," she said, voice hoarse. "It's going to hurt."

"Worth hurting for?"

She opened her eyes. Rain streaked his lashes. "I don't know yet. But I know I don't want to keep building walls around this." She pressed a hand to his chest, feeling his heart hammer. "We have to be honest—with Marco, with ourselves."

"Honesty is the least we owe him," Adrian said. "And the harbor." He kissed her fingertips, reverent. "I'll wait for you to lead." He stepped back, giving her space even as longing radiated from him.

Elena hugged his jacket close. "I need time," she said. "Tomorrow, after the briefing, I'm talking to Marco." The words tasted like salt and grief. "I can't keep splitting myself between tides."

Adrian nodded. Pain carved his features, but he didn't flinch. "I'll be there after. Whatever you need." He turned, walking into the rain until the downpour swallowed him.

Elena stood beneath the awning, heart pounding in sync with the storm. She pressed fingers to her lips, the taste of rain and Adrian lingering. The sea beyond churned, waves slamming against pilings. Somewhere in the distance, thunder rolled. Change had cracked open, irreversible as a breached seawall.

She walked home through the rain, drenched despite the jacket. Marco waited on the sofa, soup steaming on the table. He looked up, smile blooming. Guilt pierced. She joined him, hands trembling as she lifted the spoon. He reached across the table, squeezing her knee. "You smell like a thunderstorm," he said affectionately.

Elena swallowed hard. "We need to talk," she began, voice soft.

His smile faltered. "Tonight?" Hope flickered, fragile.

She hesitated. Cowardice warred with resolve. "Tomorrow," she said. The word tasted like failure. She forced herself to meet his gaze. "After the Geneva briefing."

He studied her, worry clouding his eyes, but he nodded. "Okay. Tomorrow." He lifted his bowl, offering a toast. "To surviving storms."

Elena clinked her spoon against his. "To surviving," she echoed. The soup scalded her tongue. She barely tasted it. Rain hammered the roof, steady as heartbeat.

Later, alone in bed, she lay awake listening to the storm. Marco breathed beside her, even and deep. She stared at the ceiling, replaying the kiss, the softness of Adrian's mouth, the tremble in his hands. Desire and dread twisted. She clutched the compass, feeling its edges dig into her palm. The sea outside roared, reminding her that tides did not pause for fear. Dawn would come, and with it choices that would redraw the map of her life.

She closed her eyes, surrendering to the rhythm of rain. In her mind, the reef glowed, resilient under assault. She whispered a promise to the dark: to be as brave as the corals that rebuilt themselves after every storm, to face the tides without flinching. Sleep finally crept in like a receding wave, leaving her floating in uncertainty but resolved to chart the next course honestly.

