\chapter{Riptide Signal}

Two days after the abduction, Marisport's harbor bristled with vessels readying for open ocean. Coast Guard cutters idled beside fishing boats rigged with extra fuel tanks. Priya's legal brief had detonated across the globe—NorthCross's archive splashed on front pages, Navarro indicted in absentia, Sterling assets frozen. The victory tasted hollow while Adrian remained captive.

Elena stood on the pier as dawn painted the water blush gold. The air smelled of diesel and salt. Marco strapped down crates on Ignacio's largest boat, movements efficient despite bloodshot eyes. "We'll rendezvous with Patel's cutter twenty miles out," he said. "From there, we follow the coordinates." He glanced at her. "You ready?"

"Ready enough," she replied. Fear coiled tight in her belly, but resolve kept her upright. She wore a drysuit under her rain gear, gear harness snug. The compass rested against her sternum, cold and certain.

Priya approached, headset looped around her neck. "Interpol issued a warrant for Victor Sterling," she said. "He vanished. We're betting he's on that platform." Her gaze softened. "We're bringing him down and bringing Adrian home."

"Or we go down trying," Elena said quietly. The thought didn't terrify her as much as leaving Adrian to drown. She boarded the boat, heart hammering.

The flotilla glided past the lighthouse, beam extinguished in daylight. Townspeople lined the seawall, raising fists, waving banners. Talia blew a kiss toward the crowd before gunning the engine. Marco steered, jaw set. Naomi monitored comms from the lab, voice steady through Elena's earpiece. "Satellite feed tracking you," she reported. "Platform shows increased activity. Heat signatures: eight."

Open water stretched, gray-green under overcast sky. Swells lifted and lowered the boat like a slow heartbeat. Elena inhaled sea spray, letting it ground her. Marco cleared his throat. "Before we hit whatever that is," he said, eyes on the horizon, "I need you to know I'm not holding on to old promises. I love you, Elena. That won't change. But I'm here because saving him means saving you." He glanced at her briefly. "Bring him back. Then figure out what tide you want to ride."

Emotion clogged her throat. "Thank you," she whispered. "For staying." She squeezed his shoulder. The conversation ended there, words insufficient amid waves.

Hours later, the oil platform rose from the sea like a rusted cathedral, legs plunged deep into churning water. Weathered pipes snaked along its sides. Satellite dishes glinted. The place radiated menace. Patel's cutter approached from the east, armed officers at the ready. "Thermal scans confirm eight hostiles, one high-heat signature isolated in the west ballast chamber," Patel radioed. "Likely Adrian." His voice carried grim determination. "We go in fast."

They executed the plan with precision. Talia piloted the skiff under the platform's shadow, spray soaking them. Elena, Priya, and two Coast Guard divers clipped onto rappel lines. The metal smelled of salt and oil. Elena's gloves squeaked as she climbed the ladder, heart pounding. Above, gulls screamed.

They breached through a maintenance hatch. Inside, the air reeked of brine and coolant. Dim emergency lights flickered. Footsteps pounded elsewhere. Priya led the way, gun steady. Patel's team fanned out, clearing corridors. The platform groaned beneath their weight, waves smashing against pylons.

They reached the control room. Monitors glowed with camera feeds. One displayed Adrian strapped to a steel chair inside a glass-walled chamber, water sloshing around his ankles. Bruises darkened his cheek; his eyes burned bright even behind the blindfold. Beside him stood Victor Sterling, silver hair disheveled, expression carved from granite. He spoke into a mic—words unheard but demeanor unmistakably cold.

Elena lunged toward the glass. "Adrian!" She slammed her palm against it. He flinched, blindfolded head turning toward the sound. Victor's eyes snapped up, meeting hers through the camera. Contempt twisted his mouth. He pressed a button. The water level rose, swirling around Adrian's calves.

"Release him!" Elena shouted, voice cracking. Victor simply lifted a hand and the feed cut. Alarms blared. Priya cursed. "They triggered the scuttle sequence," she said, scanning screens. "Charges set to detonate in twenty minutes."

"Control panel locked," Patel reported. "Override requires two keys. One's missing."

Elena's earpiece crackled. Naomi's voice: "We're intercepting a transmission from the platform." Static fizzled, then Adrian's voice, hoarse, burst through. "Elena, if you hear this—" He coughed. "There's a secondary pipeline. Coordinates in the data port. Don't let them flood the Atlantic network." The message cut abruptly.

"Secondary pipeline?" Priya muttered, eyes darting. She plugged a drive into the console. Files streamed—schematics of undersea conduits connecting NorthCross facilities, timed to release chemical blooms along multiple coasts. Elena's blood ran cold. "They planned this as a distraction," Priya said. "If we don't stop it, dozens of reefs die." The stakes multiplied.

Marco's voice came through, tense. "Ignacio reports sirens in Marisport. They found explosives under the boardwalk, wired to storm alarms. We're defusing but it's a mess." Elena's chest clenched. Danger stalked every front.

"We split," Patel ordered. "Team Alpha to ballast chamber, Team Bravo to engine room. Priya, stop that pipeline. Elena, with me." They raced down metal staircases slick with condensation. The platform's groans deepened, metal protesting. Water sprayed from ruptured pipes. The sea crashed below, a hungry roar.

They reached the ballast chamber door—thick steel with a manual wheel. Locked. Elena's palms slipped as she strained. "Help me!" she gasped. Patel and Marco (who'd followed despite orders) heaved with her. The wheel creaked, budged, then jammed. "They welded it," Marco snarled.

Through the small viewport, Elena saw Adrian struggling against restraints, water at his knees. The blindfold hung around his neck now; his eyes met hers through the glass. Relief and terror flared. He mouthed her name, lips forming \textit{I love you}. Tears blurred her vision. She pressed her hand to the window. He mirrored the gesture, separated by inches and unyielding steel.

Victor appeared behind him, wrench in hand. He leaned close to Adrian's ear, saying something Elena couldn't hear. Adrian bared his teeth in defiance. Victor struck him across the face. Elena screamed, pounding the glass until her fists ached. "You coward!"

Priya's voice crackled over comms. "Pipeline upload is live. They're about to trigger releases worldwide." Her breathing was ragged. "I can stop it but need sixty seconds." Gunfire echoed in the background. "Hold them off!"

"We don't have sixty," Patel snapped, eyeing the countdown blinking on a panel: 08:42. The platform shuddered as charges armed.

Naomi cut in, panic lacing her voice. "Sirens in Marisport just activated. The explosives are wired to detonate if the storm alarms silence. We can't disarm without remote access." Chaos layered upon chaos.

Elena's mind raced. Save Adrian or prevent global catastrophe? Another impossible choice loomed. "I can reroute the siren system remotely," Naomi said. "But it will set off the harbor evacuation, mass panic." A beat. "Lena, decide."

Elena's heart pounded. Adrian's gaze locked with hers, pleading and resolute. "Stop the pipeline," he mouthed, pushing her away with his eyes. He shook his head fiercely. \textit{Do it.} The message was unmistakable. He would rather drown than let them destroy the seas.

She swallowed a sob. "Naomi, trigger the evacuation," she ordered. "Priya, stop that pipeline." Her voice shook but didn't waver. "Patel, buy us time." She slammed her palm against the glass one more time. "Hold on," she whispered. "I'm coming back." Adrian nodded once, tears glistening. She turned, sprinting toward the control deck where Priya fought to override the upload.

Gunfire erupted. Elena ducked behind a console, adrenaline surging. Priya's fingers flew over keys, sweat streaking her face. "Almost—" she gritted out. "Done!" She hit enter. The upload stalled, progress bar freezing. "Pipeline neutralized." Relief crashed—but the countdown continued: 04:12.

A new alarm shrieked—higher, more urgent. "Scuttle sequence locked," Patel shouted over comms. "Charges armed. We have to evacuate." He sounded like he hated the words.

"We don't leave him!" Elena cried, racing back toward the chamber. Marco grabbed her arm, eyes blazing. "If we die here, no one saves him." He dragged her toward the exit. She fought, desperate. Behind the glass, Adrian thrashed, water now at his waist. Victor had disappeared. Sirens wailed from the platform's loudspeakers. Through comms, Elena heard Marisport's sirens echo—a distant, discordant chorus.

"Let go!" she shouted, tearing free. She rushed back to the wheel, ignoring the countdown. "Adrian!" She jammed her fingers into the seam, trying to pry it open. Metal sliced her skin. Blood streaked the door. Adrian shouted something she couldn't hear. She mouthed back, "I love you." The words felt like both confession and battle cry.

Marco wrapped his arms around her, hauling her away as the deck lurched. "We go now!" he yelled. Priya grabbed Elena's wrist, pulling. "He'd kill us himself if we stayed," Priya said through clenched teeth. Tears streamed down her face. "We regroup and return."

They stumbled toward the skiff as explosions rippled through the platform. Fire roared. Metal shrieked. The structure leaned. Elena looked back. Through the smoke, she saw Adrian still at the glass, water to his chest, hand pressed where hers had been. His lips formed words lost to wind and alarms. The image seared into her.

They leaped into the skiff as a fireball erupted behind them. Heat scorched Elena's back. The platform groaned, tilting. Alarms melded with the distant wail of Marisport's evacuation sirens transmitted through comms. The sea churned, a chaos of spray and debris. Elena reached toward the collapsing structure even as the skiff sped away, her scream torn away by wind.

Behind them, the platform began to sink, flames licking sky. Ahead, the horizon darkened with storm clouds racing in. Elena's body shook with fury and terror. "Turn back!" she shouted at Marco.

"We can't!" he yelled. "The charges—"

Naomi's voice burst through, frantic. "The bay sirens won't stop. People are evacuating. We found secondary devices under the sea wall. We need you back."

Elena stared at the burning platform, at the water swallowing the only path to Adrian. She reached for the disappearing silhouette, voice raw. "Adrian!" The wind swallowed his name. Flames reflected in her tears.

They reached for each other across smoke and distance, but the sirens were already rising from the bay.

