\chapter{Floodgate}

Morning arrived in shades of slate and mauve, bleeding through the blinds of the Sterling office like diluted ink. Elena woke on the nap pod's narrow mattress with the compass imprinting a crescent on her sternum. For a heartbeat she forgot where she was; then the hum of HVAC and distant sirens snapped the previous day's battles back into focus. Her body protested every movement. Priya thrust a cup of bitter coffee into her hand before she could sit up fully.

"Monitor hearing at nine," Priya said, voice hoarse. "DOJ wants us there by eight."

"What time is it now?" Elena croaked.

"Six. You slept three hours. Luxurious." Priya's eyes were red-rimmed but bright. "Commander Patel sent a thank-you. Coast Guard seized the \textit{Morning Zenith}."

Elena exhaled, letting the news settle like a warm stone. "Any fallout from Blue Current?"

"Their stock tanked ten percent overnight," Adrian said from the doorway, suit jacket draped over one arm. His tie hung loose. "My father called an emergency board meeting for noon. I'm invited."

"To be congratulated or crucified?" Priya asked dryly.

Adrian's mouth twitched. "Depends on whether I bring donuts."

Elena sipped the coffee. It tasted like burnt almonds and necessity. Her phone blinked with messages layered upon messages—Marco, Aisha, city officials. She scanned quickly. Marco had sent a photo of the café filled with neighbors sleeping on cots; the caption read: \textit{Your hearing rerun knocked them out.} Aisha's message carried the Palawan council's thanks and a question: \textit{Will you join the cross-Pacific resilience consortium call tonight? We need your voice on international funding.}

Elena tucked the phone away. One tide at a time.

They walked to the courthouse under a sky striated with high clouds. The air smelled of wet pavement and magnolia leaves bruised by rain. Downtown commuters rushed past with umbrellas and coffees, oblivious to the emergency docket. At the courthouse entrance, reporters thronged behind barricades, microphones thrust forward like a kelp forest. Priya kept her gaze ahead, jaw set. Adrian offered Elena a steadying glance.

Inside, the courtroom felt smaller than the previous day, intimacy magnifying stakes. Judge Vasquez presided again, robes crisp, hair pulled back. Blue Current's team looked more rumpled, as if sleep had eluded them. Victor Vance sat with hands clasped, knuckles pale. Beside him, a younger executive scribbled notes furiously.

"We're here to appoint a federal monitor pursuant to yesterday's injunction," Judge Vasquez announced. "Counsel, state your proposals."

The DOJ attorney rose. "The government nominates Commander Raj Patel of the United States Coast Guard to serve as monitor," she said. "Commander Patel has overseen maritime environmental enforcement for a decade." Patel sat in the front row, uniform pressed, eyes steady. Elena felt a surge of relief.

Hensley stood smoothly. "Your Honor, Blue Current proposes Dr. Miriam Paxton as monitor. Former head of the Coastal Engineering Institute. She has experience with maritime infrastructure and a proven ability to work with private industry." A poised woman in a navy suit inclined her head.

Priya leaned toward Elena. "Paxton took consulting fees from Blue Current last year," she whispered.

Elena's stomach clenched. Priya rose. "Your Honor, we object to Dr. Paxton's appointment due to conflict of interest," she said. "She received payments from Blue Current subsidiaries for `strategic assessments' within the last eighteen months." She slid a document across the clerk's desk. "We have invoices."

Hensley frowned. "Those were for independent studies."

"Funded by Blue Current, benefiting Blue Current," Priya shot back. "Commander Patel has no such entanglements."

Judge Vasquez studied the documents. She looked up, gaze sharp. "Dr. Paxton, did you receive compensation from Blue Current or its affiliates in the past two years?"

Dr. Paxton clasped her hands. "Yes, Your Honor. I provided engineering assessments."

"Then you're conflicted," the judge said matter-of-factly. "Commander Patel, please approach."

Patel rose, spine straight. Judge Vasquez regarded him with measured respect. "Commander, do you accept the appointment?"

"Yes, Your Honor," he replied. "I'll ensure compliance and protect these coastlines."

"Good." She signed the order with a decisive stroke. "Commander Patel is hereby appointed federal monitor with authority to inspect Blue Current facilities, vessels, and records. Mr. Vance, cooperate fully or face contempt." Vance's jaw tightened, but he nodded stiffly.

As the hearing adjourned, the gallery murmured. Elena felt a knot loosen between her shoulder blades. Priya squeezed her hand. "One more gate closed," she said softly.

Outside, reporters converged. Naomi materialized at Elena's elbow, gently steering them toward a bank of microphones set up by the coalition. Senator Ramirez joined them, teal blazer exchanged for crisp white. Cameras flashed. Elena squared her shoulders.

"Today's appointment ensures accountability," she told the press. "But our work doesn't end with oversight. Communities need funding, training, and a seat at the table. We'll be in those rooms until every coastline has what Marisport fought for." Her voice carried down the steps. Behind her, coalition members lifted banners, the lighthouse emblem bright against overcast sky.

Questions flew. "Dr. Ruiz, will you return to Marisport now?" "How long will the injunction last?" "Mr. Sterling, are you resigning from the board?" Adrian fielded his with a measured calm that belied the tension tightening his shoulders. Priya answered legal queries with crisp efficiency.

After the scrum, they retreated to Sterling's office. Adrian's assistant had arranged breakfast—empanadas, fresh fruit, coffee that didn't taste like burnt almonds. Elena devoured half an empanada before noticing the message waiting on her tablet: a calendar invite from the United Nations Coral Alliance. \textit{Emergency Summit: Adaptive Reef Networks. Location: Geneva. Date: In two weeks. Requesting participation: Dr. Elena Ruiz, Marisport Resilience Lab. Travel grant available.}

Her heart thudded. Geneva. Two weeks. A summit she'd dreamed of but never imagined attending in person. It would mean leaving again—right after returning home. She rubbed the sea glass between thumb and forefinger, the edges softened by countless tides.

A soft knock interrupted. Adrian's mother, Celeste, stood in the doorway, silver hair swept back, eyes warm. Elena straightened, surprised. She'd met Celeste only once, years prior at a community fundraiser.

"May I come in?" Celeste asked.

"Of course," Adrian said, rising. They embraced quickly. Elena noted the tension in his shoulders ease fractionally.

Celeste turned to Elena. "I watched the hearing," she said. "You made me proud."

"Thank you," Elena replied, touched.

Celeste's gaze flicked to her son. "Your father is furious," she said without preamble. "But he's also afraid. He's built his identity on that company. He doesn't know who he is if it's held accountable."

Adrian let out a breath. "He could start by being a father instead of a CEO."

Celeste's smile held sadness. "He's trying in the only way he knows—by doubling down. I'm not asking you to forgive him. But be ready. He may try to trade contrition for control."

Adrian nodded, jaw set. "I'm not giving him either."

After she left, Priya whistled low. "Family drama during federal oversight. Iconic."

Elena's phone buzzed. Marco. She stepped into a quieter corner and answered.

"Hey," he said. "How's D.C.? Still humid and self-important?"

She laughed softly. "Always." She leaned against the window, watching clouds scud over the Potomac. "Commander Patel is monitor. Blue Current's boxed in."

"Ignacio is already planning a `Monitor Mixer' at the dock," Marco said. "I told him to let the commander unpack first." Laughter laced his voice, but an undertow of fatigue tugged beneath. "When are you coming home?"

Elena hesitated. "There's a summit in Geneva in two weeks," she said. "The UN wants me to speak."

A beat of silence. She could almost hear him absorbing the words. "That's... huge," he said carefully. "Do you want to go?"

She looked at the compass gleaming faintly under the fluorescent lights. "Yes," she admitted. "But it means leaving again so soon after getting back."

"It also means getting the funding you've been fighting for," he replied. She heard him move, probably wiping down the café counter. "We'll adjust. Seasons, remember?"

Emotion rose, thick and briny. "I don't want to keep asking you to adjust."

"We're not adjusting alone," he said gently. "We're choosing it. If you go, we'll chart it together. We'll add `Geneva' to the tide calendar."

She pressed her forehead to the glass. "I love you."

"I love you more," he said. "Call me when you have flights. I'll start stockpiling international phone cards like it's 2003."

She laughed through the ache. "Deal."

After the call, Elena stared at the UN invite. The cursor blinked like a heartbeat. Priya slid into the seat beside her. "You're going," she said. Not a question.

"How do I leave again without feeling like I'm abandoning everyone?" Elena asked, voice low.

"By remembering you're expanding the fight, not walking away," Priya replied. "Marisport didn't build you to stay put. It built you to carry it into every room that thinks it's the center of the world." She nudged Elena's shoulder. "Besides, we need someone to bully international donors while I sue domestic ones."

Elena huffed a laugh. "When did we become the tidal coalition?"

"When Blue Current decided profit outranked people," Priya said. "We're just correcting the tide chart."

Noon approached. Adrian straightened his tie, preparing for the board confrontation. "Wish me luck," he said.

"Break a ledger," Priya replied.

Elena squeezed his hand. "You already chose who you are," she said softly. "Let him see it."

He nodded, gratitude flickering in his eyes, and left with Naomi. The office quieted. Priya dove back into filings. Elena sifted through data requests, sending coral stress logs to Commander Patel, coordinating with Aisha on the consortium agenda, drafting talking points for the summit she hadn't yet accepted.

By late afternoon, exhaustion wove through every action like a heavy net. Elena stepped outside for air. The Potomac glimmered under a sky clearing to blue. Joggers passed, earbuds in. Tourists snapped photos of monuments that seemed to float above the river's slow current. The city felt suspended between storms.

She walked to the water's edge, breathing in the scent of algae and boat fuel. A low rumble drew her attention. Adrian approached, jacket over his arm, expression equal parts relief and grief.

"How'd it go?" she asked.

"I resigned," he said, voice steady. "Effective immediately."

Elena's eyes widened. "Adrian—"

"He tried to bargain," Adrian continued. "Offered to create a resilience wing if I stayed and `tempered the activists'." He let out a sharp laugh. "I told him accountability isn't a brand. He called me ungrateful. I walked." He gazed at the river. "I don't know what's next." His shoulders slumped for the first time since they landed.

Elena stepped closer. "Whatever it is, you won't be doing it alone."

He nodded, eyes shining. "Thank you," he whispered. "For not letting me drown in loyalty."

They stood in silence, watching sunlight break through clouds and shatter across the water. A heron lifted from the bank, wings beating slow and deliberate. The moment stretched, bittersweet as salt on a fresh wound.

By evening, the war room transformed into a global conference hub. Screens displayed faces from Palawan, the Gulf Coast, the Caribbean. Elena sat at the head of the table, headphones in, Aisha's voice crackling through the speakers.

"We propose a cross-Pacific resilience network," Aisha said. "Shared data, coordinated funding asks, mutual aid. Elena, will Marisport co-lead?"

The question hung like a suspended tide. Elena glanced at Priya, who gave an almost imperceptible nod. "Yes," Elena said. "We'll co-lead. We'll share our models, our failures, our victories."

Cheers erupted through the call. Aisha grinned. "Then let's design a sea wall they can't punch holes through."

The meeting stretched into the night. Plans unfurled: training exchanges, sensor sharing, emergency communication drills. Elena felt energy spark beneath her fatigue—a current pulling her toward something larger than any single harbor.

When the call ended, she stepped onto the office's rooftop terrace. The city's lights shimmered, constellations built of glass and ambition. She pulled out Marco's star chart, now creased from use. Vega burned bright above the Potomac, exactly where he said it would be. She traced the line from Vega to Altair, an imaginary bridge spanning continents.

Her phone buzzed with a new message from the UN coordinator: \textit{Looking forward to your confirmation. Agenda attached. We have an opening for a keynote on community-led resilience.}

Elena smiled, the expression tinged with awe and apprehension. She typed her response, fingers steady.

\textit{Confirming attendance. Let's talk about tides that cross oceans.}

She hit send. The future unfurled like a tide chart populated with cities and reefs she'd only studied in journals. Geneva, Palawan, Marisport, Flower Garden Banks—a constellation of commitments.

Below, traffic murmured. A warm breeze carried the faint scent of river mud. Elena closed her eyes and pictured the lab's rooftop garden, Marco's calloused hands pressing sea glass into her palm, Priya's laughter, Adrian standing taller without the weight of his father's shadow, Ignacio planning a flotilla parade. She pictured children in Palawan watching the livestream, teenagers in Marisport coding new alert systems, Coast Guard crews hauling contraband from hulls.

Her compass rested against her heart, metal cool, edges familiar. It had guided generations of fishers through fog and storm. Now it pointed her toward courtrooms, boardrooms, summits. Toward seasons defined not by absence, but by purpose.

Thunder grumbled far off, a reminder that storms never ceased for long. Elena opened her eyes. The Potomac flowed dark and steady. Somewhere beyond the horizon, waves broke on a coral reef she hadn't yet touched. She would go. She would return. She would carry Marisport with her, a tide that refused to recede.

Behind her, the terrace door opened. Priya stepped out, holding two mugs of tea. "Ignacio texted," she said. "He's naming the flotilla's new patrol boat after you."

Elena groaned. "Absolutely not."

Priya laughed, handing her a mug. "Argue with him yourself."

They stood shoulder to shoulder, sipping tea as night deepened. Far below, the river whispered against stone. Ahead, the next tide gathered, full of summons and promises.

"Ready?" Priya asked quietly.

Elena lifted her chin, eyes on the horizon's faint glow. "Always," she said.

Lightning flickered distant and silent, illuminating the clouds in fleeting gold. The storm would come, as storms always did. But Elena was no longer bracing alone. She was steering into it, compass in hand, surrounded by a flotilla that spanned oceans.

The tide was still rising.
