\chapter{Capitol Tide}

The transport touched down on a ribbon of wet tarmac just before dawn, wheels thudding against the runway with a final shudder. Elena's neck ached from sleeping upright. When the cargo ramp lowered, humid August air and the smell of jet fuel rushed in, layered with the petrichor of a night storm that had brushed Washington. Sodium lights haloed the National Guard hangar at Joint Base Andrews. Mechanics in reflective vests strode past crates stenciled with emergency insignias. Priya unbuckled beside Elena, hair flattened by the headset. Adrian collected their binders with the fastidiousness of a man clinging to ritual.

"Welcome to the other kind of storm," he murmured as they descended the ramp.

Elena tightened her grip on her duffel. Beyond the hangar bay doors, the capital's skyline glimmered faintly, the Washington Monument a pale silhouette against a bruised dawn. She inhaled and tasted jet exhaust and the ghost of the Atlantic still lodged in her lungs. Her phone buzzed before her boots hit concrete: a secure ping from Talia.

\textit{Boarding teams staged. Seas ugly. Coast Guard launches at 0340. I'll update when they make contact.}

The timestamp read 03:11. Elena thumbed a reply as soldiers rolled their evidence crates toward a waiting van.

\textit{We're on the ground. Depositions start at 0600. Holding your channel in my pocket.}

Inside a converted briefing room, Department of Justice staffers waited with thermal carafes and stacks of forms. Fluorescent lights buzzed overhead. A digital clock ticked down minutes in unforgiving red.

"Dr. Ruiz?" An assistant attorney general offered a hand. "Lara Choudhury. Thank you for making the flight. We'll start with sworn deposition to preserve testimony before the injunction hearing."

Priya accepted a lidded coffee with a grateful grunt. "We've organized exhibits alphabetically," she told Lara, sliding a drive across the table. "Chain of custody documents are tabbed." Adrian added a thick folder of financial ledgers, each page annotated in his careful scrawl. Elena eased into a metal chair, the seat cold even through her suit slacks. The room smelled faintly of bleach and anxiety.

Lara positioned a recorder between them. "We'll go on record at 05:58," she said. "Anything you need before we begin?"

Elena flexed her cramped fingers. "Is there word from the Coast Guard?"

Lara checked her phone. "Latest report says the \textit{Artemis Star} reduced speed but hasn't answered hails. Boarding team is waiting for a lull."

The information settled like ballast—useful, heavy. Elena nodded. "Then let's begin."

\bigskip

Once the red light on the recorder blinked, time flattened. Lara's questions came measured, meticulous. "Describe the condition of the reef modules prior to the sabotage attempts." Elena recounted months of growth—the pale gold shimmer of new polyps, the faint sweet smell of thriving algae. "Explain the impact of Blue Current's dredging plan." She described turbidity plumes thick as winter fog, the muffled silence after fish fled. Priya occasionally interjected to clarify dates, her pen skittering across legal pads. Adrian provided financial bridges—how shell companies wired funds through Sterling accounts without board approval.

Between sections, Elena sipped tepid coffee and rolled her shoulders. The fluorescent lights hummed like cicadas. Outside the small window, dawn unfurled over the runway, bathing C-130s in a wash of pale gold. At 06:32, Lara paused the recorder for a brief recess. Elena stepped into the corridor and leaned her forehead against cool cinderblock.

Her phone vibrated again. This time, the message was audio. Talia's voice, clipped and low, filled her ear.

"Boarding team made contact. Blue Current security refused ladder. Coast Guard is cutting anchors. Heavy swell. They'll breach in seven minutes. Ignacio says flotilla reports rogue drone skimming the surface—probably a decoy. We're tracking it."

Elena swallowed, the hallway tilting for a moment. "Stay safe," she whispered into the phone. "Log everything." She imagined the harbor lights flickering in the pre-dawn rain, Marco on the pier with binoculars, every muscle coiled.

When she returned to the conference room, Priya pushed a protein bar into her hand. "Eat. We're shifting to damages."

Lara resumed recording. "Dr. Ruiz, can you articulate the community impact of the attempted sabotage in economic terms?"

Elena pictured the café's mud-slicked floor, the daycare in the gymnasium, the teenagers cataloguing drone footage with wet socks. "We sheltered three hundred residents during the hurricane," she said. "Those people returned to homes that remained standing because our reef slowed the surge by thirty-seven percent. Without it, the marina district would have experienced catastrophic loss—businesses, homes, lives. Blue Current's charges targeted that protective infrastructure."

She described Ignacio's flotilla, the smell of corroded charges, the high schooler whose translation app relayed warnings to Palawan. The words came steadier than she felt. By the time Lara clicked off the recorder at 07:21, Elena's voice had roughened, but her gaze held firm.

"Thank you," Lara said. "We're filing the injunction with Judge Vasquez at nine. The Senate Subcommittee on Coastal Resilience expects you at ten." She gathered the exhibits. "We have secure transport into the city. There's a conference room where you can prep, and a shower if you need it."

Priya slumped briefly, relief flashing across her face before battle-readiness returned. "We need thirty minutes to coordinate with the coalition."

Adrian checked his watch. "Sterling's D.C. office is two blocks from the Rayburn building. My team set up war room access."

Elena nodded. The adrenaline that had propelled her through the deposition ebbed, leaving tremors in its wake. "Give me five minutes for the shower," she murmured. "I want to wash storm salt off before I testify."

The shower stall was utilitarian, the water barely warm, but the sensation of rinsing grit from her hair felt like reclaiming her own skin. She changed into a charcoal suit, looped the compass and sea glass beneath the crisp collar, and clipped on her ID badge. When she met Priya and Adrian in the staging area, both looked sharper, exhaustion tucked away beneath tailored lines.

They climbed into a dark SUV escorted by base security. The driver took Suitland Parkway toward the Potomac, the sky shifting from pewter to pale blue. Elena pressed her forehead to the cool window, watching the landscape change from military infrastructure to tree-lined avenues. Flood markers etched into bridge supports glinted in morning light—a silent ledger of rising waters.

"I grew up measuring those markers," Priya said quietly, following Elena's gaze. "Every year, the city painted new lines."

"They're going to have to stop painting and start moving people," Adrian replied. The cadence of their voices reminded Elena of nights spent planning resilience workshops, the same urgency refracted through marble and stone instead of cedar and steel.

As they crossed the river, Elena glimpsed the Capitol dome gleaming beyond scaffolding. A protest already gathered on the Mall—handmade signs bobbing above rain ponchos. She read phrases as they rolled by: \textit{Protect Our Coasts}. \textit{Resilience Is Infrastructure}. A banner bearing Marisport's lighthouse emblem snapped in the breeze. Her throat tightened.

Sterling's D.C. office occupied a renovated row house near the Hill, all glass and exposed brick. Inside, staffers hustled between workstations, eyes flicking toward televisions tuned to national news. Adrian's chief of staff, Naomi, pressed tablets into their hands. "Media requests have tripled since the storm," she said. "We drafted talking points aligned with the coalition's demands."

Priya scanned the notes, crossing out jargon without breaking stride. Elena skimmed video clips queued for the hearing: drone footage of the sabotaged charges, testimonials from shelter residents, a split-screen comparison of Palawan and Marisport. Her phone vibrated with a call from Marco.

"You in one piece?" His voice crackled, background noise full of gull cries and the rhythmic slap of waves.

"Depositions done," she said. "Heading into the Hill." She closed her eyes, picturing him on the pier, wind tugging at his curls.

"Coast Guard boarded," he reported. "We're keeping channel nine open in case they need translation. Ignacio is swearing in three languages."

"That's how I know he's calm," she said, laughter threading through the tension.

Marco sobered. "Whatever they throw at you, remember you've already stood in a hurricane. Senators are just wind with better suits."

"I'm picturing them in storm slickers now," she replied. "I'll call when the hearing ends."

"I'll be awake," he promised. "The whole town's watching the livestream on the café projector."

She pocketed the phone, the words grounding her like the compass's weight. Naomi guided them into a glass-walled conference room where coalition members dialed in from across the country. Aisha's face filled one panel, eyes ringed with fatigue but alight with determination.

"We've drafted testimony in Tagalog and Spanish for allied senators," Aisha said. "We want them to cite Palawan's case alongside Marisport."

"We'll weave it in," Priya replied. "Elena leads with impact, Adrian with finance. I'll handle legal precedent."

Aisha nodded. "We'll be streaming the hearing for the Palawan council. Make them understand the ocean doesn't respect borders."

After the call, Priya spread hearing agendas across the table. "Senator Tilden chairs the subcommittee," she said. "Moderate, but receptive. Senator Kline will be hostile—he has Blue Current donors in his state. Ramirez is our champion. She wants you to draw the line between sabotage and national security."

Elena scanned highlighted sections of proposed questions. Her stomach lurched, adrenaline surging anew. "We have video exhibits queued?"

"Two-minute limit per witness," Naomi reminded. "Use the charge footage sparingly."

Adrian adjusted his tie, jaw tight. "My father is in town," he said abruptly. "He texted. Says he's here to `observe'."

Priya's eyebrows shot up. "Do we need security?"

"No," Adrian said, though tension rippled beneath the word. "He won't sabotage the hearing in person. He prefers boardrooms. But if you see Sterling Foundation donors lingering, keep them away from the press risers."

Elena placed a hand on his arm, a brief squeeze. "We make the record. He can read it along with everyone else."

They departed for the Capitol complex at 09:40, badges clipped to lapels. Security lines buzzed with staffers clutching folders, interns balancing coffee trays, activists in matching shirts. Inside the Rayburn building, the air held a chill despite summer outside, conditioned to museum sterility. Portraits of former legislators watched from paneled walls.

The hearing room itself resembled a small amphitheater—tiered dais, microphones, nameplates gleaming under recessed lights. C-SPAN cameras stood sentinel at the back. Reporters whispered while adjusting recorders. Rows behind the witness table filled with community members wearing pinned ribbons shaped like waves. Elena spotted Ignacio's niece, Sofia, her hair dyed coral pink, seated beside Naomi. Priya set a binder on the table, tabs bristling like the spines of a sea urchin.

Elena ran fingertips over the polished wood, centering herself. The compass pendant rested cool against her sternum. She placed the sea glass beside her notes, a shard of home catching the sterile light. The chair's leather squeaked as she sat.

Senator Ramirez approached before the gavel fell, hand extended. "Dr. Ruiz. Thank you for coming on such short notice." She wore a teal blazer the color of deep water, hair pulled into a sleek knot. "My staff toured Marisport last year. They still talk about your reef gardens."

"Thank you for seeing us," Elena replied.

Ramirez's gaze sharpened. "Blue Current's lobbyists have been circling since dawn. They will frame sabotage as a misunderstanding. Don't let them." She squeezed Elena's shoulder before ascending to the dais.

The gavel struck at 10:02. "The Subcommittee on Coastal Resilience will come to order," Senator Tilden intoned. Cameras whirred softly. Elena drew a breath, tasting recycled air laced with coffee and old paper.

As Tilden read the opening statement, Elena's phone buzzed discreetly. A notification flashed from the secure channel: \textit{Boarding underway. Intercept feed pending}. She silenced the alert, pulse hammering, and fixed her attention on the dais.

When her name was called, she stood. The room receded until only the microphone, the senators, and the burn of her own heartbeat remained. "Chair Tilden, members of the subcommittee," she began, voice steady despite the tremor in her hands. "My name is Dr. Elena Ruiz, marine biologist and director of the Marisport Resilience Lab." She described the hurricane, the sabotage, the community that refused to surrender.

As she spoke, screens behind the dais displayed the drone footage—charges corroded by salt, volunteers hauling nets in gale-force winds. Gasps rippled through the audience. Senator Kline leaned forward, expression carved from skepticism.

"Dr. Ruiz," he interrupted, "isn't it possible that these explosives were the work of rogue contractors? Blue Current denies authorizing sabotage."

Priya's pen paused, ready. Elena met Kline's gaze. "The charges we recovered bear the Blue Current logo etched into the casing. They match devices seized in Palawan. Their satphones pinged a coordination hub registered to a Blue Current subsidiary. Rogue contractors don't carry corporate-issue access cards."

Murmurs rose. Kline opened his mouth, but Ramirez spoke first. "Dr. Ruiz, can you explain what would have happened if the charges had detonated as planned?"

Elena exhaled. "Our reef modules would have dissolved from the inside. The storm surge would have slammed into our seawall at full force. Families who took shelter in our lab might have drowned. The café where my fiancé feeds first responders would be rubble. The sabotage wasn't theoretical. It was murder deferred only by a community's vigilance."

Silence followed, taut as a fishing line. Then Tilden cleared his throat. "Let the record reflect that the witness has submitted photographic evidence, Exhibit 14A, depicting Blue Current logos on the recovered charges."

Adrian's testimony followed, detailing shell corporations and diverted funds. Priya laid out legal precedent for emergency injunctions against infrastructure sabotage. As they spoke, Elena glanced at her muted phone. Another message waited: \textit{Artemis team encountered chemical pods. Sending images when uplink stable.} Her mouth went dry.

The hearing stretched into noon, punctuated by recesses while senators huddled with aides. During one break, Elena stepped into the hallway where marble floors gleamed like tide pools. She leaned against a column, calling Marco on the secure line.

"We saw you," he said before she could speak. "The kids at the café cheered when you told Kline about murder."

"How's the harbor?"

"Holding. Coast Guard just transmitted stills of the cargo hold. Elena... there's enough chemical agent in there to strip half our reef."

Her knees wobbled. She braced a hand against cool stone. "They're securing it?"

"Working on it," he said. "Ignacio says the pods are rigged with failsafes. Talia's relaying the schematics you gave the DOJ."

Elena pressed her forehead to the column. "Keep the flotilla back. If those pods rupture—"

"Already ordered," he replied. "Focus on the senators. We'll keep breathing."

She hung up as Priya beckoned her back. The second half of the hearing crackled with urgency. Senators proposed amendments on the fly—emergency funds, federal oversight of private dredging. Blue Current's counsel, a silver-haired man with a placid smile, delivered a rebuttal laced with euphemisms. "Unfortunate miscommunications." "Anomalous subcontractors." Priya dismantled each with receipts. Adrian detailed the board vote to suspend partnerships.

When the hearing adjourned at 13:17, Ramirez caught Elena before she could sit. "The judge will hear arguments at two," the senator said. "Vasquez wants you there."

Elena blinked. "Today?"

"Today," Priya confirmed, already gathering binders. "Emergency docket."

Adrian rubbed the bridge of his nose. "Sterling's driver is outside."

Elena gathered her sea glass and compass, fingers trembling. The hearing room buzzed with reporters shouting questions. Naomi shielded them, guiding the trio through a side corridor lined with portraits of historical debates. Outside, humidity smacked Elena like a wave. Sirens wailed in the distance. The Capitol dome gleamed against a sky thickening with afternoon heat.

As they descended the steps, Elena's phone chimed once more. A single sentence from Talia scrolled across the screen: \textit{Artemis captain triggered failsafe. Boarding team sealed the compartment but we need your chemical breakdown now.} Her vision tunneled.

"Priya," she said, voice thin. "We have to send specs before the failsafe dissolves the pods."

Priya looked at the text, then at Elena. "We'll do it en route to the courthouse," she said. "You read the hazard mitigation. I'll call the judge's clerk if we run late."

They piled into the SUV, doors slamming like the crack of a starting gun. Elena flipped open her tablet, fingers flying over schematics, converting chemical jargon into step-by-step neutralization instructions. Outside the tinted windows, Washington blurred—a city of monuments and barricades. Inside, their war continued, the tide pulling them toward a courtroom even as the ocean demanded attention.

She hit send just as the SUV turned toward the federal courthouse. Talia's reply came almost immediately: \textit{Instructions received. Coast Guard deploying foam. Hold the line in D.C. We'll hold it on the water.}

Elena let her head fall back against the seat, eyes closed. Exhaustion tugged at her bones, but the current remained relentless. Ahead waited Judge Vasquez, Blue Current's legal hydra, and the possibility of halting further sabotage. Behind her, the \textit{Artemis Star} strained against the Coast Guard's grip. Every tide converged.

The SUV stopped. Priya squeezed Elena's hand once. "We do this," she said.

Elena straightened, smoothing her suit, and stepped into the afternoon heat. The courthouse doors loomed, glass reflecting a sky freighted with thunderheads building over the Potomac. She squared her shoulders and walked toward the next battle, the compass cold against her heart.

\noindent\textit{Testifying while the \textit{Artemis Star} sat one trigger away from catastrophe forced me to move between marble corridors and engine rooms without leaving my seat. Every spec sheet I sent from the back of that SUV was a reminder that policy only matters if it reaches the people hauling foam onto a freighter in a storm. Tomorrow's arguments have to keep that urgency coursing through them.}
