\chapter{Ebb Glass}

The overnight shuttle banked low over the Chesapeake, wing lights glimmering like buoys strewn across the dark. Elena watched silt-laden water curl against the shoreline, the plane's shadow drifting over marsh and mangrove before dissolving into dawn. Exhaustion pressed behind her eyes, but sleep refused to claim her. Too much adrenaline. Too much ache. The compass rested cool beneath her blouse, a steady weight against a heart that no longer understood rest.

Adrian sat beside her, jacket folded across his lap. He had loosened his tie hours ago; now it lay coiled like shed skin on the seat between them. Through the window's reflection she saw his profile—jaw shadowed with stubble, eyes fixed on the horizon where the bay blurred into sky. He looked, she thought, like someone standing on a pier at low tide, waiting to see what the water would reveal when it fell away.

"I keep replaying the boardroom," he said quietly, voice husked with exhaustion. "Trying to decide if there was a moment I could have argued harder."

Elena turned toward him. The cabin lights cast amber across his features. "You walked away before it swallowed you. That was the hard argument."

He huffed a laugh devoid of humor. "You make leaving sound noble."

"Sometimes not drowning is the noblest thing we can do." She let her shoulder rest against the seat, inches from his. Their flight attendant dimmed the cabin. Outside, the first blush of sunrise painted the water copper. "What are you going to tell your father?"

"That I'm done cleaning up his tides." Adrian's gaze never left the window. "He'll call it betrayal. Maybe it is. I still feel the tug." He shifted, the leather seat creaking. "You? Geneva in two weeks, a federal monitor arriving tomorrow, a town that will greet you with fireworks and demands. When do you breathe?"

"When the tide turns." The answer slipped out before she could temper it. "Or when the reef hums. Or when the café smells like cinnamon." Marco. The name rose with a mix of comfort and pressure. She imagined his hands flour-dusted, his smile easy. Longing twined with guilt.

They landed in Wilmington just after dawn. A loaned SUV idled outside the terminal, Naomi at the wheel despite bloodshot eyes. "Three hours to Marisport if traffic behaves," she said, passing back a thermos of strong coffee. "Commander Patel's team beat us there. Priya's on a conference call chasing shell companies."

The highway unfurled, bordered by pine and glimpses of water flashing through marsh grass. Adrian dozed for snippets, head resting against the window, but every time the SUV hit a rough patch he jolted awake. Elena stared at the tidal creeks that veined the landscape, each one glittering with the morning's pale light. The closer they drew to Marisport, the tighter the band around her chest.

They crested the final rise. Marisport sprawled below: harbor studded with fishing boats, rooftops shining damp from night fog, the lighthouse a clean white slash against cobalt sky. Morning gulls wheeled. The scent of salt and fried dough drifted up the hill. Home. Elena's throat closed.

Naomi dropped them at the Institute before heading to the coalition hub. The cedar siding glowed honey in the early sun. Volunteers already lined the loading dock, unloading crates of reef sensors. Ignacio stood among them, beard damp with dew, voice booming instructions. When he spotted Elena, he lifted both arms. "Look who rode in on the federal tide!"

She laughed, the sound raw. He crushed her in a hug that smelled of diesel and salt. "We watched every hearing," he said, eyes suspiciously wet. "You made the senators choke on their own suits."

"We had a whole harbor behind us," she replied, glancing past him to where Talia supervised a cluster of teenagers coiling hoses. The lab buzzed like a reef at dawn.

Marco emerged from the crowd, apron streaked with flour, hair wind-tossed. He carried two paper cups. Relief flooded his features when their eyes met. "You made it," he breathed, wrapping her in his arms. Cinnamon, citrus, the grounding warmth of him—it flooded her senses. She folded into the embrace, inhaling the familiar. His heartbeat thudded steady beneath her ear. Safe. Known.

"I promised," she whispered. The guilt she'd been bracing for didn't strike as sharply as she'd feared. Instead, she felt suspended between tides: the urgent current of the battles she had fought with Adrian and Priya, and the anchoring pull of the life she'd built with Marco.

When they parted, Marco offered one cup to Adrian. "Black, no sugar," he said. "You look like you need it."

Adrian accepted, surprise flickering across his face before he nodded. "Thank you."

The morning blurred into triage. Elena briefed the staff on the monitor's arrival, reviewed coral stress data, assigned dive rotations. She moved through the labs like a conductor orchestrating a fragile symphony. Each time she glanced up, she caught Adrian shadowing her, tablet in hand, quietly integrating himself into workflows—coordinating with Naomi on press protocols, fielding calls from coalition partners who now looked to him as a bridge between the old guard and the insurgent tide.

By noon, the sun burned white. Elena escaped to the rooftop garden, the only place where the wind could strip the courthouse's stale air from her lungs. Succulents basked in terracotta pots. Sea lavender swayed in planter boxes. Below, the harbor shimmered. She leaned against the railing, closing her eyes as salt-laden breeze kissed her face.

Footsteps scuffed. Adrian joined her, rolling his sleeves to his forearms. The inside of his wrists bore faint indentations from watchbands and cufflinks—marks of an old life. He braced his hands on the railing, shoulders bowed. "Naomi says the press wants a statement about my resignation," he said. "Part of me wants to disappear." His mouth quirked. "The rest wants to stand on the seawall with a bullhorn."

"You did something rare," Elena said. "You changed course mid-tide. People are going to stare."

He looked at her, the blue-gray of his eyes flecked with green in the sunlight. "How do you keep doing it? Standing there while they dissect you?"

She let her gaze drift to the reef markers bobbing beyond the breakwater. "I remind myself the sea doesn't care if I'm tired or afraid. It keeps moving. I can drown in it or learn its rhythm."

"And the rhythm brought you back to him," Adrian said softly. "To Marco." The name held no derision, only observation. "He seems... solid."

"He is." Elena traced the railing's worn paint. Splinters caught the pad of her finger. "He kept the harbor fed while we were in D.C. He turned the café into a command center. He has more patience than the tide." Saying it out loud felt like reciting a vow she had written years ago. Yet a tremor threaded through. "He deserves someone who isn't always running headlong into storms."

"Maybe storms are what you are," Adrian said. His voice roughened. "Maybe that's why I keep ending up in the eye with you."

The words hung between them, delicate as salt crystals. Elena's pulse stumbled. The rooftop seemed to tilt, the world narrowing to the space between their shoulders. She wanted to step away, to reassert boundaries shaped by years of choices. Instead, she stayed rooted, the garden's soil scent mingling with the ocean's brine.

Below, the tide slid over oyster beds, whispering against pilings. Elena inhaled. "We can't pretend those storms aren't complicated," she said finally. "We owe people honesty."

Adrian nodded. "Starting with ourselves." He pushed away from the railing, giving her space. "I'm heading to the coalition hub. Naomi's prepping statements. Priya's got leads on a funding lattice that might explain how Blue Current kept paying mercenaries. She asked if you can review sensor invoices tonight."

"I'll be there," Elena said. The prospect of more spreadsheets should have exhausted her, yet a sliver of anticipation sparked. The work was a tide she knew how to navigate.

As the sun slid westward, Elena made rounds through the lab. Volunteers scrubbed equipment. Laptops hummed with data uploads. The hum of community buoyed her like lift from a wave. Yet beneath it pulsed a quieter rhythm—the awareness of Adrian's presence, the memory of his voice on the rooftop, the unspoken acknowledgement that something between them had shifted. Not a cresting wave yet, but an undercurrent.

She caught Marco near closing, wiping down tables at the café. The engagement party board sat propped against a wall, sticky notes detailing menu possibilities. "Tonight, after the hub?" he asked without turning, the question threaded with hope and fatigue. "We could watch the harbor from the lighthouse. Mom's been hoarding fireworks since summer."

Elena hesitated. The thought of the lighthouse's lantern room, of Marco's arm warm around her waist, tugged at her like a familiar tide. Yet Priya's request pressed against her ribs. "I promised Priya I'd help audit invoices," she said. "She thinks there's siphoning we missed."

Marco set the rag down. "You're always fighting."

"Because the fight doesn't end." She stepped closer, resting her forehead between his shoulder blades. He stiffened, then melted. "I'll be back before midnight. We'll watch the tide from our roof instead."

"I'll hold you to that," he murmured, turning to kiss her gently. His lips tasted of cafecito and determination. She tried to memorize it.

Night fell. The coalition hub thrummed under fluorescent lights. Priya spread spreadsheets across a table, her eyeliner smudged, hair twisted into a knot held by two pens. "Found three shell nonprofits routing money through regional development grants," she said without preamble. "Names sound like craft beer flavors. Tidecraft Initiative. Harbor Helix."

Elena leaned over her shoulder. Numbers blurred into channels and current speeds in her mind. "These invoices coincide with shipments we flagged last month," she murmured. "If they're feeding mercenaries, they've embedded in the same networks that fund municipal projects." Her stomach knotted. "That's not just Blue Current. That's the infrastructure we rely on."

Adrian joined them, sleeves rolled high. The faint scent of bergamot clung to him, tempered by engine grease from the maintenance bay he'd just toured. He placed two cups of tea beside them. "Naomi thinks Tidecraft ties back to a maritime lobbying firm my father uses."

Elena met his gaze. Something steely glinted there—resolve laced with fear. "Then we tear it out by the roots," she said. The words tasted like brine.

Hours later, after Priya chased the last email and Naomi collapsed onto a couch, Elena walked home along the boardwalk. The bay lay dark, tide receding. She clutched the compass through her coat, feeling the metal warm against her skin. Above, the lighthouse beam swept slow arcs over water. In its rotation, she glimpsed Adrian standing alone on the far end of the pier, phone pressed to his ear, face lit by the beam's sweep. His posture spoke of battles still waged.

She almost called out. Instead, she watched as he lowered the phone, shoulders sinking. For a heartbeat he turned toward her. Moonlight silvered his features. The space between them filled with the scent of salt and night-blooming jasmine. She felt the pull, tidal and inevitable.

Then the lighthouse beam swung away, carrying him back into shadow. Elena continued home, steps measured with the cadence of waves dragging pebbles across sand. Inside, Marco slept curled on the couch, television flickering low. She covered him with a blanket, traced the line of his brow, and whispered a promise she wasn't sure she could keep: "I'm here."

The tide outside sighed, restless even at low ebb. Elena stood in the doorway, listening until the rhythm steadied her heartbeat. The day had taken everything she had and offered back only questions. Yet beneath fatigue, a strange clarity glimmered: storms had carved new inlets in her life, and the water rushing through them carried both danger and light. She would have to decide which currents to follow before the next tide turned.

\noindent\textit{Tonight proved that emotional fault lines can crack even when the spreadsheets line up. The rooftop conversation with Adrian and the café promises with Marco reminded me that every audit we run on corrupt funds needs a mirror held up to the ways I ration truth. Before I chase another shell nonprofit, I have to decide how honest I'm willing to be about the storms inside my own harbor.}
