\chapter{Spring Tide Pressure}

The morning they unveiled the NorthCross dossier, Geneva shimmered under a sun that belied the chill in the air. Elena barely tasted her coffee. Priya had been awake all night finalizing exhibits, eyes ringed in dark circles. Adrian paced like a caged current, phone buzzing with messages from regulators and journalists.

"Swiss authorities scheduled a closed session in two hours," Priya announced, sliding encrypted drives into a waterproof case. "Once we present, there's no turning back."

"Good," Elena said, though her stomach flipped. She checked messages from home: Talia reporting calm seas, Ignacio prepping a celebratory boil "for when you topple the giants," Marco sending a weather update with a note: \textit{Storm brewing Thursday. I'll hold the docks. Come home safe.} His steady handwriting made her chest ache.

They walked to the International Oversight Council building, an austere structure overlooking the lake. Security was tight—metal detectors, badge scans, armed guards whose expressions betrayed curiosity. Inside the conference chamber, representatives from multiple countries sat behind curved desks. Navarro occupied a seat near the center, flanked by lawyers. She kept her gaze fixed ahead, jaw locked.

Priya led the presentation with surgical precision. She outlined NorthCross's structure, projected wire transfers, named shell companies. Elena supplemented with testimony from community partners harmed by withheld funds. Adrian delivered the coup de grâce: a statement detailing board votes, memos from his father authorizing "strategic partnerships" with paramilitary contractors. His voice trembled but held.

The council's chair, a stern woman with salt-streaked hair, listened without visible reaction. When the presentation ended, she leaned forward. "Ms. Navarro, do you contest these records?"

Navarro's lips thinned. "NorthCross supports security for critical infrastructure. Any misuse by subcontractors—"

"Is your responsibility," the chair cut in. Murmurs rippled. "Effective immediately, NorthCross operations are suspended pending investigation. Assets frozen." The gavel struck. Navarro's composure cracked, rage flashing across her features.

Outside, cameras and microphones swarmed. Elena delivered a statement emphasizing community-led oversight. Adrian announced his cooperation with Swiss prosecutors. Priya declined comment, which the press interpreted as ominous. As they headed back to the hotel, a man brushed against Elena, slipping something into her pocket. Instinct honed from years of protests made her spin, but he melted into the crowd.

She fished out a folded note. \textit{Tides rise. Anchors sink. Choose which to save.} Her heart stuttered. She showed Priya.

"Navarro's dogs," Priya muttered, scanning for tails. "Security detail stays glued to you both." She signaled to the Swiss guards assigned to them. "Double coverage."

Back at the hotel, Naomi called with a grim update. "The lab's sensors detected interference along the eastern reef," she said. "Someone jammed the data stream for six minutes. Talia sent a crew—found a drone tangled in the kelp, broadcasting coordinates to an offshore vessel."

"Where's the vessel now?" Elena asked, pulse spiking.

"Coast Guard tracked it but lost signal near the shipping lanes," Naomi said. "Patel thinks they're testing response times." Her voice tightened. "They're probing for weaknesses because they know you're away."

Elena gripped the balcony railing, knuckles white. The lake sparkled deceptively serene. "We need to get back."

"We can't yet," Priya said, joining her. "Council wants follow-up testimony tomorrow. Regulators from Luxembourg are flying in." She touched Elena's arm. "We do more good staying."

As dusk fell, they attended a strategy session with allied delegations. Laisa and leaders from Ghana, Bangladesh, and Kiribati crowded around a table strewn with maps. They planned a coalition demand: an independent global resilience fund managed by community representatives. Elena contributed Marisport's data, Adrian offered legal pathways. The room buzzed with purpose, but a taut undercurrent remained.

After the meeting, as Elena and Adrian walked back through the plaza, a car screeched to a stop nearby. Two men in dark suits stepped out, one calling Adrian's name. "Mr. Sterling, your father requests a private conversation," he said, accent clipped.

Adrian stiffened. "Tell him I'm unavailable."

"He insists," the man said, advancing. The second man reached inside his jacket. Security guards materialized, intercepting. A tense standoff erupted. Elena's heart pounded. She grabbed Adrian's hand, pulling him back. The guards radioed for reinforcement. The men retreated with glares that promised this wasn't over.

"They're escalating," Adrian said, voice shaking. "He's trying to drag me away before I testify." Fear flickered. "We need to move hotels."

"Already arranged," Priya said when they relayed the incident. "Pack now. We'll relocate to the secure wing near the UN complex." She checked her watch. "And I'm filing charges against those goons."

They packed in haste, tension thick. Elena's hands shook as she folded clothes. She tucked the compass inside her coat, feeling its weight. "They won't stop until they silence us," she said.

"Then we get louder," Adrian replied, though his eyes betrayed exhaustion. He paused, stepping close. "If anything happens—"

"No," she interrupted. "Don't go there." She cupped his face, forcing him to meet her gaze. "We face it together." She kissed him, quick but fierce, sealing the promise.

Their new accommodations resembled a fortress—reinforced windows, guards at every entrance, badges required for elevators. The view still captured the lake, but now it felt like a moat. Elena struggled to sleep, mind replaying the note, the attempted abduction, the jammed sensors.

At 02:17, Naomi called. "We intercepted a coded transmission," she said. "NorthCross loyalists plan a `dual strike'—one targeting the Geneva delegation, the other hitting Marisport's reef during the upcoming storm."

"What does `targeting the delegation' mean?" Elena asked, dread pooling.

"Unclear," Naomi said. "The message referenced `harbor leverage' and `asset retrieval.' Patel thinks they're planning to kidnap Adrian to force a recantation."

Adrian paled. "Asset," he repeated, disgust twisting. "That's how they see me."

"The reef strike?" Elena demanded.

"Timed with the storm Marco mentioned," Naomi said. "They plan to release a chemical slurry upriver to ride the flood toward the reef modules." Her voice strained. "We can intercept if we mobilize volunteers now. But it'll take coordination."

Elena's pulse hammered. "We can't be in two places at once." The dilemma constricted her chest. Save Adrian or the reef. The threat she'd feared materialized. "We need contingencies." She turned to Priya. "How soon can we get home?"

"Earliest flight is after tomorrow's session," Priya said grimly. "Even if we left now, we'd arrive as the storm peaks." She rubbed her temples. "We need to split responsibilities."

Adrian gripped Elena's hands. "You lead the reef defense remotely," he said. "I'll handle Geneva security."

"They're targeting you," she shot back. "I won't leave you vulnerable."

"And I won't let them destroy everything you built," he said. "This is the test they wanted. We can't let them force a choice." His eyes shone. "We'll find a way to do both." The conviction sounded fragile.

Priya paced. "I can petition the council to delay tomorrow's session," she said. "If they refuse, we send recorded testimony and leave tonight." She pulled out her phone. "Naomi, activate contingency plan Delta." The line crackled as Naomi relayed orders to Marisport: volunteers to river checkpoints, Coast Guard to storm routes, Marco coordinating shelter for at-risk families.

Elena called Marco. He answered on the first ring, wind howling in the background. "Thought you'd be sleeping," he said.

"We intercepted a plan to dump chemicals during the storm," she said without preamble. "I need you to lead the dock watch."

"Already on it," he replied. No bitterness, only steady resolve. "Ignacio's flotilla is staging upriver. We won't let them through." He paused. "Elena—if they come for Adrian, you protect him."

Her throat tightened. "You don't owe me that."

"Maybe not," he said. "But the fight doesn't end because hearts break." Rain pounded on his end. "Bring him home. Bring yourself home. We'll hold the reef." The call ended before she could respond.

Elena lowered the phone, tears blurring vision. "He still chooses us," she whispered.

Adrian pulled her into a fierce embrace. "You built a harbor full of people like that," he said against her hair. "We're not alone."

They spent the remaining hours drafting remote commands, relaying sensor protocols, establishing secure communication lines. Priya negotiated with the council to accept pre-recorded testimony, buying them a narrow window to fly home after delivering statements at dawn. Security doubled their escort. The note in Elena's pocket felt heavier with each passing minute.

Before sunrise, she stood by the window, watching the lake's surface ripple under a rising wind. It looked almost tidal. She pressed the compass to her lips, whispering a plea to any force listening: let them hold both the man and the reef. The first streaks of dawn painted the mountains pink. The day they'd been hurtling toward was here. Choices loomed like storm fronts. She squared her shoulders, determined to face the spring tide without flinching.


\noindent\textit{Splitting our forces between Geneva security and a storm-battered harbor was the nightmare I'd dreaded, yet Marco's unwavering support over a howling phone line reminded me why we built redundancy into every plan. If enemies think forcing impossible choices will break us, they haven't met the people tying down boats upriver. We answer by refusing to let distance fracture our resolve.}
