\chapter{Stormglass}

The storm warning chart glowed bruise-purple on Elena Ruiz's laptop, a constellation of data points marching across the Atlantic. Outside the Institute's conference room, rain needled against the glass wall, whispering promises of the larger system gathering offshore. Dawn was still a rumor, the horizon a smudge beyond the harbor's sodium lights, yet the room hummed with life: maps unfurled across tables, portable radios crackling, coffee steaming in mismatched mugs.

"That's three separate models converging on landfall within seventy-two hours," Priya Singh said, tapping the projected map with a capped pen. Her hair was twisted into a high knot, stray curls frizzing in the damp. "If the cold front over the Carolinas stalls, we get the full brunt. If it pushes through, we still get gale-force winds and a storm surge pushing right over the reef." Her eyes flicked to Elena. "We need to decide which assets we can secure and which we let go."

Elena rubbed her thumb along the edge of a ceramic mug, aware of how the porcelain trembled against her pulse. The past two days had blurred into a cycle of cleanup, sleep in snatches, data entry, more cleanup. Now the spill's residue clung to the pilings in stubborn streaks, their progress measurable but unfinished. And here came the next tide. "We can't let the coral nurseries take direct surge," she said. "We move the suspended pods into the sheltered tanks, reinforce the stanchions with additional bracing, and pray the pumps hold." She inhaled salt-tinged air. "We also have to prepare the Institute to double as a shelter. The town will look to us whether we're ready or not."

Talia Ramos slumped into a chair with a thud, her teal hoodie damp at the cuffs. "The volunteers are still cycling out from the spill response," she said. "Half of them are running on caffeine and adrenaline. The other half are in bed because they literally collapsed after the third shift." She yawned, covering her mouth with the back of her hand. "I can reassign the science club to prep the dry lab as a medical station, but we need a morale plan before people mutiny."

"No mutinies on my watch," Priya murmured, though the corners of her mouth twitched. She slid a printed checklist toward Elena. "Emergency generator inspection at nine. Sandbag delivery at eleven. Mayor Liao scheduled an emergency management summit for this afternoon. You, me, and Adrian are on the agenda."

At the mention of Adrian, the air seemed to tighten. He was late, but not absent; his texts lit Elena's screen every hour with updates from the foundation's logistics team, photographs of pallets of supplies staged in the abandoned cannery warehouse, bullet-point summaries of calls with investors suddenly fascinated by Marisport's resilience.

"I'll brief the volunteers," Elena said. "Talia, send a message through the community channel: anyone available meets on the dock at six for tide reinforcement. We'll rotate shorter shifts." She rose, chair legs scraping against the tile. Her muscles protested—each movement a reminder of diving in cold water, hauling contaminated eelgrass, sleeping in wet hair. "We don't get to be tired yet."

"Already handled," Talia said. "I drafted the message at four when the storm alert pinged." She pulled her hood up, eyes soft despite exhaustion. "Take a minute to breathe before you go stand in the rain barking orders."

Elena almost laughed. "I'll inhale on the walk." She picked up her laminated tide charts, the corners frayed from years of handling, and headed into the corridor. The Institute felt different in pre-dawn: the humming tanks held their own glow, the air thick with the green scent of seawater and algae. In the rehabilitation ward, a rescued sea turtle lifted its head from a shallow pool, eyes ancient and placid. Elena paused, pressing her fingers to the glass. "Hold on," she whispered, unsure if she meant the turtle, the reef, or herself.

The dock behind the Institute was slick with mist. Volunteers clustered under the overhang, silhouetted against the bay's pewter sheen. Marco stood among them in his yellow slicker, passing out paper cups of coffee that steamed in the cold. His presence warmed her even before he caught sight of her and grinned, relief blooming on his face.

"Morning, Dr. Ruiz," he said, teasingly formal as he offered her a cup. "You're right on time for your own dawn sermon."

"I'll try not to lecture for longer than the tide cycle." She took the cup, the heat seeping into her palms, and faced the group. Talia joined her, tablet in hand.

"We have seventy-two hours," Elena began. The wind tangled her hair despite the braid she'd twisted, salt dampening every strand. "That gives us six full low tides to reinforce the nursery anchors, relocate the most vulnerable species, and tie down anything that can become a projectile." She scanned their faces: Mateo with grease smudged along his jaw from late-night generator maintenance; Mrs. Delgado, cane planted firmly, jaw set; high schoolers hugging borrowed rain jackets. "We'll work in pairs. No one goes into the water alone. Check on your neighbors. If someone looks like they're about to fall over, drag them to the café and feed them."

A ripple of laughter eased the tension. Marco lifted his cup. "I have cinnamon rolls proofing already. Consider it hazard pay."

"Hazard pay includes actual hazard prevention," Elena said, pointing at him. "You and Mateo are on generator duty after this. We can't lose power when the pumps need to run." She swallowed the rest of her coffee, the bitterness grounding. "First crew with me: we secure the eastern anchors before the tide turns."

They moved. Rope hissed through calloused hands. Sandbags thudded into position along the lower boardwalk. Talia jogged back and forth, logging assignments, her stylus tapping an urgent rhythm. Elena waded thigh-deep near the nursery platforms, the water numbing the cuts on her hands. Marco tossed her ratchet straps; she looped them around metal braces, tightening until the cords sang. The tide pushed and pushed; she pushed back.

By the time they finished the first round of reinforcements, the horizon blushed pink. The lighthouse's beam dimmed, surrendering to daylight. Rain softened to a mist. Elena's shoulders ached with the promise of bruises, but momentum held her upright.

"Breakfast delivery," Priya called from the top of the dock stairs, a bakery box balanced on one hip. Her normally pristine blazer was replaced by a rain jacket dotted with spray. "Eat while you can. The mayor moved the emergency summit to ten."

"Of course she did," Elena muttered, wringing water from her braid. She climbed the stairs, lungs protesting. The conference room smelled like yeast and wet wool. Adrian had arrived, a dark sweater clinging damply to his shoulders, his hair flattened by the weather. He stood beside the map table, hands braced on either side, gaze fixed on the storm track.

"Morning," he said. His voice held equal parts fatigue and focus. "The foundation's coastal response team is en route. They're bringing portable pumps, medical supplies, and—" He glanced at Priya. "—legal counsel to help process claims against the developers."

"Add storm prep to their to-do list," Priya replied. "We're operating as a unified command with the city. Elena, I need you to brief the mayor on the reef's role in storm surge mitigation. Adrian, you're handling the logistics update." She looked between them, a silent reminder that the town would watch every interaction for signs of fault lines.

Elena inhaled. "Let's go give the town a reason to believe we have a plan."

The emergency summit convened at the community center, its basketball court converted into a command hub. Folding tables formed a hollow square layered with maps, laptops, and stacks of forms. Representatives from the harbor master’s office, the volunteer fire department, the Coast Guard auxiliary, and neighborhood associations filled metal chairs. The air buzzed with the murmur of overlapping conversations and the metallic scent of anxiety.

Mayor Liao stood at the podium, her posture rigid. "Thank you for coming on such short notice," she began. "We have an incoming storm system with the potential to make landfall as a Category Two hurricane. We cannot afford to treat this as a distant threat. We act now." She gestured toward Elena. "Dr. Ruiz will outline our coastal vulnerabilities and assets."

Dozens of eyes pinned Elena as she stepped forward. She had spoken to this crowd before, but never under the weight of solvent-stained docks and storm projections colliding. She pulled up a slide on the large monitor: a topographic map of Marisport overlaying coral density data.

"The reef is our first line of defense," she said. Her voice sounded steadier than she felt. "Healthy coral dissipates wave energy by up to ninety-seven percent. The sections we've restored in the past five years sit here, here, and here." She tapped the areas glowing green. "These sections will take the brunt of the surge. If we lose them, the waves impact the marina and the lower town directly." She changed slides, revealing simulations of surge with and without the reef. Gasps rippled through the crowd as the second image flooded the boardwalk, the Lighthouse Café submerged to its windows.

"We can't rebuild a reef in three days," Elena continued. "But we can minimize damage. We're reinforcing nursery structures, relocating fragile specimens, and establishing underwater booms to trap debris before it strips the coral. On land, we need sandbags along the boardwalk, window shutters secured, and evacuation routes cleared." She met the gaze of Captain Hernández. "Your fleet becomes our evacuation vessels if the bridges flood."

He nodded, jaw tight. "We'll be ready."

Mayor Liao motioned to Adrian. He stepped forward, a tablet in hand. "The Sterling Foundation is staging emergency supplies at the old cannery: generators, water purification units, cots, medical kits," he said. "We're coordinating with regional partners to supplement what the state can send. The foundation will cover the cost of reinforcing shelters, including hazard pay for crews working through landfall." He paused, scanning the room. "All of this operates under the town's command. We're here to support, not direct."

An elderly man near the back raised his hand. "And what happens when the storm clears?" he asked, voice thick with skepticism. "We already got a toxic spill. Now a hurricane? How many hits can we take before this town breaks?"

"We prepare to rebuild before the storm makes landfall," Elena said. "We're organizing the Reef Revival Gala as a resilience fundraiser. Every dollar will go toward restoration and support for affected families. We can't stop the storm. We can decide what the town looks like afterward."

Murmurs swept through the room—agreement, doubt, fear. The mayor outlined evacuation timelines, the fire chief detailed shelter capacities, the school superintendent offered gymnasiums as additional space. Elena scribbled notes, her mind racing ahead to supply lists and volunteer rotations.

During a break, she stepped outside into the gray morning. The air tasted of ozone, the wind carrying the distant thump of waves slamming rocks. She leaned against the brick wall, breathing deep. Footsteps approached. Adrian stopped a few feet away, as if respecting an invisible boundary.

"You left before I could hand you this," he said, offering a waterproof folder. "It's the revised partnership agreement. Priya suggested we finalize language before the storm hits in case communications go down."

Elena took the folder, the plastic cool against her palm. "Are we really negotiating legal clauses with a hurricane inbound?"

"Apparently that's the only time we sit still long enough," he said, humor flickering across his face before fading. "Listen—I know the town is stretched thin on trust. If there's anything else we can deploy—"

"We need portable lab space," Elena interrupted. "If the Institute floods, we lose years of samples."

"Done," he said without hesitation. "I'll reroute the mobile research unit from the Providence team. It'll be here by nightfall." He hesitated, eyes searching hers. "How are you holding up?"

The question lodged beneath her sternum. "Functioning," she said. "That's the bar."

He nodded, accepting the half-answer. "I'll see you at the cannery in an hour. We'll inventory the supplies together." He turned toward the parking lot, rain spotting his sweater anew.

Elena watched him go, folder tucked under her arm. Wind whipped across the pavement, lifting the edges of posters taped to the community center doors: \textit{Resilience Rally Tonight — Harbor Pavilion — Bring Nonperishables and Hope}. The slogan had seemed corny when Priya drafted it at two in the morning. Now it felt like a lifeline.

The cannery smelled like rust and old stories. Once, the clatter of conveyor belts and the tang of brine had filled the cavernous space; now pallets of shrink-wrapped water jugs and crates labeled \textit{Emergency Lanterns} lined the floor in neat rows. Fluorescent lights buzzed overhead, casting everything in a stark glow. Volunteers in neon vests zipped between stacks, scanning barcodes, logging inventory on tablets loaned from the high school.

"You could run a small country out of here," Elena murmured to Priya, who was hunched over a folding table covered in paperwork.

"Don't tempt me," Priya replied without looking up. "State wants inventory by noon. FEMA wants daily updates. The foundation wants proof their money is buying goodwill." She shoved a clipboard toward Elena. "Sign off on the medical supplies. We need your certification to release controlled meds to the clinic."

As she moved through the aisles, Elena cataloged what they had and what they still needed. More tarps. Extra oxygen tanks. Backup batteries for the reef monitoring buoys. She made lists upon lists, each item a thread she refused to let slip.

At midday, Marco arrived with a convoy of volunteers pushing carts laden with trays from the café. The smell of arroz con pollo and roasted vegetables cut through the metallic air. He caught Elena between pallets, brushing a kiss against her temple.

"Eat," he ordered, pressing a plate into her hands. His eyes were rimmed with fatigue, but determination blazed there. "The café's running like a soup kitchen. Mamá's in full command."

"Remind me to knight her after the storm," Elena said around a mouthful of rice. "How's Mateo?"

"Rewiring the secondary generator with Ignacio. Apparently storm prep is the only thing that convinced your dad to let Mateo near his tools." Marco's smile was soft despite the chaos.

As if summoned, Ignacio Ruiz appeared, his limp pronounced but strides purposeful. He wore a battered raincoat and the expression of a man who had seen storms swallow boats whole. "The new buoys are secure," he reported. "But the outer channel markers are loose. I'll take a crew out at low tide to reset them."

"You're not supposed to be out on the water," Elena said automatically.

His eyebrows rose. "Since when do Ruiz men wait for permission from storms?" He softened, resting a hand briefly on her shoulder. "I'll take Mateo and Luis. We'll be careful."

She swallowed the instinct to forbid him. "Wear your life jacket," she said instead.

"Always do." He winked at Marco. "Make sure she eats. She gets mean when she's hungry." He disappeared among the pallets before Elena could retort.

The afternoon blurred into logistics. Elena met with the aquarium staff to coordinate relocating the sea turtle to a reinforced tank. She reviewed the Institute's emergency comms plan, ensuring volunteers had radio call signs. She recorded a video message for the school's social media account, reminding teenagers to secure their kayaks and check on elderly neighbors. Every task felt both essential and insufficient.

By late afternoon, the rain intensified, drumming against the cannery's metal roof. Priya called for a break. "Harbor Pavilion in thirty," she announced. "Resilience Rally. Wear something dry if you can find it."

The Harbor Pavilion buzzed with organized chaos. String lights twinkled overhead, reflecting in puddles on the concrete floor. Tables overflowed with donated canned goods, baby supplies, batteries. Children chalked messages on the damp concrete—\textit{We Love Our Reef}, \textit{Stay Strong Marisport}. The air smelled of rain and cinnamon from the churros Isabela Alvarez insisted on frying as a "goodwill gesture."

Mayor Liao took the stage first, flanked by council members and the police chief. "This rally isn't about pretending we're not scared," she said into the microphone. "It's about facing that fear together. We have supplies coming in, volunteers on standby, shelters ready. Now we need to support each other with more than sandbags." She nodded toward Elena. "Dr. Ruiz?"

Elena stepped forward to applause that felt too loud for the tightness in her chest. She spoke of the reef's resilience, of the volunteers' grit, of the way Marisport had already turned a toxic spill into a coordinated response. She introduced the Reef Revival Gala's transformation into the Reef Resilience Fund, detailing how donations tonight would fund post-storm restoration and direct aid. She kept her voice steady, even when her heart hammered. When she finished, she saw Marco near the back, clapping with his whole body, pride shining through fatigue.

Adrian followed, his speech shorter. "We're here because this town taught us what responsibility looks like," he said. "Every Sterling Foundation resource is at your disposal. Hold us to that." He stepped back, absorbing the mingled cheers and wary looks.

After the speeches, the pavilion shifted into motion: donations sorted into neat stacks, signup sheets filling as fast as Priya could flip pages, Talia pressing laminated checklists into waiting hands. Elena moved through it all accepting hugs, promising updates, pocketing the rosary beads Mrs. Delgado pressed on her. The town thrummed with nervous energy transmuted into purpose.

As the rally wound down, thunder rolled in the distance. The first outer bands were still hundreds of miles away, but the atmosphere already felt charged. Elena lingered near the edge of the pavilion, watching rain streak across the harbor lights. Adrian joined her, hands tucked into his coat pockets.

"You were born for this," he said quietly.

"For storms?" she asked, half a laugh escaping.

"For standing between chaos and community and convincing both to calm down." He glanced sideways at her. "Marisport listens to you."

"Marisport listens to anyone who shows up when it matters." She looked past him to where Marco stood talking with Ignacio, their heads bent close. The sight tugged at something tender. "I just happen to be loud enough to get their attention."

"You also happen to be the one person who can braid science, emotion, and logistics into something people understand." His voice softened. "I spent years building models in boardrooms. None of it felt real until I watched you on that dock at midnight."

Elena exhaled slowly. "You left without a word," she said before she could stop herself. "Do you know what that did to me?"

His shoulders stiffened. "Yes," he said. "I also know what staying would have done. My father wanted me to sign falsified safety reports. If I'd refused publicly, he would have dragged the Institute through court until it bled dry. If I'd stayed quietly, I'd have become him. Leaving felt like the only option."

Elena stared at the harbor, the water a dark mirror. "You could have told me," she whispered.

"I was nineteen and drowning," he said. "I didn't know how to ask for help without taking you under."

Silence stretched, filled only by the patter of rain on the pavilion roof. Finally, Elena said, "We're not teenagers anymore. If we're doing this—this partnership, this fight—we do it with honesty."

"Agreed," he said. "No more disappearing."

She stepped away, letting the night swallow the conversation before it sank deeper than she could afford.

Back at the café, the Alvarez family had transformed the dining room into a staging area. Cases of bottled water lined the walls. Folding tables groaned under the weight of sandwiches wrapped in wax paper. Volunteers moved with weary efficiency, packing meal kits, labeling containers for shelters.

"Engagement party 2.0," Mateo said, waving a roll of tape. "Featuring the always romantic aroma of canned beans."

"We'll make up for it," Marco told Elena, handing her a label gun. "After the storm, we'll find a tide pool somewhere quiet and have a picnic. No guests."

"Deal," she said. Their fingers brushed as she took the gun. Electricity shot up her arm—a reminder that amid logistics and old ghosts, love still threaded through.

They worked until nearly midnight before stumbling upstairs. Elena skimmed the partnership agreement, added her signature, and fired it to Priya and Adrian with a brief note. Marco returned with tea, relayed his father's request to shutter the café for storm prep, and she agreed without hesitation. When he quietly mentioned hearing about her sunrise meeting with Adrian, guilt flared; she apologized, promised no more secrets, and they sealed it with interlaced fingers while rain tapped the windows.

Sleep came in fragments. Every creak of the building pulled Elena back to consciousness. At three a.m., she rose and padded to the window. The street below glistened under streetlights, rain falling in slanting sheets. Across the harbor, lightning flickered like distant camera flashes. She checked the latest weather models on her phone. The storm had strengthened. Landfall projections shifted closer to Marisport with every update.

By five, she was back at the Institute. The lobby thrummed with activity despite the hour. Volunteers stacked crates against interior walls to prevent flooding. The turtle rehab tanks had been reinforced with steel braces. Portable heaters hummed in corners, ready to ward off the chill when the power inevitably flickered.

"The mobile lab arrived," Talia called, waving Elena toward the parking lot. A gleaming trailer sat hitched to a foundation-branded truck, its sides emblazoned with \textit{Sterling Coastal Response Unit}. Inside, stainless steel counters gleamed, microscopes bolted down, sample freezers humming softly. Elena ran a hand along the counter, impressed despite herself.

"We could run a full analysis from here," she said.

"That's the plan," Adrian replied from the doorway. He wore rain pants and a waterproof jacket, the professional veneer replaced by practical readiness. "We stocked it with backup reagents, portable spectrophotometers, everything you requested." He held up a sealed envelope. "The board unanimously approved the emergency funding. They also approved the scholarship clause."

Elena took the envelope, heart stuttering. "That was fast."

"Disaster has a way of clarifying priorities," he said. "Also, Priya threatened to livestream the board meeting if they dragged their feet." His smile flashed, quick and genuine. "Fear of public embarrassment is a powerful motivator."

"Remind me to send her flowers," Elena said dryly. She tucked the envelope into her bag. "Briefing in twenty. Let's make sure the divers know the new protocols."

The day unfolded in overlapping waves. Ignacio returned from resetting channel markers, cheeks ruddy, announcing the buoys would hold. Priya juggled calls with state emergency management while overseeing sandbag placement along the Institute's lower level. Marco coordinated meal deliveries to the shelters, his voice hoarse but steady over the radio. Talia led the Providence response team through underwater remediation plans, her enthusiasm slicing through fatigue.

In a rare lull, Elena escaped to the observation deck. The bay writhed under the increasing wind, whitecaps stitching the water into a froth. The horizon had vanished beneath a wall of bruised clouds. She pressed her hands to the glass, the coolness grounding.

Her phone buzzed with a message from the high school: the gym roof still leaked. Elena rerouted volunteers with tarps, called the superintendent before the thought could curdle into panic, and kept the shelter plan intact.

By evening, the wind howled through the rigging of docked sailboats. Rain lashed sideways, plastering hair to faces, soaking through supposedly waterproof jackets. The first outer bands arrived faster than forecasted, sheets of water marching across the bay. Lightning strobed behind the clouds, the thunder rolling seconds later.

Inside the Institute, the lights flickered once, twice, steadied as the generators kicked in. Volunteers huddled around radios, listening to the coast guard updates. Priya paced with a satellite phone pressed to her ear. Adrian anchored the mobile lab, double-checking seals. Talia distributed headlamps.

Elena moved among them, checking on each team, offering a nod, a squeeze of a shoulder, a reminder to hydrate. She paused at the rehab tank. The sea turtle blinked slowly, unbothered by human storms. "We're staying," she told the reptile softly. "We're not letting this place flood without a fight."

Marco appeared at her side, water dripping from the brim of his hat. "The café basement's secured," he reported. "We moved the roaster upstairs. Mamá threatened anyone who touches it with bodily harm." He sobered. "Dad's staying at the shelter with the early evacuees. He wanted me to tell you to watch the barometric pressure. Says when it drops like a stone, that's when the storm's teeth show."

"I'll keep one eye on the altimeter," Elena promised. She leaned into him briefly, absorbing his warmth. "You heading to the shelter?"

"Not yet. I promised to help Ignacio with the boats through high tide." He brushed rain from her cheek. "I'll be back before the worst of it."

"Marco—"

"I know." He kissed her forehead. "I'm not a hero. I'm just stubborn."

"Stubborn keeps this town upright," she said. "Be careful."

He jogged toward the dock, joining Ignacio and Captain Hernández as they secured lines with practiced hands. Elena watched them through the glass until rain obscured them completely.

The wind intensified, a steady roar punctuated by higher-pitched whines as gusts rattled loose shutters. The Institute's walls creaked. Somewhere down the hall, a door slammed. Volunteers called updates over the radio every fifteen minutes, voices crackling with static. The mobile lab's sensors pinged as water levels rose inch by inch along the shoreline.

At eight p.m., the National Weather Service upgraded the storm to a hurricane. The notification blared across every screen, the red banner stark against the blue radar swirls. Elena read the update twice, absorbing the words: \textit{Hurricane Calista expected to make landfall near Marisport within 36 hours. Storm surge 8-10 feet. Prepare for life-threatening flooding}. Her stomach lurched.

"We're on lockdown," Priya announced, raising her voice over the wind's howl. "Once the sustained winds hit fifty miles per hour, no one leaves the Institute unless it's a life-or-death emergency." She locked eyes with Elena. "Text your father and Marco. Now."

Elena's fingers shook as she typed. \textit{Winds hitting threshold. Stay put. Check in every hour}. Marco responded within seconds: \textit{Tying down last vessel. Heading in}. Ignacio: \textit{Already in. Storm's teeth are sharp}. The words steadied her.

Minutes stretched, elastic and cruel. The lights flickered again, plunging the lobby into brief darkness before emergency strips glowed along the floor. The generators hummed louder. Rain battered the roof like fists. The barometric pressure monitor on the wall ticked downward, numbers dropping in a steady cascade.

Marco burst through the Institute doors soaked to the bone, hair plastered to his forehead, eyes bright with adrenaline. Elena exhaled a breath she hadn't realized she'd been holding. He wrapped his arms around her, drenched jacket and all, anchoring himself with the contact.

"Lines are double-secured," he said into her hair. "Ignacio and Luis are bedding down in the maintenance closet with space heaters."

"Good." She pulled back enough to study his face. "You scared me."

"Ditto." His smile was grim but real. "Now what?"

She looked toward the observation deck. Beyond the glass, the bay had vanished under a wall of rain. The lighthouse beam cut through the downpour in fragmented arcs. The storm roared, relentless.

"Now we hold," she said. "We hold until the tide turns."

A sound like thunder but closer—an impact—shuddered through the building. Elena's heart lurched into her throat. "Report!" she called over the radio.

"North storage bay!" Talia's voice crackled. "Debris just slammed into the exterior wall!"

Elena grabbed her rain jacket, adrenaline slicing through exhaustion. "Priya, coordinate internal teams," she ordered. "Adrian, with me." She sprinted down the corridor, Marco on her heels despite the lockdown order. Wind whipped down the hallway, carrying a fine mist. At the storage bay, a section of wall shuddered under the weight of a toppled sailboat mast, the wood gouging into the siding. Rain sprayed through the splintered gap.

"We need to brace it before the whole wall gives," Adrian shouted over the gale.

"Get the interior support beams!" Elena yelled. "Marco, sandbags along the base! Talia, clear the area!"

They moved in practiced chaos. Metal braces clanged into place. Sandbags thudded against the floor, forming a barrier against the invading water. Elena pressed her shoulder against the wall, muscles straining, as Adrian wedged a beam into place. Marco shoved sandbags until his arms trembled. Talia sealed the gap with tarps and industrial tape, her face set in fierce concentration.

For a heartbeat, the storm seemed to test their resolve, wind pushing with brute force. Then the braces held. The wall groaned but stayed upright. Water seeped, but it slowed. Elena exhaled, lungs burning.

"That's one," she said, breathless. "Keep eyes on the exterior sensors. We can't lose another wall."

They stumbled back into the hallway, soaked and shaking. Priya met them with towels and a glare that softened into relief. "Don't make me write your eulogies," she snapped. "We're not losing anyone tonight."

Elena nodded, wiping rain from her face. The storm raged on, relentless, but the Institute stood. For now. She knew the worst was yet to come—the eye would arrive, the surge would crest, the wind would test every anchor. Yet as she looked at the faces around her—Priya's fierce steadiness, Talia's determined fire, Marco's unwavering presence, Adrian's grim resolve—she felt the tide of fear recede just enough to breathe.

Outside, Hurricane Calista hurled her first full-throated scream against Marisport. Inside, Elena squared her shoulders, ready to meet whatever came next.

\noindent\textit{Calista's first assault taught me that leadership is as physical as bracing a buckling wall and as intimate as texting the people you love to stay inside. Feeling Marco's soaked arms around me while Adrian wedged beams into place made clear that our strange alliance is forged under pressure, not press releases. When the next impact slams the Institute, I'll remember that we already proved we can hold.}
