\chapter{Court of Currents}

The federal courthouse smelled of polished stone and tension. Elena stood in the security line between a schoolteacher petitioning for disaster relief and a lobbyist with a lapel pin shaped like an oil derrick. Her binder dug into her palm. Priya murmured statute numbers under her breath. Adrian scrolled through emails, jaw set. Outside, humidity pressed against the glass like a damp hand. Inside, the air was chilled to the edge of discomfort, as if justice required refrigeration.

"Remember," Priya whispered, "Judge Vasquez clerked for an environmental rights group before the bench. She respects data. But she hates grandstanding."

"I don't have energy to grandstand," Elena replied. Her muscles ached from the flight and the hearing, but clarity cut through the fatigue. The compass lay cool against her sternum. The sea glass warmed with her skin.

A marshal escorted them to a waiting room paneled in mahogany. Bottled water sweated on a credenza. Through a half-open door, Elena glimpsed Blue Current's legal team—expensive suits, perfectly knotted ties, faces composed into polite neutrality. At their center stood Victor Vance, blue-gray hair immaculate, eyes the color of fogged steel. He met Elena's gaze for a fraction of a second, mouth curving into a tight smile that never touched his eyes.

"Don't look at him," Priya muttered. "He's bait."

Elena inhaled slowly. The waiting room's clock ticked louder than the roar of the transport's engines. Her phone remained on the secure network, notifications muted. She resisted the urge to check, trusting Talia's updates would break through if critical. A NOAA liaison entered, tablet tucked under one arm.

"Dr. Ruiz?" the liaison asked. "Commander Patel sends word: foam deployment is reducing corrosion on the chemical pods. But the freighter's crew initiated ballast purges to destabilize the boarding ladder. Coast Guard is requesting guidance on neutralizing the purge without triggering the failsafes."

Priya's eyebrows shot up. "In the middle of a hearing?"

"We can step into the hall," Elena said, throat tightening. She followed the liaison into a nook lined with historical photographs. Pulling up schematics on her tablet, she traced out the ballast system Blue Current engineers had boasted about during a trade show two years earlier. "They're using the purge valves to flood the lower compartments," she explained. "If you flood them slower than the failsafe threshold, the failsafe won't trigger. Pair the foam with a temperature drop. The chemicals react slower in cold water." She typed instructions with shaking fingers. "Tell Patel to divert chilled seawater from the firefighting system."

The liaison nodded, already relaying the message through an earpiece. Elena wiped damp palms on her slacks before returning to the waiting room. Priya eyed her.

"You good?"

"I'll rest when Blue Current is broke," Elena replied. Priya's quick grin flashed, fierce and approving.

A bailiff opened the courtroom doors. "All rise," she intoned. The gallery filled with coalition members, Sterling staffers, and a handful of reporters. Elena caught sight of a young man in a Coast Guard uniform recording the proceedings on a body cam. Beside him sat Naomi, flanked by community leaders from Chesapeake fishing towns. Their presence radiated solidarity.

Judge Vasquez entered, robes sweeping, expression inscrutable. Lines fanned from the corners of her eyes, testament to decades spent squinting at briefs. She settled behind the bench, gaze sweeping the courtroom.

"We're here on the emergency injunction filed by the Department of Justice on behalf of the Marisport Resilience Lab and allied communities," she said. "Counsel, announce your appearances."

Priya rose. "Priya Malhotra for the plaintiffs, Your Honor." She gestured to Elena and Adrian. "With me are Dr. Elena Ruiz and Adrian Sterling, appearing as witnesses." A DOJ attorney introduced herself. On the other side, Blue Current's counsel stood smoothly.

"Robert Hensley for Blue Current Infrastructure and affiliated entities," he said. "Mr. Victor Vance is present."

Judge Vasquez inclined her head. "Noted. Ms. Malhotra, you may proceed."

Priya launched into a surgical argument. "Blue Current attempted to sabotage federally permitted resilience infrastructure during a declared state of emergency," she said. "We have physical evidence, eyewitness testimony, and financial records connecting corporate leadership to that attempt. We seek an injunction halting Blue Current operations along the eastern seaboard pending investigation, and the appointment of a federal monitor." She moved between podium and counsel table with the precision of a fencer. When she cited the Clean Harbors Act, her voice carried the cadence of someone who had memorized entire case law volumes on insomnia-driven nights.

Hensley countered with a calm smile. "Your Honor, Blue Current categorically denies authorizing these actions. We are the victims of rogue employees—"

Priya cut in. "Rogue employees with corporate-issued satphones and payroll disbursements signed by Mr. Vance?"

Hensley spread his hands. "Your Honor, Ms. Malhotra's theatrics—"

"Counsel," Judge Vasquez warned. "Let's keep to the facts."

Priya shot Hensley a razor glance and returned to her notes. "We move to admit Exhibits 14A through 14F." She displayed photographs of the charges, the intercept logs, the intercepted emails. Adrian took the stand, voice even as he described board votes, memos, attempts to shutter oversight committees. When it was Elena's turn, she swore in and sat, palms damp.

"Dr. Ruiz," Priya began, "describe the impact the sabotage attempts would have had on Marisport if successful."

Elena kept her eyes on Judge Vasquez. "Our reef modules are engineered to absorb storm energy. Dissolving them would have removed the buffer between surge and seawall. We have modeling that shows a five-foot increase in inland flooding if the charges detonated. Our shelters would have been underwater." She swallowed. "We would have lost lives."

Hensley cross-examined with a thin smile. "Dr. Ruiz, isn't it true that your lab stands to gain financially if Blue Current's projects are halted? Increased grants?"

Elena met his gaze without flinching. "We stand to gain breathable air and intact homes. Any grants would fund protective infrastructure, not dividends."

A ripple of approval ran through the gallery. Judge Vasquez's mouth twitched, almost a smile. Hensley adjusted his cuffs, pressing on. "Isn't it also true that your fiancé owns a business that competes with Blue Current's subsidiary for waterfront leases?"

"The Lighthouse Café sells espresso and grilled fish," Elena said dryly. "If Blue Current plans to diversify into cortaditos, I'll happily compete on flavor."

Laughter broke the tension. Even Judge Vasquez allowed it a beat before rapping her gavel lightly. "Counsel, move on."

During a recess, Elena retreated to a bench outside the courtroom, her body humming with adrenaline. She checked her phone. A video thumbnail from Talia awaited. She tapped it. Grainy footage filled the screen: the \textit{Artemis Star}'s cavernous hold, walls slick with condensation. Coast Guard officers in hazmat suits sprayed foam over gray canisters. A flashing red light pulsed near the ceiling—the failsafe indicator. The camera panned to a hatch where water gushed in thin streams.

Talia's voice overlaid the images. "Failsafe slowed. Your instructions worked. But we found a secondary cache tucked behind ballast tanks. Marked for `coastal deployment'. The manifest lists drop coordinates along the Atlantic corridor. If they jettison, they contaminate multiple reefs."

Elena's lungs squeezed. She glanced toward the courtroom door. Priya paced inside, phone pressed to her ear. Adrian reviewed notes with the DOJ team. Elena typed a rapid response: \textit{Send coordinates. We'll present to the judge. They support the monitor request.}

A minute later, Talia replied with a spreadsheet of GPS points, each annotated with tidal predictions. Elena forwarded it to Priya with a single line: \textit{Show her the dots.}

Back in the courtroom, Priya introduced the new evidence with quiet triumph. "Your Honor, the Coast Guard discovered additional canisters labeled for deployment along the coastline," she said, passing up the spreadsheet. "We ask the court to extend the injunction to cover all Blue Current maritime operations pending forensic analysis."

Judge Vasquez studied the map, brows knitting. She looked up at Hensley. "Counsel?"

Hensley cleared his throat. "Blue Current cannot be held responsible for unlabeled cargo stowed without executive knowledge."

"The cargo is labeled," Priya countered. "And the coordinates correspond to vulnerable reef systems."

The judge tapped a pen against the bench. "Mr. Vance, stand," she ordered.

Victor Vance rose, moving with controlled deliberation. His jaw muscle ticked. "Yes, Your Honor."

"Did you authorize any employee to load chemical agents onto the \textit{Artemis Star}?"

"No," he said smoothly.

"Are you willing to submit to an independent audit with full access to your vessels and communications?"

A beat of silence. Vance's gaze slid to his counsel. Hensley nodded fractionally. "Yes," Vance said, the word forced through gritted teeth.

Judge Vasquez leaned forward. "Here's my ruling. Blue Current Infrastructure is hereby enjoined from operating vessels, construction equipment, or dredging machinery within fifty miles of federally protected coastlines pending completion of an independent audit. A federal monitor will be appointed within forty-eight hours to oversee compliance. Failure to comply will result in contempt charges."

A collective exhale swept the courtroom. Priya's shoulders sagged with relief. Adrian closed his eyes briefly. Elena felt a tremor run through her limbs, part exhaustion, part triumph.

But Judge Vasquez wasn't finished. "Ms. Malhotra, draft the order with the DOJ and submit by six p.m. Mr. Hensley, ensure your client preserves all relevant records. Dr. Ruiz, please remain available for follow-up testimony."

"Yes, Your Honor," they chorused.

The gavel came down. Reporters surged toward the aisle. Priya grabbed Elena's elbow, steering her toward a side exit. "Don't give Vance a soundbite," she hissed.

They emerged into a courtyard ringed by granite pillars. The late-afternoon sky had turned the color of tarnished copper. Thunderheads stacked over the Potomac, grumbling distantly. Elena's phone buzzed again—this time with messages tumbling over each other. Marco. Talia. Naomi. Ignacio.

She answered Marco first. His voice trembled with restrained emotion. "The whole café erupted when the injunction came through," he said. "Ignacio cried. Don't tell him I told you."

Elena laughed, the sound breaking on a sob. "How's the \textit{Artemis}?"

"Contained for now," he said. "Your chilled water trick bought time. But they found canisters labeled for a drop near Palawan's north reef. Aisha's mobilizing their patrol."

Elena pinched the bridge of her nose. "We stopped one ship. There might be more."

"Then we keep stopping them," Marco replied. "Come home when you can. We'll keep the harbor standing."

She swallowed hard. "Tell Isabela to save me a bowl of caldo."

"Already on the stove," he said, then lowered his voice. "I miss you."

"I miss you too," she whispered. "I'll call tonight."

She hung up and turned to Priya. "We need to coordinate with NOAA about those coordinates," she said. "And the monitor appointment."

Priya nodded. "Naomi's setting up a war room at Sterling's office. DOJ wants us there in thirty."

They spent the next hours in a whirlwind of conference calls and document drafting. The Sterling office's glass walls reflected tired faces lit by laptop glow. Naomi projected a map across an entire wall, each red dot marking a potential drop site. Coalition partners joined via video, their backgrounds ranging from fishing docks to municipal offices.

Aisha appeared again, hair damp from sea spray. "We're dispatching patrol boats," she reported. "But if Blue Current has more freighters, we need satellite support."

A NOAA analyst on the call nodded. "We're flagging cargo movements tied to Blue Current shell companies. Coast Guard will board any vessel showing similar signatures."

Elena contributed sensor data, overlaying currents and reef locations. She caught Adrian staring at the map, fists clenched.

"You okay?" she asked quietly.

He exhaled. "My father texted: `Congratulations on kneecapping our margins.'" He let out a humorless laugh. "He still sees coastlines as ledger lines."

"Let him," she said. "We're drawing new ledgers."

By early evening, their words blurred. The DOJ attorney finalized the injunction order, tapping send with a flourish. Priya slumped back. "Filed," she said. "Judge Vasquez signed electronically."

Applause rippled through the room. Elena leaned against the table, letting the moment sink in. Victory tasted like burnt coffee and adrenaline. Her phone chimed with a new message from Talia: \textit{Coast Guard secured secondary cache. Chemicals neutralized. Boarding team en route to port with evidence. You did it.}

Elena closed her eyes, a wave of relief washing through her muscles. She pictured the flotilla cheering beneath sodium lights, the lab's volunteers hugging each other, the café's projector replaying the injunction clip.

Yet even as relief settled, fatigue sharpened every sensation. Her stomach growled. Priya tossed her a granola bar. "Dinner of champions," she said wryly.

"Is there anywhere in this building that sells actual food?" Elena asked.

Naomi grinned. "There's a Salvadoran place two blocks over. Pupusas and caldo. My treat."

They walked through humid twilight, city sounds muted by the promise of rain. The restaurant was small, windows fogged, air fragrant with masa and simmering broth. Elena inhaled deeply. The first bite of pupusa nearly made her cry. The warmth seeped into her bones, chasing the chill of the courthouse.

Halfway through the meal, her phone vibrated with a coded ring reserved for emergencies. She excused herself and stepped outside beneath a strip of awning. Rain had begun to fall, fat drops pitting the sidewalk.

"Dr. Ruiz?" Commander Patel's voice crackled through the line. "The \textit{Artemis Star} is secure, but we intercepted communications indicating another vessel—\textit{Morning Zenith}—departed Charleston last night. Same shell company. Manifest says turbine parts. Satellite imagery shows deck modifications consistent with hidden compartments."

Elena gripped the railing. "Where's it headed?"

"Projected route takes it near the Flower Garden Banks," Patel said. "We can intercept, but we need probable cause. Your injunction helps, but we need your lab's data connecting Blue Current operations to those reefs."

A gust of wind sprayed rain across her face. "I'll have Talia send over the coral stress logs. We tagged anomalies last month when their survey drones lingered."

"Make it fast," Patel urged. "They could dump cargo before we arrive."

Elena's mind raced. "I'll call you back within fifteen minutes." She hung up, heart pounding, and dashed inside.

"We have another ship," she told Priya and Adrian. "\textit{Morning Zenith}. Headed toward Flower Garden Banks."

Priya swore softly. "We just got the injunction."

"Which gives us leverage," Elena said. "But we need to show pattern." She texted Talia, fingers flying: \textit{Pull sensor logs from Flower Garden monitoring. Cross with Blue Current drone transponder data. Send to NOAA + Coast Guard now.}

Within minutes, Talia responded with a compressed file. Elena forwarded it to Commander Patel and the DOJ. Naomi patched Patel into their video call. His face appeared, streaked with saltwater and determination.

"We have probable cause," he said after skimming the data. "We're dispatching cutters and coordinating with Mexican authorities."

Elena nodded, relief blending with renewed vigilance. "We'll stay on standby."

Priya rubbed her temples. "At this rate, we need a 24-hour command center."

"We have one," Naomi said, gesturing around the war room. "You're looking at it."

They worked late into the night, drafting advisories, coordinating with Gulf Coast communities, briefing senators on the new development. Outside, rain drummed on the windows, turning streetlights into hazy halos. Elena's eyes burned, but each time she considered sleeping, another alert chimed. By midnight, her words blurred. Naomi pressed a keycard into her hand.

"There's a nap pod upstairs," she said. "Forty-five minutes. If we need you, we'll pound on the door."

Elena hesitated. Priya waved her away. "Go. Adrian and I will cover." He nodded, though exhaustion carved shadows under his eyes.

The nap pod resembled a curved shell lined with soft fabric. Elena slid inside, shoes off, compass resting against her chest. The hum of the city filtered through the walls, blending with distant thunder. She closed her eyes and let the darkness swallow her.

Sleep came in staccato bursts—images of the \textit{Artemis Star}, the courthouse, Marco's smile, waves exploding against a seawall. She woke to Naomi shaking her shoulder gently.

"It's 02:10," Naomi whispered. "Commander Patel is on the line."

Elena pushed upright, mind already reaching for focus. She padded downstairs, smoothing her hair with one hand. Priya stood at the map wall, eyes bloodshot, coffee clutched like a weapon. Adrian stared at a screen filled with coordinates.

Patel's voice boomed over speaker. "We intercepted the \textit{Morning Zenith}. Hidden compartments confirmed. We're escorting her to New Orleans."

A ragged cheer rose from the room. Elena sagged against the table, relief flooding her limbs. Patel continued, "Your data sealed it. They couldn't argue with the patterns."

"We're building a case for a criminal conspiracy," the DOJ attorney added, joining the call. "This goes beyond an injunction."

Elena scrubbed her face. "Good."

Patel's tone softened. "Dr. Ruiz, get some rest. You're testifying again tomorrow at the monitor appointment hearing."

Elena nodded automatically, though he couldn't see. "We'll be ready."

The call ended. Silence settled, heavy with exhaustion and victory. Priya slumped into a chair. "We keep putting out fires," she muttered. "One day, maybe we get to plant gardens instead."

"We will," Elena said quietly. She pictured Flower Garden Banks, coral fans swaying in azure water. She pictured Marisport's reef, polyps glowing under survey lights. She pictured Marco wiping tables in the café, humming low, waiting for her call.

She stepped to the window. Rain had tapered to a mist. The Capitol dome glowed in the distance, reflected in slick streets. Her phone buzzed softly—a final message for the night. Marco: \textit{I left the compass star chart on the counter. When you look out, you'll see Vega over the Potomac at 03:00. I'll be looking at it from the pier. Same sky, mi amor.}

She pressed her palm to the glass. The city smelled of ozone and ambition. The tide still surged, but for a breath she floated, anchored by a community that refused to drown and a partner tracing constellations across the same night.

The next tide would carry her into another courtroom, another confrontation. But for now, rain tapped a lullaby against the glass, and the compass at her heart steadied its beat.
