\chapter{Moorings}

Elena woke before the gulls. The apartment above the Lighthouse Café was still, the air tinged with cooling cinnamon and the faint salt of drying kelp. Marco's arm was a warm weight across her waist. For a long moment she lay listening to the harbor's hush and the distant grind of generators, letting the decision she had voiced the night before settle into bone. She was leaving. The thought rippled through her like the incoming tide—cold, bracing, inevitable.

Marco stirred. "You breathing like you're about to dive," he murmured against her shoulder.

"Feels like it," she admitted. "Except the water's on the other side of the world."

He propped himself on one elbow, studying her in the dim light. "We start charting it today. Flights, housing, when I'm visiting, who is shipping you coffee beans."

Elena laughed softly. "You're making spreadsheets before dawn?"

"Priya weaponized me," he said. "Color-coded tabs and everything."

He brushed a kiss against her collarbone, then slipped out of bed to start the coffee. Elena sat up, pressing her palms to her eyes. The exhaustion from the week carved hollows under her cheekbones, yet a bright, nervous energy thrummed beneath it. She rose, tugged on a sweatshirt, and joined Marco in the kitchenette. Steam curled from the mug he handed her.

"Your dad asked me to send you his way once you're up," he said, leaning a hip against the counter. "He's got opinions about pilings and, I'm guessing, children crossing oceans."

Elena winced. "I should've told him last night."

"You get a pass," Marco said. "We were dismantling a corporation."

She nodded, blew on her coffee, and stared out the window. The boardwalk below was a patchwork of new planks and temporary rails, lanterns guttering in the early breeze. Volunteers in borrowed waders hauled debris carts toward the cannery. Marisport was rebuilding, and she was preparing to leave.

"You'll come back different," Marco said quietly, following her gaze.

"So will the town," she replied. "Maybe we grow in the same direction."

He reached for her hand, squeezed once. "We will."

\bigskip

Her father was already on the boardwalk, boots planted on fresh timber, surveying the morning crews like a general. Miguel Ruiz was wind-chapped and stubborn, the kind of man who could coax a pier out of splintered driftwood. He turned when Elena approached.

"Thought you were on reef duty," he said, eyes narrowing.

"Priya confiscated my dive schedule," Elena answered. "Apparently I'm in meetings today."

He grunted. "Good. Somebody has to make sure the lab folks don't design something that can't survive a nor'easter."

Elena took a breath that tasted of cedar sawdust and brine. "Papi, I need to tell you something."

His gaze sharpened. "If this is about Adrian's foundation, I've already told him I'm not naming a dock after his grandfather."

"It's not that." She tugged the folded letter from her pocket, smoothing its creases. "I accepted an assignment with the International Oceanic Collective. I'll be in the Philippines for six months. Maybe longer, rotating through other sites after."

Miguel's silence was as heavy as lead. He took the letter, skimmed the header, the signature, the promise of research stations etched on coral atolls.

"You leaving us in the middle of rebuilding," he said finally. No accusation, just fact.

"I'm leaving to make sure what we rebuild here is part of something larger," she said. "The Collective's funding will stabilize the Institute. The resilience lab will have resources we never dreamed of. I'll bring back techniques, networks, attention."

He folded the letter carefully and handed it back. "And your family?"

Elena swallowed. "I'll call. I'll send videos. You'll visit."

"I'm a shipwright, hija. I don't hop on planes."

"We'll figure it out," she said, though the idea of her father navigating an airport made her chest tighten. "Priya already offered to help."

Miguel looked out toward the harbor where the lighthouse beam winked off, day asserting itself. "When your mother got the apprenticeship in San Juan, everyone said she was abandoning the yard," he murmured. "She came back with designs that kept us afloat for a decade. She also missed your first steps."

"I remember the stories," Elena said softly. "You told them whenever I accused you of hovering."

He huffed. "You'll accuse me of worse before you go." He pinched the bridge of his nose, the gesture of a man negotiating with his own worry. "I'm proud of you," he said at last. "Doesn't mean I won't complain every minute until you come home."

The knot in Elena's throat threatened to choke her. She stepped forward, wrapping her arms around him. He stiffened, then returned the embrace, his calloused hands warm against her back.

"You better teach those reefs to speak Spanish," he muttered. "So when they send you messages, I can understand the accent."

Elena laughed into his shoulder. "Deal."

He released her with a pat. "Go tell your aunt before she hears it from Mrs. Delgado. And tell your cousin Mateo he just got promoted to my right hand." He squinted. "When do you leave?"

"End of the month," she said. Saying it aloud made the timeline real. "We have four weeks to get the lab skeleton up, train the volunteer leads, finish the contamination reports, and somehow plan a wedding we might postpone."

Miguel snorted. "Wedding can wait. The sea won't."

\bigskip

By midmorning, the cannery smelled of fresh paint and ambition. The wide bay doors stood open, inviting in crisp autumn air. Sawhorses supported sheets of drafting paper. Laptops crowded folding tables beside trays of empanadas. Elena wove through the bustle, greeting volunteers and visiting engineers with quick nods.

The resilience lab charrette had drawn everyone from high-school robotics students to retired shipbuilders. Talia commandeered a whiteboard, sketching modular tank systems. Priya helmed a table of zoning maps, arguing with a city planner about load-bearing walls. Adrian moved between groups with a tablet, logging cost estimates, his tie abandoned in favor of rolled sleeves.

"You look like the conductor of a particularly chaotic orchestra," Elena said as she joined him.

"I'd settle for not dropping the baton," Adrian replied. His eyes flicked to the satchel slung over her shoulder. "How'd your father take the news?"

"With complaints and pride, in equal measure." She hesitated. "I need to make an announcement here, too. People deserve to hear it from me."

"I'll clear the floor after lunch," he said. He glanced toward Priya. "We finalized the memorandum of understanding. Lab governance will be a cooperative between the Institute, the city, and the foundation. No single entity in control."

Elena exhaled. "That's more equitable than most consortia I've seen."

"Priya wrote it," Adrian admitted. "I just threatened to pull funding if anyone argued."

Elena smiled despite herself. "Threats suit you when used for good."

He grimaced. "My board disagrees. Half of them want me back in Boston smoothing donor egos."

"What did you tell them?"

"That if they wanted a CEO who ignored communities in crisis, they should have left me in exile." He tapped his tablet. "Speaking of egos, Providence media wants an interview this afternoon. They'll ask about the Collective."

Elena winced. "Word travels fast."

"Faster when we redirect millions." He met her gaze. "I'll follow your lead."

At noon, the charrette paused for food. Volunteers gathered on overturned crates and pallets, balancing plates of arroz con gandules and still-warm focaccia. Elena climbed onto a crate, the chatter fading as eyes turned toward her.

"Before we dive back into tank specifications," she began, "I want to share something personal."

Murmurs rippled. Marco looked up from the makeshift coffee station, brow furrowed. Priya set her fork down, attention sharp. Adrian stood at the edge of the circle, hands tucked in his pockets.

"Last night I accepted an assignment with the International Oceanic Collective," Elena said. "They've invited me to join a global coral resilience initiative based in the Philippines for six months. After that, I'll rotate through partner sites."

Silence settled like mist. Somewhere, a gull cried.

"I'll leave at the end of the month," she continued. "Until then, I'll work with you to launch the resilience lab, train our teams, and secure every resource we can. While I'm away, Priya, Talia, and the Institute staff will lead the day-to-day. Adrian and the Sterling Foundation are committed to funding and support. I'll be a video call away."

An older fisherman near the back raised his hand. "You coming back?"

Elena nodded, the motion steady despite the quake inside. "Marisport is home. This is a season away, not a goodbye."

Talia wiped at her eyes with the heel of her hand. "You're going to bring back so many new coral strains we'll need another warehouse."

Laughter broke the tension. Priya stood, clapping once. "You better believe we'll hold you accountable, Ruiz. No slacking on saving the world."

The crowd followed with applause that swelled, warm and fierce. Marco threaded through the group to press a kiss to Elena's temple. "Proud of you," he whispered, voice thick.

Afterward, questions flew—logistics, delegation, travel vaccines, how to send care packages overseas. Elena answered until her throat rasped. With every plan, the reality of departure stitched tighter into the fabric of the day.

\bigskip

The afternoon dissolved into blueprints and budgets. Elena huddled with Talia and a team of engineers, debating flow rates for the new seawater intake. They mapped out contingency plans for power outages, anchored tank placements against flood projections, argued over whether the lab's observation deck should double as a community classroom.

"Make it modular," Elena insisted, pencil tapping the paper. "Storms will hit again. We need walls that can be dismantled and rebuilt without shutting down operations."

"We're designing for the next century," Talia said, eyes alight. "Not just the next hurricane season."

Across the room, Marco sat with Isabela and Ignacio, outlining staffing rotations for the café's relief kitchen. Elena caught snatches of their conversation—bulk ordering flour, coordinating deliveries with the food bank, scheduling downtime so no one burned out. Pride swelled in her chest. Marco thrived when caring for others, yet she saw the tightness in his jaw when their gazes met.

As evening edged in, Adrian approached, holding two paper cups of tea. "You look like you haven't blinked in an hour," he said, offering one.

"Blinking wastes time," she replied dryly, accepting the cup. The tea smelled of chamomile and citrus. "You okay?"

He leaned against a support beam, gaze roaming the bustling hall. "I keep waiting for the other shoe to drop. For someone to point out that a Sterling is steering relief efforts and decide the whole thing is rotten."

"People already pointed," Elena said. "Then they saw you hauling sandbags and getting yelled at by Mrs. Delgado. Actions matter."

He laughed under his breath. "She threatened to exile me if I didn't eat her empanadas."

"That's how she shows love." Elena took a sip of tea, letting the warmth anchor her. "When I'm gone, I need you to keep listening. To Priya. To Marco. To the volunteers. To the reef."

"I will," Adrian said. Something vulnerable flickered across his face. "For what it's worth, I'm... glad you're chasing this. Even if the selfish part of me hates how far away you'll be."

Elena held his gaze. Their history stretched between them—childhood summers at the tide pools, years of absence, the complicated gravity since his return. "Distance might be what we need to figure out who we are to each other," she said quietly.

He nodded, accepting the boundary in her words. "When you send updates, I'll turn them into grant proposals and marketing decks."

"Just don't make me a mascot," she warned.

"Never," he promised.

\bigskip

Night settled heavy and cool by the time Elena and Marco closed the café. Volunteers had drifted home, leaving behind empty trays and the echo of laughter. The boardwalk glowed under string lights rigged between newly erected posts. The sea beyond whispered secrets she longed to decipher.

They climbed the stairs to the apartment, bodies aching. Marco sank onto the couch, pulling Elena into his lap. She tucked her head under his chin, inhaling flour, coffee, the scent that meant home.

"We have four weeks," he murmured. "I made a list of things we need to cover. Budgeting, flights, a communications schedule, care package preferences, emergency contacts, what to do if you get dengue—"

"Marco," Elena interrupted gently. "Breathe."

He huffed out a shaky laugh. "I'm trying. I just keep seeing all the cracks."

"Then look at me," she said, tipping his chin until their eyes met. "We survived a hurricane. We exposed Tidefront. We're building a lab that will outlast us. We can do long distance."

His eyes softened. "Promise you'll let me visit before the six months are up."

"I'll book your flight myself," she said. "You'll bring contraband spices and scandalize customs."

"And I'll propose again somewhere with less debris," he said, attempting levity. "Maybe on a beach where the sand isn't full of splinters."

Elena's heart squeezed. Their engagement had been forged in storms, their plans perpetually deferred by disaster. "We don't have to postpone the wedding," she said. "We can keep planning, even if the date shifts."

He traced circles on her back. "Maybe the point isn't the ceremony. It's the choosing. Over and over, no matter the distance."

"Then we choose," she whispered. "Every day."

They sat in quiet, the hum of the refrigerator and the distant crash of waves the only sounds. Eventually, exhaustion dragged them to bed. Elena fell asleep with Marco's heartbeat against her spine and dreams of reefs pulsing like galaxies beneath foreign moons.

\bigskip

Two days later, the first shipment of lab equipment arrived—crated pumps, filtration systems, stacks of glass tanks shimmering in the morning light. Elena stood on the cannery loading dock, clipboard in hand, directing volunteers.

"Careful with the UV sterilizers," she called. "They're fragile. Miguel, can we rig a pulley to get the larger tanks to the mezzanine?"

"Already halfway there," her father replied, adjusting a chain hoist with Mateo's help.

Dr. Nia Okoye appeared via tablet, propped on a crate. Her video feed flickered slightly, but her smile was clear. "Your team moves like a tide at full moon," she said. "I'm impressed."

"We're stubborn," Elena replied. "The Collective sent preliminary itineraries?"

"Landing in Manila, then a week of orientation in Quezon City," Nia said. "After that, you'll join our reef base in Palawan. You'll rotate through satellite sites in Malaysia and Indonesia."

The list made Elena's pulse race. "I'll need to coordinate remote access to the lab systems here."

"Our IT team will support," Nia assured her. "We'll have weekly briefings. Also, bring the town's secret soup recipe. The scientists there still dream about the caldo from last year's summit."

Elena grinned. "That's Marco's domain."

As the day wore on, she barely paused. She led training sessions on water quality monitoring, recorded instructional videos with Talia, updated documentation for volunteers. She met with the school principal about integrating the lab into science curricula. She attended a city council session to secure expedited permits for the lab's exterior upgrades.

By evening, her voice was a rasp. Marco pressed a mug of honeyed tea into her hands. "You're doing it," he said softly. "You're building something that'll keep breathing while you're away."

"We're doing it," she corrected. "All of us."

He brushed his thumb over her knuckles. "You still scared?"

"Terrified," she admitted. "But the fear feels like standing on the bow of a boat heading toward sunrise."

He smiled. "Then let's keep steering."

\bigskip

A week later, at the first resilience lab donor walkthrough, Elena found herself guiding a group of skeptical benefactors past exposed beams and the tang of curing epoxy.

"Imagine this space with panoramic tanks showcasing reef regeneration in real time," she said, gesturing toward the central hall. "We'll host citizen science nights, livestream coral spawning events, train volunteer divers."

A woman in a tailored coat sniffed. "It looks... industrial."

"That's because we're mid-construction," Priya said dryly from behind her. "Come back in a month and it will look like the future of coastal resilience."

Adrian flanked the donors, smoothing edges with charm. Elena caught his eye; he gave a subtle nod, signaling that pledges were trending positive. Relief pricked behind her eyes. They were cobbling together funding, one skeptical benefactor at a time.

After the tour, Elena lingered on the mezzanine overlooking the harbor. The sunset painted the water copper. The skeleton of the lab cast long shadows across the floor. Priya joined her, leaning on the railing.

"You ready?" Priya asked quietly.

"Ask me again in three weeks," Elena said. "Or in Manila."

Priya bumped her shoulder. "We'll keep things afloat here. You go learn how to boss around a whole new set of bureaucrats."

Elena laughed, then sobered. "Take care of Marco while I'm gone. Make sure he remembers to sleep."

"Already have a shared calendar," Priya said. "And I'm deputizing Isabela."

Below, Marco emerged onto the boardwalk carrying trays of pastries for the night crew. He looked up, caught Elena watching, and lifted the tray in a mock toast. Warmth flooded her chest.

"You know," Priya mused, "when you get back, that wedding is going to have to seat half the global reef community."

Elena groaned. "One crisis at a time."

They fell into companionable silence, listening to the gulls and the rhythmic knock of waves against the pilings. The harbor smelled of seaweed and fresh paint. The lab would rise. Elena would leave. Both truths coexisted, heavy and hopeful.

\bigskip

Later that night, Elena reviewed a spreadsheet of training assignments when a notification pinged: an email from Nia with subject line \textit{Revised timeline}. Dread curled in her stomach. She opened it.

\textit{Elena}, the message read. \textit{We've received word that the Palawan site needs immediate leadership due to a cyclone damaging their monitoring equipment. We'd like you on the ground two weeks earlier than planned. Can you depart in fourteen days?}

Elena stared at the screen, pulse roaring. Fourteen days. Two fewer weeks to prepare, to breathe, to memorize the shape of home. She closed her eyes, imagined the reef halfway around the world gasping for attention.

Marco found her minutes later, concern etched on his face. "Bad news?"

She handed him the tablet. He read, jaw tightening. "Two weeks."

"I can't say no," Elena whispered. "They need help now."

Marco nodded slowly. "Then we accelerate the plan." He cupped her face, forcing her to meet his steady gaze. "We'll be ready."

Elena pressed her forehead to his. The apartment hummed with the quiet of impending change. Outside, the tide turned, pulling seaward. In fourteen days, she would follow.

\noindent\textit{Fourteen days isn't enough to memorize every tide line of home, yet urgency rarely waits for comfort. Standing on the mezzanine tonight, watching Marco salute me with pastry trays, I realized preparation is as much about trusting the team as it is about packing gear. If I want this lab to thrive while I'm gone, I have to let others steer sooner than feels safe.}
