\chapter{Outbound}

Departure day dawned clear and brittle. The harbor wore a hush, as if even the waves held their breath. Elena watched the sunrise from the café window, a mug cupped between her hands. Marco moved quietly around her, packing last-minute snacks into her backpack—empanadas wrapped in foil, tamarind candies, a small jar of café coffee beans.

"You don't have to feed the entire plane," she teased.

"Consider it insurance," he replied. "If they taste Marisport, they'll take care of you."

Her suitcases stood by the door, zippers straining. The compass lay against her sternum on a leather cord. The waterproof journal tucked into her carry-on. Marco's folded note waited in her passport. Every item felt like an anchor.

A knock rattled the door. When Marco opened it, half the town seemed to fill the stairwell. Priya held a thermos. Talia waved a stack of laminated checklists. Miguel carried a duffel bristling with tools she absolutely could not take through airport security.

"Dad," Elena protested, laughing. "They'll arrest me."

"Fine," he grumbled, passing the duffel to Mateo. "We'll mail them."

Isabela pressed rosary beads into Elena's palm. "For protection," she said. "Even scientists need saints."

Adrian appeared at the back of the crowd, a travel pillow slung over his shoulder. "I booked the car to the airport," he said. "Figured you'd want company for the first leg."

"I thought you had a board meeting," Elena replied.

"I moved it," he said simply. "Wouldn't miss this."

The apartment could not contain the goodbyes. They spilled onto the boardwalk, where the morning air tasted of salt and sawdust. Volunteers lined up, hugging Elena one by one. She promised to write, to call, to send photos. Priya hugged her so fiercely Elena wheezed.

"Don't become a bureaucrat," Priya whispered. "Or if you do, be the terrifying kind."

"I'll terrorize responsibly," Elena promised.

Talia hugged her next, eyes shining. "I set up the remote coral spawning monitor," she said, voice thick. "Call me the second you land."

"I will," Elena said. "You're in charge of scolding Adrian if he overworks."

"Already scheduled," Talia replied, managing a watery grin.

Miguel's embrace nearly cracked her ribs. "Call your father," he ordered. "Not just when you're sick."

"Every Sunday," she vowed.

Finally, it was Marco. The crowd respectfully looked away as he pulled her close. "Two flights," he murmured against her hair. "Providence to LA, LA to Manila."

"Plus a puddle jumper to Palawan," she said.

"Text me from every layover. Send me pictures of airport chairs so I can critique their ergonomics."

Elena laughed, the sound breaking. "I love you."

"I love you more," he said, kissing her slow and sure. He stepped back reluctantly, fingers trailing from hers until the last possible moment.

Adrian cleared his throat. "Car's waiting."

Elena gathered her bags. The compass thudded gently against her chest with each step. She climbed into the backseat beside Adrian, Marco squeezing her hand through the open window one last time.

"Bring back stories," he said.

"And new recipes," Isabela called.

"And legal strategies," Priya added.

Elena waved until the boardwalk curved out of sight. The car rolled through Marisport's streets—past the lab skeleton wreathed in scaffolding, past the lighthouse, past the boarded windows still awaiting glass. She pressed her palm to the glass, committing every corner to memory.

\bigskip

The drive to the Providence train station passed in quiet conversation. Adrian updated her on lab permits, donor pledges, the Sterling board's grudging compliance.

"They agreed to the transparency audits," he said. "Priya is already drafting the first report."

"She'll make it mandatory reading for every city official," Elena said.

He smiled. "How are you, really?"

"Oscillating between exhilarated and nauseous," she admitted.

"Sounds about right," he said. "When I took over the foundation, I felt like I was piloting a ship in a storm with a map drawn by people who hated me."

Elena snorted. "We do not hate you."

"An improvement," he said lightly. His eyes softened. "Elena, if you need anything—"

"I know," she said. "Thank you for steering things here."

At the station, Priya's SUV awaited with Marco at the wheel, unwilling to let go too soon. They transferred luggage, double-checked tickets, hugged again. Finally Elena boarded the train with Adrian. As the car eased out of the station, Marco trotted alongside the platform, keeping pace until the train gathered speed. He lifted a hand; she pressed hers to the glass. Then he was a blur, then a point, then gone.

The train hummed south toward the airport. Adrian scrolled through emails; Elena stared at the passing marshes, the water flashing silver between reeds.

"Read the note," Adrian said quietly, nodding toward her passport.

"It's for the plane," she said.

"The train counts," he argued. "Consider it acclimation."

She rolled her eyes but slid the folded paper free. Marco's handwriting slanted across the page.

\textit{Mi sirena,}\
\textit{If you're reading this, you're already farther away than we've ever been. That's terrifying and thrilling. Here's what to remember: You are not alone. I'm in your pocket (check the inside zipper—yes, do it now).}\
\textit{—She checked, finding a tiny Polaroid of them laughing on the lighthouse steps.—}\
\textit{Call me when you land. Tell me about the clouds. Tell me about the food. Tell me about the reef like it's gossip.}\
\textit{When doubt whispers, hear my voice louder. When joy erupts, share it with me so it doubles. When you need grounding, hold the compass and feel how steady you are.}\
\textit{Come back when the tide tells you. I'll be waiting with caldo and a ring we still haven't used.}\
\textit{Always,}\
\textit{M.}

Elena pressed the note to her lips. Adrian pretended not to see her tears.

\bigskip

Airports blurred into a series of fluorescent tunnels. At Providence, Priya hugged her one last time at the security checkpoint, whispering, "Crush them." Elena and Adrian navigated TSA with minimal chaos—though Miguel's forgotten wrench did trigger a secondary bag search. In Los Angeles, they parted ways. Adrian boarded a return flight east; Elena boarded the long haul to Manila.

She found her seat between a grandmother crocheting and a businessman poring over spreadsheets. The plane shuddered into the night. Elena watched the lights of the coast recede, the dark expanse of the Pacific swallowing the horizon. She closed her eyes, feeling the compass pulse against her sternum, the weight of hundreds of goodbyes settling into purpose.

Hours dissolved into movies, fitful sleep, the rhythm of engines. She woke to dawn bleeding pink across cloud tops. The businessman snored softly. The grandmother offered her mango candy. Elena accepted gratefully, the sweetness anchoring her in the surreal liminal sky.

In Manila, humidity wrapped her like a wet blanket the moment she stepped off the plane. The air smelled of jet fuel and blooming sampaguita. Dr. Nia Okoye waited at the arrivals gate, wearing a dress patterned with coral branches.

"Welcome to the archipelago," Nia said, pulling Elena into a hug. "You look exhausted and magnificent."

"Mostly exhausted," Elena replied, laughing.

"Sleep later," Nia said, already steering her through the crowd. "We have orientation in two hours."

They navigated a blur of customs, baggage claims, taxis honking like geese. Elena glimpsed jeepneys painted in neon colors, billboards advertising whitening cream, street vendors frying plantains. Manila pulsed, frenetic and alive.

At the Collective's Manila office, a converted colonial house shaded by mango trees, Elena met the global team—scientists from Indonesia, Kenya, Brazil, Fiji. They shook her hand, welcomed her in accents layered with sea stories.

"We'll brief you on the cyclone damage," Nia said, ushering her into a conference room where maps of Southeast Asia covered the walls. "Palawan's monitoring array was shredded. Fishers reported bleaching along the outer reef. The local community council is wary; they've been burned by outsiders before. We need your diplomacy as much as your data."

Elena nodded, the challenge sparking adrenaline despite her jet lag. "What support do we have on the ground?"

"A team of twenty scientists, plus community stewards," Nia said. "You'll be co-leading with Dr. Aisha Karim—brilliant, stubborn, hates bureaucracy. You'll get along."

The orientation lasted four hours. Elena fought to stay alert as they covered health protocols, evacuation routes, data infrastructure. She signed a stack of documents, received a satellite phone, memorized call signs. By the time they finished, the afternoon sky had turned the color of wet slate.

"We fly to Puerto Princesa at dawn," Nia said. "Tonight, rest. Eat. Call home."

Elena retreated to the guest suite, showered off twenty hours of travel, and dialed Marco on the satellite phone. The connection crackled, but his voice came through, warm and familiar.

"You sound like you're underwater," he joked.

"Feels like it," she said, smiling. She described the humidity, the mango candy, the team. He told her about the café's lunch rush, the lab's new turbine, the way Priya had reorganized the city council agenda.

"How's the compass?" he asked.

"Still pointing home," she said.

"Good," he replied. "Sleep. I'll call when you're up."

She spoke next with Priya, then Talia, then her father. Each call braided her life in Marisport with the new horizon unfurling before her. Afterward, she collapsed into bed and slept like a stone.

\bigskip

The flight to Palawan was a jostling hop over islands scattered like emeralds. Elena pressed her forehead to the window, watching the South China Sea glitter. Beaches curved white against turquoise water. Mangrove forests unfurled like green lace.

At Puerto Princesa, the Collective's field trucks waited. Elena climbed into the back, duffel at her feet, compass warm against her chest. Beside her sat Dr. Aisha Karim, a lean woman with keen eyes and a shaved head.

"You the famous reef whisperer from Rhode Island?" Aisha asked, arching a brow.

"Depends who you ask," Elena replied. "Some people call me bossy."

"Good," Aisha said. "We need bossy. Cyclone tore our sensors apart and scared our partners. Local fishers think we're bringing more trouble."

"Let's show them otherwise," Elena said.

They bounced along coastal roads, passing nipa huts on stilts, children waving, roosters crowing. The air smelled of salt and hibiscus. As they neared the field station, a battered sign announced \textit{Bahura Resilience Hub}. The compound overlooked a lagoon, the water churned cloudy by recent storms. Docks jutted into the shallows, some planks missing.

The team greeted them with weary smiles. Solar panels lined the roof of the main lab, some cracked. Wind turbines creaked. Elena recognized the expression on the scientists' faces—determined exhaustion she had worn for weeks.

"We lost the main array," a technician named Leo reported, gesturing toward twisted metal stacked beside the lab. "Sensors fried."

"We'll rebuild," Aisha said crisply. "Dr. Ruiz, meet our community liaison, Alon Santos."

A man in his fifties stepped forward, skin sun-darkened, hair streaked with gray. "Welcome," he said cautiously. "My people are wary. The government promised support after the last typhoon and delivered nothing but surveys."

"I understand distrust," Elena replied. "Where I'm from, developers poisoned our reef. We fought them. We won."

Alon's gaze sharpened. "Then you know what we're up against."

"I do," she said. "And I'm here to work alongside you. Not above you."

He studied her for a heartbeat, then nodded. "We'll see your worth in the water."

\bigskip

That afternoon, despite jet lag, Elena insisted on assessing the reef. She and Aisha suited up, joined by Alon and two younger divers. The lagoon's water was warm, visibility decent. As they descended, the reef unfurled—tables of coral bleached in patches, broken branches littering the sand. Schools of damselfish darted nervously. A torn fishing net tangled around a colony of staghorn coral, strangling polyps.

Elena's chest tightened. She carefully cut the net free, mindful of the fragile branches. Aisha recorded footage, narrating the damage. Alon pointed to cracks in the limestone shelf, where storms had pried loose chunks.

"We've seen dynamite fishing scars," he signaled underwater.

Elena's gut clenched. At the surface, she pulled off her mask, gasping. "Illegal blast fishing?"

"Yes," Alon said grimly. "The cyclone disrupted patrols. People desperate for fish made bad choices."

Aisha cursed. "We'll have to address it with the council."

Elena's mind whirled. They were fighting storms, corporate negligence, and now illegal fishing. The scale of the work loomed like a wave. She reminded herself: one fragment at a time. She had lived this rhythm before.

That evening, she joined the team around a bamboo table. They planned sensor replacements, community meetings, dive schedules. She outlined strategies they'd used in Marisport—volunteer brigades, storytelling campaigns, transparent data. The team listened, some skeptical, others hopeful.

As darkness fell, Elena stepped outside. The lagoon shimmered under starlight. Cicadas droned. She dialed Marco, the satellite phone crackling.

"I'm standing under a sky full of constellations I don't know," she said when he answered.

"Take pictures," he replied. "We'll learn them together."

"We dove today," she said softly. "The reef is hurting, but it's alive. There's blast damage. We'll have to win hearts before we win the water."

"You've done it before," he reminded her. "You'll do it again."

"How's home?"

"Talia led her first solo dive and didn't let the city council derail the lab's permit hearing. Priya terrified a developer into donating lumber. Adrian sent you a spreadsheet titled 'Things To Fix Before Elena Yells At Me.'"

Elena laughed, the sound echoing across the lagoon. "Tell them I expect weekly reports."

"Already on the calendar," Marco said. "Get some sleep."

She hesitated. "I miss you."

"I miss you," he said. "But hearing your voice from the other side of the world feels like a miracle."

They said goodnight reluctantly. Elena slipped the compass from beneath her shirt, holding it up to the stars. The needle pointed north, unwavering. She tucked it back against her skin, grounding herself in the steady pull of home even as she rooted in new waters.

\bigskip

Two nights later, during a strategy meeting, Aisha burst into the room clutching her phone.

"We have a problem," she said, voice taut. "Local radio reports a syndicate planning a blast fishing run near the protected zone tomorrow night. They're targeting the reef section we just stabilized."

Elena's pulse spiked. "Do we have authority to intervene?"

"We coordinate with the Coast Guard," Aisha said. "But they need proof before launching a patrol."

Alon slammed his palm on the table. "We can't wait. One blast could undo months of work."

Elena leaned over the map spread across the table. The threatened zone overlapped with the coral nursery they'd planned to install. She imagined dynamite tearing through delicate branches, fish scattering like shattered glass.

"We gather evidence," she said, mind racing. "Set up hydrophones tonight. Deploy the drone at dusk. Document any illegal activity."

"The syndicate won't like being filmed," Alon warned.

"They won't see us coming," Elena replied, voice steely. "We faced corporate lawyers and hurricanes. We can face this."

Aisha met her gaze, respect sparking. "You ready to go to war, Ruiz?"

Elena clenched her fists, feeling the compass press against her skin. The tide had carried her across an ocean to stand at this threshold. "I didn't cross the world to watch another reef die," she said. "We protect it."

Outside, the lagoon lapped quietly at the shore, unaware of the battle forming. Elena stepped into the humid night, inhaled the scent of salt and hibiscus, and felt the tide of responsibility surge. Somewhere far away, the lighthouse beacon in Marisport swept across the harbor. Here, under unfamiliar stars, she lit her own resolve. The next chapter would begin with a fight.
