% disposition.tex - Outline for a love triangle novel
\chapter*{Disposition}

\section*{Premise}
In the coastal city of Marisport, three intertwined lives are upended when the long-lost childhood friend of a local marine biologist returns as the charismatic heir to a renewable-energy empire. Their reunion rekindles memories, rivalries, and unspoken desires that threaten to derail a decade-long engagement.

\section*{Principal Characters}
\begin{description}
  \item[Elena Ruiz] A driven marine biologist devoted to conserving the fragile reefs surrounding Marisport. Logical, compassionate, and rooted in her community, Elena struggles between loyalty to her fiancé and the tidal pull of her past.
  \item[Marco Alvarez] Elena's fiancé, owner of the beloved Lighthouse Café. Steady and dependable, Marco champions Elena's work but secretly fears being left behind as her ambitions grow beyond their small town.
  \item[Adrian Sterling] Elena and Marco's childhood friend who left Marisport after a family scandal. Returning as the newly appointed CEO of the Sterling Foundation, Adrian carries unresolved guilt and a magnetic confidence that unsettles the couple's carefully curated life.
\end{description}

\section*{Structure}
The novel unfolds over four parts that mirror the ebb and flow of the tide.
\begin{enumerate}
  \item \textbf{Low Tide} introduces Marisport's routines, Elena and Marco's engagement preparations, and Adrian's unexpected return to fund a cutting-edge reef restoration project.
  \item \textbf{Rising Tide} charts Elena's deepening collaboration with Adrian, Marco's mounting insecurities, and the town's divided loyalties as secrets from the past resurface.
  \item \textbf{High Tide} culminates in a hurricane that forces the trio into close quarters, exposing buried truths, shifting alliances, and Elena's realization that love must encompass both passion and partnership.
  \item \textbf{Ebb Tide} follows the aftermath as each character must choose between comfort and growth, ultimately redefining their relationships with one another and with Marisport itself.
\end{enumerate}

\section*{Themes and Motifs}
Recurring imagery of tides, coral regeneration, and lighthouse beacons symbolize resilience, change, and guidance through emotional storms. The narrative explores how love evolves when ambition, history, and community obligations collide.

\section*{Resolution}
Elena embraces a new research opportunity abroad while negotiating a long-distance partnership with Marco built on renewed honesty. Adrian remains in Marisport to repair familial ties and supports Elena's project from afar, transforming the former triangle into a network of chosen family grounded in mutual respect.
