% Contents overview for the manuscript front matter
\chapter*{Contents Overview}
\addcontentsline{toc}{chapter}{Contents Overview}

\noindent\textbf{Chapter 1: Low Tide}\\
Elena Ruiz opens the story tending Marisport's coral nurseries, discovers an alarming algae bloom, and juggles preparations for both a critical funding visit and her life with Marco. The chapter anchors the stakes in the reef's fragility while hinting that Adrian Sterling's return will unsettle the balance she has built.

\medskip

\noindent\textbf{Chapter 2: Undertow}\\
Elena confronts Adrian at dawn, extracting strict terms for a Sterling Foundation partnership even as old emotions resurface. The day spirals through algae sampling, political negotiations, and a packed council meeting that lays bare how the town will scrutinize every step they take together.

\medskip

\noindent\textbf{Chapter 3: Crosscurrents}\\
A solvent spill from the luxury condo site forces the Institute and town into emergency cleanup, testing alliances and exposing the developers' negligence in full public view. Press conferences, a volatile town hall, and a dawn inspection push Elena, Marco, and Adrian into new patterns of cooperation under intense pressure.

\medskip

\noindent\textbf{Chapter 4: Stormglass}\\
As forecasts confirm a looming hurricane, Elena orchestrates storm preparations that transform the Institute, cannery, and café into command centers. Community rallies, logistical marathons, and long-suppressed conversations set the stage for the partnership contract and the emotional storm still to come.

\medskip

\noindent\textbf{Chapter 5: Eyewall}\\
Hurricane Calista slams Marisport, turning the Institute into a bunker where rescues, power failures, and structural triage unfold in breathless succession. During the eye's brief calm, Elena, Marco, and Adrian brave the surge to relight the lighthouse, saving the fleet waiting offshore before racing the storm's return.

\medskip

\noindent\textbf{Chapter 6: Driftline}\\
In the storm's aftermath, Elena coordinates relief, surveys reef damage, and uncovers a leaked solvent drum that shuts down the Tidefront project amid legal fallout. Exhaustion mixes with resolve as the town commits to rebuilding, and an invitation to lead a global coral initiative hints at new horizons ahead.

\medskip

\noindent\textbf{Chapter 7: Soundings}\\
Elena salvages coral fragments while marshaling legal action against Tidefront, ultimately securing a new resilience lab and redirecting Sterling funds to community recovery. As she confides in Marco and the town rallies, she accepts an invitation to lead a global coral initiative, setting the stage for love and duty to stretch across oceans.
